### 2025-01-31 paper/paper.qmd
Project Proposal

---
title: "Analyzing How Organization Size, Sector, and Cybersecurity Strategies Influence Impacts on Cyberattacks"
subtitle: "Based on Data Collected From the University of Queensland"
author: 
  - Shivank Goel
thanks: "Code and data are available at: https://github.com/shivankgoel003/DataBreach_Ransomware_Stats"
date: today
date-format: long
abstract: "Undoubtedly as technology is progressing and we are stepping more closer to the digital world, the digital threats are also increasingly rapidly. This study discusses the influence of organizational size, sector, and cybersecurity strategies on cyberattack impacts. Utilizing a dataset from the University of Queensland about data breaches and ransomware attacks from 2004 to 2019, we analyze the trends and correlations and study how different factors contribute to the severity and frequency of these incidents. Our analysis reveals key insights: larger organizations report more cyber incidents, sectors like healthcare and education are frequent targets, and cybersecurity frameworks significantly help in reducing the user impact. These findings highlight critical areas for how organizations can improve their security and protect their data."
header-includes:
   - \usepackage{tikz}
   - \usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, calc}
   - \usepackage{pgfplots} 
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{longtable}

format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(readxl)
library(here)

breach_data <- read.csv(here("data/analysis_data/breach_data.csv"))
```

# Introduction

Therefore, in response to such attacks, there is a need for a plan, that not just keep the intruder or hackers out but also quickly alert if an attack does happen. Our study looks at cyber resilience, which is “ the ability to anticipate, withstand, recover from, and adapt to adverse conditions, stresses, attacks, or compromises on systems that use or are enabled by cyber resources.” as defined by National Institute of Standards and Technology [@NISTGlossary2023]. We break our study into three major research questions, which forms the thesis of our study:

**RQ1**: How do organizational factors such as size and sector, influence the severity of cyber breaches experienced by companies?

**RQ2**: Which cybersecurity strategies, including frameworks, policies, and preventive measures, are the most effective one, in reducing the damage caused by cyber attacks?

**RQ3**: In what ways do the industry type and digital dependence of a business affect the overall impact of a cyber attack, in terms of preserving confidentiality, integrity and availability of data?

We also plotted a bar graph @fig-sector to count the number of incidents across various sectors. The bar chart clearly indicates that the 'Human Health Activities' sector has the highest count of incidents, standing out significantly from the other sectors. This might suggest that health sector is a more frequent target for cyber incidents or probably it is more diligent in reporting such events. The other sectors show a range of incident counts, with most appearing to have far fewer incidents in comparison. This could point to different levels of risk exposure, varying security measures, or reporting practices across these sectors.

\newpage

# References

### 2025-01-31 paper/project_proposal.qmd
Project Proposal

---
title: "Project Proposal"
author: 
  - Navya Hooda
  - Mohammed Yusuf Sheikh
  - Shivank Goel
  - Vanshika Vanshika
  - Jena Shah
date: today
date-format: long
number-sections: true
format: pdf
---

# Project title: Effects of Different Pain Relievers on Task Performance

## Relevant background information  
Pain can affect how well we perform everyday tasks in situations where focus and mental clarity are crucial. Aspirin, Paracetamol, and Tramadol are pain relievers used commonly to reduce discomfort, but we don’t know much about their impacts on cognitive functions. Tasks that require mental effort such as solving math problems, recalling information, or remaining focused for long periods of time, are harder to perform while in pain.  
This study is interested in how different types of common pain relievers at standard dosages (Aspirin, Paracetamol, and Tramadol) may affect how well people perform in tasks testing mental arithmetic, memory, and attention. These tasks are used in various settings, so understanding how pain relief can impact performance can be valuable to help with pain management without an impact on productivity.

## Research questions  
**Question 1:** How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg) affect cognitive task performance, as measured by mental arithmetic and memory tests?  
**Question 2:** How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg) affect physiological task performance, as measured by respiratory rate and blood pressure?  
**Question 3:** How do pain relievers at different doses (Aspirin 250 mg vs 500 mg vs 750 mg, Paracetamol 250 mg vs 500 mg vs 750 mg, Tramadol 25 mg vs 50 mg vs 75 mg) affect cognitive and physiological task performance while controlling for individual variability?

## The experimental units  
Individuals from the island simulation.

## The variables  
- **Factor Variables:** Type of pain reliever (Aspirin, Paracetamol, Tramadol, Placebo).  
- **Quantitative Covariates:** Age, weight, IQ test score.  
- **Response Variables:**  
  - Cognitive tasks: Mental Arithmetic, Memory Task  
  - Physiological tasks: Blood pressure, Respiratory rate

## The treatments  
- Aspirin  
- Paracetamol  
- Tramadol  
- Placebo

## The total number of planned observations  
Considering 50 observations per treatment (and 4 treatments), the total number of planned observations is \(50 \times 4 = 200\). So there will be 200 total observations.

TO-DO

## How the experiment will be conducted, and how will possible confounding variables   be mitigated?
Our experiment will include all four principles of experimental design:

### Control  
- A placebo group is included to compare the effects of active pain relievers against no treatment.  
- Participants' baseline task performance will be measured before administering treatments to account for individual variability.

### Blocking  
- Participants will be blocked by age group (e.g., 18-30, 31-50, 51+), as age may influence both pain tolerance and task performance.

### Randomization  
- Participants will be randomly assigned to the treatments (Aspirin, Paracetamol, Tramadol). Randomization ensures that any confounding variables are evenly distributed across groups.

### Replication  
- Each treatment will have 50 observations to ensure sufficient data for statistical analysis. This replicates the experiment multiple times across participants.

## Name the method(s) you are planning to use to analyze the data  
This is submitted before you start conducting the experiment and get any data. Methods include (but are not limited to):  
- One-way ANOVA  
- Two-way ANOVA  
- Randomized Complete Block Design (RCBD): A Randomized Complete Block Design (RCBD) can be used, where each individual (or simulation agent) acts as a block and is exposed to all three dosage levels of a randomly assigned pain reliever. This design helps control for variability between individuals while isolating the effects of dosage on task performance.  
- Latin Square Design  
- Balanced Incomplete Block Design (BIBD)  
- ANCOVA

### 2025-02-01 paper/project_proposal.qmd
Corrected Name Update for MYS

@@
   - Navya Hooda
-  - Mohammed Yusuf Sheikh
+  - Mohammed Yusuf Shaikh
   - Shivank Goel

### 2025-02-01 paper/project_proposal.qmd
Updated point number 1.3 Experimental Units
Draft for proposal

@@
 ---
-title: "Project Proposal"
+title: "Effects of Different Pain Relievers and Dosages on Cognitive Retention"
 author: 
@@
 
-# Project title: Effects of Different Pain Relievers on Task Performance
-
 ## Relevant background information  
 Pain can affect how well we perform everyday tasks in situations where focus and mental clarity are crucial.
-Aspirin, Paracetamol, and Tramadol are pain relievers used commonly to reduce discomfort, but we don’t know much about their impacts on cognitive functions.
-Tasks that require mental effort such as solving math problems, recalling information, or remaining focused for long periods of time, are harder to perform while in pain.
-This study is interested in how different types of common pain relievers at standard dosages (Aspirin, Paracetamol, and Tramadol) may affect how well people perform in tasks testing mental arithmetic, memory, and attention.
-These tasks are used in various settings, so understanding how pain relief can impact performance can be valuable to help with pain management without an impact on productivity.
+Aspirin, Paracetamol, and Tramadol are pain relievers used commonly to reduce physical discomfort, but we don’t know much about their impacts on cognitive functions.
+Tasks requiring mental effort, such as recalling information, are harder to perform while in pain.
+This study is interested in how different types of common pain relievers at standard dosages (Aspirin, Paracetamol, and Tramadol) may affect outcomes of tasks involving memory tests.
+We also analyze the effects of different dosages of each drug on memory function.
+The concept of recalling information is used in various settings, so understanding how pain relief can impact performance can be valuable to help with pain management without an impact on productivity.
 
 ## Research questions
-**Question 1:** How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg) affect cognitive task performance, as measured by mental arithmetic and memory tests?  
-**Question 2:** How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg) affect physiological task performance, as measured by respiratory rate and blood pressure?  
-**Question 3:** How do pain relievers at different doses (Aspirin 250 mg vs 500 mg vs 750 mg, Paracetamol 250 mg vs 500 mg vs 750 mg, Tramadol 25 mg vs 50 mg vs 75 mg) affect cognitive and physiological task performance while controlling for individual variability?
+
+*Question 1:* How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg) affect cognitive task performance, as measured by mental arithmetic and memory tests?
+
+*Question 2:* How do pain relievers at different doses (Aspirin 500 mg vs 1000 mg, Paracetamol 500 mg vs 1000 mg, Tramadol 50 mg vs 100 mg) affect cognitive performance while controlling for individual variability?
 
 ## The experimental units  
-Individuals from the island simulation.
+We will use 'The Islands' virtual population as our simulated dataset to investigate our research questions. This dataset provides individual-level data for experimental analysis.
 
 ## The variables
-- **Factor Variables:** Type of pain reliever (Aspirin, Paracetamol, Tramadol, Placebo).  
-- **Quantitative Covariates:** Age, weight, IQ test score.  
-- **Response Variables:**  
-  - Cognitive tasks: Mental Arithmetic, Memory Task  
-  - Physiological tasks: Blood pressure, Respiratory rate
+
+a) The first question looks at the different drugs at standard doses.
+So the type of *pain reliever* taken is our *qualitative factor variable* with 4 levels (Aspirin, Paracetamol, Tramadol, Placebo).
+Each level is of the average dosage – 500 mg, 500 mg, 50 mg, respectively.
+
+b) The second question tackles the *dosage levels* amongst the pain relievers taken.
+So the variables here are not just the type of pain reliever, but also the dosages (500 mg vs 1000 mg, 500 mg vs 1000 mg, and 50 mg vs 100 mg).
+The dosage levels are *qualitative factor variables*.
+
+c) The performance with the *memory task cards* and *memory game* are our *response variable*.
+
+*Quantitative Covariates:* Age, IQ test score, highest level of education obtained.
 
 ## The treatments  
+Pain Reliever Types (4 Levels)
 - Aspirin  
@@
 ## The total number of planned observations  
-Considering 50 observations per treatment (and 4 treatments), the total number of planned observations is \(50 \times 4 = 200\). So there will be 200 total observations.
-
-TO-DO
+Considering 30 observations per treatment (and 4 treatments), the total number of planned observations is 30 x 4 = 120. So there will be 120 total observations.
 
@@
 ### Control
-- A placebo group is included to compare the effects of active pain relievers against no treatment.  
-- Participants' baseline task performance will be measured before administering treatments to account for individual variability.
+
+-A placebo group is included to compare the effects of active pain relievers against no treatment. 
+-Participants' *baseline performance* on cognitive tasks (mental arithmetic, memory, and attention) will be measured before giving any treatment.
+-The same environment will be used for all participants (e.g., time of day, noise levels).
 
 ### Blocking
-- Participants will be blocked by age group (e.g., 18-30, 31-50, 51+), as age may influence both pain tolerance and task performance.
+
+- To reduce the variability, participants will be blocked by IQ level (e.g., 70 below, 70-130, 130 above), as IQ may influence task performance.
+- Other key variables, if needed, like education level (less than high school, high school, undergraduate, above undergraduate) and age (18-34 , 35-50, 50+), will also be blocked to ensure fair comparisons between groups.
 
 ### Randomization
-- Participants will be randomly assigned to the treatments (Aspirin, Paracetamol, Tramadol). Randomization ensures that any confounding variables are evenly distributed across groups.
+
+- Each participant will be randomly assigned a treatment to balance out any differences between individuals.
+- If done as a group, we will also randomize which group member is responsible for administering each treatment.
 
 ### Replication
-- Each treatment will have 50 observations to ensure sufficient data for statistical analysis. This replicates the experiment multiple times across participants.
+
+- We will collect 30 observations per treatment.
+-Since there are 4 treatments (Aspirin, Paracetamol, Tramadol, Placebo), there will be 120 total observations.
+-This replication will provide enough data to detect differences in performance across treatments.
 
 ## Name the method(s) you are planning to use to analyze the data
-This is submitted before you start conducting the experiment and get any data. Methods include (but are not limited to):  
-- One-way ANOVA  
-- Two-way ANOVA  
-- Randomized Complete Block Design (RCBD): A Randomized Complete Block Design (RCBD) can be used, where each individual (or simulation agent) acts as a block and is exposed to all three dosage levels of a randomly assigned pain reliever.
-This design helps control for variability between individuals while isolating the effects of dosage on task performance.
-- Latin Square Design  
-- Balanced Incomplete Block Design (BIBD)  
-- ANCOVA
+
+We plan to use *one-way ANOVA* for Research Question 1 and *two-way ANOVA* for Research Question 2.

### 2025-02-27 paper/EDA.qmd
EDA paper setup

--- 2025-01-31 paper/paper.qmd
@@
 ---
-title: "Analyzing How Organization Size, Sector, and Cybersecurity Strategies Influence Impacts on Cyberattacks"
-subtitle: "Based on Data Collected From the University of Queensland"
+title: "Effects of Different Pain Relievers and Dosages on Cognitive Retention"
 author: 
+  - Navya Hooda
+  - Mohammed Yusuf Shaikh
   - Shivank Goel
-thanks: "Code and data are available at: https://github.com/shivankgoel003/DataBreach_Ransomware_Stats"
+  - Vanshika Vanshika
+  - Jena Shah
 date: today
 date-format: long
-abstract: "Undoubtedly as technology is progressing and we are stepping more closer to the digital world, the digital threats are also increasingly rapidly.
-This study discusses the influence of organizational size, sector, and cybersecurity strategies on cyberattack impacts.
-Utilizing a dataset from the University of Queensland about data breaches and ransomware attacks from 2004 to 2019, we analyze the trends and correlations and study how different factors contribute to the severity and frequency of these incidents.
-Our analysis reveals key insights: larger organizations report more cyber incidents, sectors like healthcare and education are frequent targets, and cybersecurity frameworks significantly help in reducing the user impact.
-These findings highlight critical areas for how organizations can improve their security and protect their data."
-header-includes:
-   - \usepackage{tikz}
-   - \usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, calc}
-   - \usepackage{pgfplots} 
-   - \usepackage{float}
-   - \usepackage{booktabs}
-   - \usepackage{longtable}
-
+number-sections: true
 format: pdf
-number-sections: true
-bibliography: references.bib
-toc: true
 ---
@@
 library(tidyverse)
-library(readxl)
+library(janitor)
 library(here)
+library(lubridate)
+library(arrow)
+library(dplyr)
 
-breach_data <- read.csv(here("data/analysis_data/breach_data.csv"))
+clean_data <- read.csv(here("data", "analysis_data", "clean_data.csv"))
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+library(performance)
+library(knitr)
+library(ggplot2)
+
+# Compute summary statistics for all numeric variables
+summary_stats <- clean_data %>%
+  summarise(
+    Mean_GameBefore = mean(game_before, na.rm = TRUE),
+    Median_GameBefore = median(game_before, na.rm = TRUE),
+    SD_GameBefore = sd(game_before, na.rm = TRUE),
+    IQR_GameBefore = IQR(game_before, na.rm = TRUE),
+
+    Mean_GameAfter = mean(game_after, na.rm = TRUE),
+    Median_GameAfter = median(game_after, na.rm = TRUE),
+    SD_GameAfter = sd(game_after, na.rm = TRUE),
+    IQR_GameAfter = IQR(game_after, na.rm = TRUE)
+  )
+
+# Display summary statistics in a table
+knitr::kable(summary_stats, caption = "Summary Statistics for Memory Game Scores")
+
 ```

### 2025-02-27 scripts/01-data_cleaning.R

@@ -16,33 +16,20 @@ library(dplyr)
 #### Clean data ####
 
 # Reading dataset
-breach_data <- read_excel("data/raw_data/Dataset-cyberattacks-06102020.xlsx", sheet = 2)
+df  <- read.csv("data/raw_data/STA305 Dataset.csv")
+df$name <- trimws(df$name)  # Removes extra spaces
+df$drug_dosage <- trimws(df$drug_dosage)  # Cleans up drug_dosage
 
-# Simplifying names
-breach_data <- clean_names(breach_data)
+sum(is.na(df$name))  # Check for missing names before split
 
 
-# Ensure 'attack_type' is treated as a character
-breach_data$attack_type <- as.character(breach_data$attack_type)
+# Separate the 'drug_dosage' column into 'drug' and 'dosage_level'
+df <- df %>%
+  separate(drug_dosage, into = c("drug", "dosage_level"), sep = "_") %>%
+  select(name, drug, dosage_level, everything())  # Reorder columns
 
-# Replace both NA values and "NA" strings with "Unknown" in 'attack_type' column
-breach_data <- breach_data %>%
-  mutate(attack_type = ifelse(is.na(attack_type) | attack_type == "NA", "Unknown", attack_type))
-
-# Replace both NA values and "NA" strings with "Unknown" in 'organisation_size' column
-breach_data <- breach_data %>%
-  mutate(organisation_size = ifelse(is.na(organisation_size) | organisation_size == "NA", "Unknown", organisation_size))
-breach_data <- breach_data %>%
-  filter(number_of_users_affected != "Missing")
-
-# Convert 'number_of_users_affected' to numeric, handling non-numeric cases
-breach_data$number_of_users_affected <- as.numeric(as.character(breach_data$number_of_users_affected))
-
-# Remove unwanted columns
-# Remove unwanted columns using dplyr::select to avoid any masking issues
-breach_data <- dplyr::select(breach_data, -c(summary, effect_on_share_price, inappropriate_remote_access))
-
+sum(is.na(df$name))  # Check for missing names before split
 
 # Saving cleaned data
-write.csv(breach_data, file = "data/analysis_data/breach_data.csv", row.names = FALSE)
-write_parquet(breach_data, "data/analysis_data/breach_data.parquet")
+write.csv(df, file = "data/analysis_data/clean_data.csv", row.names = FALSE)
+

### 2025-02-27 paper/EDA.qmd
Sumamry table

@@
 library(dplyr)
+library(knitr)
+library(performance)
 
 clean_data <- read.csv(here("data", "analysis_data", "clean_data.csv"))
+
 ```
@@
 ```{r}
-#| include: false
+#| echo: true
+#| message: false
 #| warning: false
-#| message: false
+#| results: asis
 
-library(performance)
-library(knitr)
-library(ggplot2)
+# Compute summary statistics individually
+m1_game_before <- mean(clean_data$game_before, na.rm = TRUE)
+m2_game_before <- median(clean_data$game_before, na.rm = TRUE)
+m3_game_before <- sd(clean_data$game_before, na.rm = TRUE)
+m4_game_before <- IQR(clean_data$game_before, na.rm = TRUE)
 
-# Compute summary statistics for all numeric variables
-summary_stats <- clean_data %>%
-  summarise(
-    Mean_GameBefore = mean(game_before, na.rm = TRUE),
-    Median_GameBefore = median(game_before, na.rm = TRUE),
-    SD_GameBefore = sd(game_before, na.rm = TRUE),
-    IQR_GameBefore = IQR(game_before, na.rm = TRUE),
+m1_game_after <- mean(clean_data$game_after, na.rm = TRUE)
+m2_game_after <- median(clean_data$game_after, na.rm = TRUE)
+m3_game_after <- sd(clean_data$game_after, na.rm = TRUE)
+m4_game_after <- IQR(clean_data$game_after, na.rm = TRUE)
 
-    Mean_GameAfter = mean(game_after, na.rm = TRUE),
-    Median_GameAfter = median(game_after, na.rm = TRUE),
-    SD_GameAfter = sd(game_after, na.rm = TRUE),
-    IQR_GameAfter = IQR(game_after, na.rm = TRUE)
+m1_cards_before <- mean(clean_data$cards_before, na.rm = TRUE)
+m2_cards_before <- median(clean_data$cards_before, na.rm = TRUE)
+m3_cards_before <- sd(clean_data$cards_before, na.rm = TRUE)
+m4_cards_before <- IQR(clean_data$cards_before, na.rm = TRUE)
+
+m1_cards_after <- mean(clean_data$cards_after, na.rm = TRUE)
+m2_cards_after <- median(clean_data$cards_after, na.rm = TRUE)
+m3_cards_after <- sd(clean_data$cards_after, na.rm = TRUE)
+m4_cards_after <- IQR(clean_data$cards_after, na.rm = TRUE)
+
+# Combine into a table
+summary_table <- data.frame(
+  Statistic = c("Mean", "Median", "SD", "IQR"),
+  Game_Before = c(m1_game_before, m2_game_before, m3_game_before, m4_game_before),
+  Game_After = c(m1_game_after, m2_game_after, m3_game_after, m4_game_after),
+  Cards_Before = c(m1_cards_before, m2_cards_before, m3_cards_before, m4_cards_before),
+  Cards_After = c(m1_cards_after, m2_cards_after, m3_cards_after, m4_cards_after)
 )
 
-# Display summary statistics in a table
-knitr::kable(summary_stats, caption = "Summary Statistics for Memory Game Scores")
+# Ensure the table prints correctly
+print(summary_table)
 
+# Display formatted table using kable
+kable(summary_table, 
+      caption = "Summary Statistics for Quantitative Variables",
+      align = "c") |> print()
 ```
@@
 
-Therefore, in response to such attacks, there is a need for a plan, that not just keep the intruder or hackers out but also quickly alert if an attack does happen.
-Our study looks at cyber resilience, which is “ the ability to anticipate, withstand, recover from, and adapt to adverse conditions, stresses, attacks, or compromises on systems that use or are enabled by cyber resources.” as defined by National Institute of Standards and Technology [@NISTGlossary2023].
-We break our study into three major research questions, which forms the thesis of our study:
-
-**RQ1**: How do organizational factors such as size and sector, influence the severity of cyber breaches experienced by companies?
-
-**RQ2**: Which cybersecurity strategies, including frameworks, policies, and preventive measures, are the most effective one, in reducing the damage caused by cyber attacks?
-
-**RQ3**: In what ways do the industry type and digital dependence of a business affect the overall impact of a cyber attack, in terms of preserving confidentiality, integrity and availability of data?
-
-We also plotted a bar graph @fig-sector to count the number of incidents across various sectors.
-The bar chart clearly indicates that the 'Human Health Activities' sector has the highest count of incidents, standing out significantly from the other sectors.
-This might suggest that health sector is a more frequent target for cyber incidents or probably it is more diligent in reporting such events.
-The other sectors show a range of incident counts, with most appearing to have far fewer incidents in comparison.
-This could point to different levels of risk exposure, varying security measures, or reporting practices across these sectors.
-
 \newpage

### 2025-02-27 paper/EDA.qmd
Sumamry stats

@@
 ```{r}
-#| echo: true
-#| message: false
-#| warning: false
-#| results: asis
+#| echo: false
 
-# Compute summary statistics individually
 m1_game_before <- mean(clean_data$game_before, na.rm = TRUE)
@@
 
-# Combine into a table
 summary_table <- data.frame(
@@
 
-# Ensure the table prints correctly
-print(summary_table)
-
-# Display formatted table using kable
 kable(summary_table, 

### 2025-02-27 paper/EDA.qmd
Summary tables for qualitative and quantitative variables

--- 2025-02-27 paper/EDA.qmd
@@
 ```{r}
-#| echo: true
+#| echo: false
+#| warning: false
 #| message: false
-#| warning: false
-#| results: asis
 
-# Compute summary statistics individually
+# References:
+# https://tellingstorieswithdata.com/
+# https://q.utoronto.ca/courses/376099/pages/project-descriptions?module_item_id=6379323
+
+library(kableExtra)
+
 m1_game_before <- mean(clean_data$game_before, na.rm = TRUE)
@@
 
-# Ensure the table prints correctly
-print(summary_table)
-
-# Display formatted table using kable
-kable(summary_table, 
-      caption = "Summary Statistics for Quantitative Variables",
-      align = "c") |> print()
+kable(summary_table, format = "latex", booktabs = TRUE, caption = "Summary Statistics for Quantitative Variables") %>%
+  kable_styling(latex_options = c("striped", "hold_position"))
 ```
@@
 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
+# Count and percentage for Drug
+drug_counts <- table(clean_data$drug)
+drug_percentages <- prop.table(drug_counts) * 100
+drug_summary <- data.frame(Drug = names(drug_counts), Count = as.numeric(drug_counts), Percentage = round(drug_percentages, 2))
+
+# Count and percentage for Dosage Level
+dosage_counts <- table(clean_data$dosage_level)
+dosage_percentages <- prop.table(dosage_counts) * 100
+dosage_summary <- data.frame(Dosage = names(dosage_counts), Count = as.numeric(dosage_counts), Percentage = round(dosage_percentages, 2))
+
+# Count and percentage for Location
+location_counts <- table(clean_data$location)
+location_percentages <- prop.table(location_counts) * 100
+location_summary <- data.frame(Location = names(location_counts), Count = as.numeric(location_counts), Percentage = round(location_percentages, 2))
+
+# Count and percentage for Age Group
+age_counts <- table(clean_data$age_group)
+age_percentages <- prop.table(age_counts) * 100
+age_summary <- data.frame(Age_Group = names(age_counts), Count = as.numeric(age_counts), Percentage = round(age_percentages, 2))
+
+kable(drug_summary, format = "latex", booktabs = TRUE, caption = "Summary of Drug Types") %>%
+  kable_styling(latex_options = c("striped", "hold_position"))
+
+kable(dosage_summary, format = "latex", booktabs = TRUE, caption = "Summary of Dosage Levels") %>%
+  kable_styling(latex_options = c("striped", "hold_position"))
+
+kable(location_summary, format = "latex", booktabs = TRUE, caption = "Summary of Locations") %>%
+  kable_styling(latex_options = c("striped", "hold_position"))
+
+kable(age_summary, format = "latex", booktabs = TRUE, caption = "Summary of Age Groups") %>%
+  kable_styling(latex_options = c("striped", "hold_position"))
+
+```
+
 \newpage

### 2025-02-27 paper/EDA.qmd
box plot for result before and after the game

--- 2025-02-27 paper/EDA.qmd
@@
 
-# Ensure the table prints correctly
-print(summary_table)
-
-# Display formatted table using kable
-kable(summary_table, 
-      caption = "Summary Statistics for Quantitative Variables",
-      align = "c") |> print()
+kable(summary_table, format = "latex", booktabs = TRUE, caption = "Summary Statistics for Quantitative Variables") 
 ```
@@
 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
+# Count and percentage for Drug
+drug_counts <- table(clean_data$drug)
+drug_percentages <- prop.table(drug_counts) * 100
+drug_summary <- data.frame(Drug = names(drug_counts), Count = as.numeric(drug_counts), Percentage = round(as.numeric(drug_percentages), 2))
+colnames(drug_summary) <- c("Drug", "Count", "Percentage")
+
+# Count and percentage for Dosage Level
+dosage_counts <- table(clean_data$dosage_level)
+dosage_percentages <- prop.table(dosage_counts) * 100
+dosage_summary <- data.frame(Dosage = names(dosage_counts), Count = as.numeric(dosage_counts), Percentage = round(as.numeric(dosage_percentages), 2))
+
+# Count and percentage for Location
+location_counts <- table(clean_data$location)
+location_percentages <- prop.table(location_counts) * 100
+location_summary <- data.frame(Location = names(location_counts), Count = as.numeric(location_counts), Percentage = round(as.numeric(location_percentages), 2))
+
+# Count and percentage for Age Group
+age_counts <- table(clean_data$age_group)
+age_percentages <- prop.table(age_counts) * 100
+age_summary <- data.frame(Age_Group = names(age_counts), Count = as.numeric(age_counts), Percentage = round(as.numeric(age_percentages), 2))
+
+# Print tables
+kable(drug_summary, format = "latex", booktabs = TRUE, caption = "Summary of Drug Types")
+
+kable(dosage_summary, format = "latex", booktabs = TRUE, caption = "Summary of Dosage Levels")
+
+kable(location_summary, format = "latex", booktabs = TRUE, caption = "Summary of Locations")
+
+kable(age_summary, format = "latex", booktabs = TRUE, caption = "Summary of Age Groups") 
+```
+
 \newpage
 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Boxplot of Game Scores Before and After by Drug"
+
+library(ggplot2)
+library(patchwork)  # For combining plots
+
+# Capitalize legend labels
+clean_data$drug <- factor(clean_data$drug, labels = c("Aspirin", "Paracetamol", "Placebo", "Tramadol"))
+
+# Create first boxplot
+p1 <- ggplot(clean_data, aes(x = drug, y = game_before, fill = drug)) + 
+  geom_boxplot() +
+  labs(title = "Game Scores Before Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
+  theme_minimal()
+
+# Create second boxplot
+p2 <- ggplot(clean_data, aes(x = drug, y = game_after, fill = drug)) + 
+  geom_boxplot() +
+  labs(title = "Game Scores After Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
+  theme_minimal()
+
+# Combine both plots with a single caption
+p1 / p2 + plot_annotation()
+
+```
+
 # References

### 2025-02-27 scripts/01-data_cleaning.R

@@ -13,6 +13,8 @@ library(readxl)
 library(arrow)
 library(dplyr)
 
+library(stringr)  
+
 #### Clean data ####
 
 # Reading dataset
@@ -28,7 +30,13 @@ df <- df %>%
   separate(drug_dosage, into = c("drug", "dosage_level"), sep = "_") %>%
   select(name, drug, dosage_level, everything())  # Reorder columns
 
-sum(is.na(df$name))  # Check for missing names before split
+
+
+# Convert first letter of categorical variables to uppercase
+df$drug <- str_to_title(df$drug)
+df$dosage_level <- str_to_title(df$dosage_level)
+df$location <- str_to_title(df$location)
+df$age_group <- str_to_title(df$age_group)
 
 # Saving cleaned data
 write.csv(df, file = "data/analysis_data/clean_data.csv", row.names = FALSE)

### 2025-02-27 paper/EDA.qmd
Adding plots

@@
 library(performance)
+library(kableExtra)
 
 clean_data <- read.csv(here("data", "analysis_data", "clean_data.csv"))
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
+clean_data$improvement <- clean_data$game_after - clean_data$game_before
+
+improvement_summary <- clean_data %>%
+  group_by(drug) %>%
+  summarise(
+    Mean_Improvement = mean(improvement, na.rm = TRUE),
+    SD_Improvement = sd(improvement, na.rm = TRUE),
+    Median_Improvement = median(improvement, na.rm = TRUE)
+  )
+
+kable(improvement_summary, format = "latex", booktabs = TRUE, caption = "Mean Improvement in Game Scores by Drug")
 
@@
 # https://q.utoronto.ca/courses/376099/pages/project-descriptions?module_item_id=6379323
-
-library(kableExtra)
 
@@
 library(ggplot2)
-library(patchwork)  # For combining plots
+library(patchwork)
 
-# Capitalize legend labels
+#References
+#https://r-graph-gallery.com/package/patchwork.html
+
 clean_data$drug <- factor(clean_data$drug, labels = c("Aspirin", "Paracetamol", "Placebo", "Tramadol"))
@@
   geom_boxplot() +
-  labs(title = "Game Scores Before Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
+  labs(title = "Memory Game Scores Before Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
   theme_minimal()
@@
   geom_boxplot() +
-  labs(title = "Game Scores After Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
+  labs(title = "Memory Game Scores After Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
   theme_minimal()
 
-# Combine both plots with a single caption
 p1 / p2 + plot_annotation()
@@
 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Boxplot of Memory Card Scores Before and After by Drug"
+
+library(ggplot2)
+library(patchwork)
+
+clean_data$drug <- factor(clean_data$drug, labels = c("Aspirin", "Paracetamol", "Placebo", "Tramadol"))
+
+p1 <- ggplot(clean_data, aes(x = drug, y = cards_before, fill = drug)) + 
+  geom_boxplot() +
+  labs(title = "Memory Card Scores Before Treatment", x = "Drug Type", y = "Memory Card Score", fill = "Drug") +
+  theme_minimal()
+
+p2 <- ggplot(clean_data, aes(x = drug, y = cards_after, fill = drug)) + 
+  geom_boxplot() +
+  labs(title = "Memory Card Scores After Treatment", x = "Drug Type", y = "Memory Card Score", fill = "Drug") +
+  theme_minimal()
+
+p1 / p2 + plot_annotation()
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 7
+#| fig.height: 4
+#| dpi: 300
+#| fig-cap: "Distribution of Dosage Levels"
+
+ggplot(clean_data, aes(x = dosage_level, fill = dosage_level)) +
+  geom_bar() +
+  labs(title = "Distribution of Dosage Levels", x = "Dosage Level", y = "Count") +
+  theme_minimal()
+
+```
+
 # References

### 2025-02-28 paper/EDA.qmd
Added Install Packges for instruction when running the code. Use it via unmarking #hastage signs. Another note Added Graph for tesing Homogeneity of  Vaiance & Normality and made graph

@@
 
+# Make sure Packages are installed
+
+# install.packages("tidyverse")
+# install.packages("janitor")
+# install.packages("here")
+# install.packages("lubridate")
+# install.packages("arrow")
+# install.packages("dplyr")
+# install.packages("knitr")
+# install.packages("performance")
+# install.packages("kableExtra")
+# install.packages("performance")
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
 library(tidyverse)
@@
 library(kableExtra)
+library(performance)
 
@@
 
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Assumption Check for Time taken after taking the Drug"
+
+# Fit ANOVA Model
+model <- aov(game_after ~ drug, data = clean_data)
+
+# Check Model Assumptions
+check_model(model, check = c("normality", "homogeneity"))
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+# Barlett Test Homegenity of Variance: testing for ass
+# bartlett_test <- bartlett.test(game_after ~ drug, data = clean_data)
+# print(bartlett_test)
 ```

### 2025-02-28 paper/EDA.qmd
Adding Assumtion graph Time Take in Second for Game for before and after Taking drug

@@
 # print(bartlett_test)
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Assumption Check for Time taken before taking the Drug"
+
+# Fit ANOVA Model
+model_b <- aov(game_before ~ drug, data = clean_data)
+
+# Check Model Assumptions
+check_model(model_b, check = c("normality", "homogeneity"))
 ```

### 2025-02-28 paper/EDA.qmd
Write up started

@@
 title: "Effects of Different Pain Relievers and Dosages on Cognitive Retention"
+subtitle: "Exploratory Data Analysis (EDA)"
 author: 
@@
 
-```{r}
-#| include: false
-#| warning: false
-#| message: false
+# Introduction
 
-# Make sure Packages are installed
+## Relevant Background
+Pain can affect how well we perform everyday tasks in situations where focus and mental clarity
+are crucial. Aspirin, Paracetamol, and Tramadol are pain relievers used commonly to reduce
+physical discomfort, but we don’t know much about their impacts on cognitive functions. Tasks
+requiring mental effort, such as recalling information, are harder to perform while in pain.
+This study is interested in how different types of common pain relievers at standard dosages
+(Aspirin, Paracetamol, and Tramadol) may affect outcomes of tasks involving memory tests. We
+also analyze the effects of different dosages of each drug on memory function. The concept of
+recalling information is used in various settings, so understanding how pain relief can impact
+performance can be valuable to help with pain management without an impact on productivity.
 
-# install.packages("tidyverse")
-# install.packages("janitor")
-# install.packages("here")
-# install.packages("lubridate")
-# install.packages("arrow")
-# install.packages("dplyr")
-# install.packages("knitr")
-# install.packages("performance")
-# install.packages("kableExtra")
-# install.packages("performance")
-```
+## Research Questions
+1. *How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg, and Placebo) affect cognitive task performance?*
+2. *How does the dosage (low vs. high) of each drug affect cognitive retention, while accounting for confounding factors like age?*
+
+## Study Design  
+This study involves *7 treatment groups*, with **30 participants** assigned to each. The groups are as follows:
+
+1. Aspirin 500 mg
+2. Aspirin 1000 mg
+3. Paracetamol 500 mg
+4. Paracetamol 1000 mg
+5. Tramadol 50 mg
+6. Tramadol 100 mg
+7. Placebo
+
+This results in **210 total observations** (7 × 30 = 210).
+
+## Confounding Variable: Age  
+To reduce variability, we consider **age** as a **confounding variable**. Participants will be categorized into three groups:
+
+1. 18–34 years
+2. 35–50 years
+3. 50+ years
+
+## Data Analysis Method   
+We will use **one-way ANOVA** to analyze the effects of pain reliever type on memory performance.
+and dosage levels on cognitive retention.
 
@@
 
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| fig.width: 9
-#| fig.height: 8
-#| dpi: 300
-#| fig-cap: "Assumption Check for Time taken after taking the Drug"
+# Summary Statistics
 
-# Fit ANOVA Model
-model <- aov(game_after ~ drug, data = clean_data)
+## Summary of quantitative variables
 
-# Check Model Assumptions
-check_model(model, check = c("normality", "homogeneity"))
-```
+@tbl-summary-1 shows the summary statistics of game scores before and after treatment.
+The mean is similar across all groups, indicating no extreme changes in cognitive performance.
+However, the standard deviation (SD) is relatively high, suggesting some variation among participants.
 
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-# Barlett Test Homegenity of Variance: testing for ass
-# bartlett_test <- bartlett.test(game_after ~ drug, data = clean_data)
-# print(bartlett_test)
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| fig.width: 9
-#| fig.height: 8
-#| dpi: 300
-#| fig-cap: "Assumption Check for Time taken before taking the Drug"
-
-# Fit ANOVA Model
-model_b <- aov(game_before ~ drug, data = clean_data)
-
-# Check Model Assumptions
-check_model(model_b, check = c("normality", "homogeneity"))
-```
+- The median game scores remain close to the mean, showing a nearly symmetric distribution.
+- The IQR (Interquartile Range) is smaller than the SD, meaning there may be outliers.
+- The cards memory task shows little change before and after treatment, suggesting that pain relievers may not have a major effect on this specific task.
 
@@
 ```{r}
+#| label: tbl-summary-1
 #| echo: false
@@
 ```
-
-# Introduction
 
@@
 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Assumption Check for Time taken after taking the Drug"
+
+# Fit ANOVA Model
+model <- aov(game_after ~ drug, data = clean_data)
+
+# Check Model Assumptions
+check_model(model, check = c("normality", "homogeneity"))
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+# Barlett Test Homegenity of Variance: testing for ass
+# bartlett_test <- bartlett.test(game_after ~ drug, data = clean_data)
+# print(bartlett_test)
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Assumption Check for Time taken before taking the Drug"
+
+# Fit ANOVA Model
+model_b <- aov(game_before ~ drug, data = clean_data)
+
+# Check Model Assumptions
+check_model(model_b, check = c("normality", "homogeneity"))
+```
+
 # References

### 2025-02-28 paper/EDA.qmd
Write up done for summary stats

@@
 
-@tbl-summary-1 shows the summary statistics of game scores before and after treatment.
+@tbl-summary-1 shows the summary statistics of memory game scores before and after the treatment.
 The mean is similar across all groups, indicating no extreme changes in cognitive performance.
@@
 ```{r}
-#| echo: false
-#| warning: false
-#| message: false
-
-clean_data$improvement <- clean_data$game_after - clean_data$game_before
-
-improvement_summary <- clean_data %>%
-  group_by(drug) %>%
-  summarise(
-    Mean_Improvement = mean(improvement, na.rm = TRUE),
-    SD_Improvement = sd(improvement, na.rm = TRUE),
-    Median_Improvement = median(improvement, na.rm = TRUE)
-  )
-
-kable(improvement_summary, format = "latex", booktabs = TRUE, caption = "Mean Improvement in Game Scores by Drug")
-
-```
-
-```{r}
 #| label: tbl-summary-1
+#| tbl-cap: "Summary Statistics for Quantitative Variables"
 #| echo: false
@@
 
-kable(summary_table, format = "latex", booktabs = TRUE, caption = "Summary Statistics for Quantitative Variables") 
+kable(summary_table, format = "latex", booktabs = TRUE) 
 ```
 
+## Summary of counts and percentage for qualitative variables
+
+@tbl-summary-2 shows the distribution of participants across drug types.
+Aspirin, Paracetamol, and Tramadol each have 60 participants (28.57\%), ensuring balance.
+However, the Placebo group is smaller (30 participants, 14.29\%).
+
+@tbl-summary-3 shows the dosage levels assigned to participants. There is an equal split between high-dose (90 participants, 50\%) and low-dose (90 participants, 50\%) conditions.
+
+@tbl-summary-4 provides an overview of participant locations.
+The distribution is relatively even across six different locations, with each site having either 30 (14.29\%) or 60 (28.57\%) participants.
+
+## Confounding Variable
+
+@tbl-summary-5 shows the breakdown of age groups, which is a confounding variable in this study. The three age groups: 18–34, 35–50, and 50+ each have 70 participants (33.33\%).
+
 ```{r}
+#| label: tbl-summary-2
+#| tbl-cap: "Summary of Drug Types"
 #| echo: false
@@
 colnames(drug_summary) <- c("Drug", "Count", "Percentage")
+kable(drug_summary, format = "latex", booktabs = TRUE)
+
+```
+
+```{r}
+#| label: tbl-summary-3
+#| tbl-cap: "Summary of Dosage Levels"
+#| echo: false
+#| warning: false
+#| message: false
 
@@
 
+kable(dosage_summary, format = "latex", booktabs = TRUE)
+
+```
+
+```{r}
+#| label: tbl-summary-4
+#| tbl-cap: "Summary of Locations"
+#| echo: false
+#| warning: false
+#| message: false
+
 # Count and percentage for Location
@@
 location_summary <- data.frame(Location = names(location_counts), Count = as.numeric(location_counts), Percentage = round(as.numeric(location_percentages), 2))
+
+kable(location_summary, format = "latex", booktabs = TRUE)
+
+```
+
+```{r}
+#| label: tbl-summary-5
+#| tbl-cap: "Summary of Age Groups"
+#| echo: false
+#| warning: false
+#| message: false
 
@@
 
-# Print tables
-kable(drug_summary, format = "latex", booktabs = TRUE, caption = "Summary of Drug Types")
+kable(age_summary, format = "latex", booktabs = TRUE) 
+```
 
-kable(dosage_summary, format = "latex", booktabs = TRUE, caption = "Summary of Dosage Levels")
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
 
-kable(location_summary, format = "latex", booktabs = TRUE, caption = "Summary of Locations")
+clean_data$improvement <- clean_data$game_after - clean_data$game_before
 
-kable(age_summary, format = "latex", booktabs = TRUE, caption = "Summary of Age Groups") 
+improvement_summary <- clean_data %>%
+  group_by(drug) %>%
+  summarise(
+    Mean_Improvement = mean(improvement, na.rm = TRUE),
+    SD_Improvement = sd(improvement, na.rm = TRUE),
+    Median_Improvement = median(improvement, na.rm = TRUE)
+  )
+
+kable(improvement_summary, format = "latex", booktabs = TRUE, caption = "Mean Improvement in Game Scores by Drug")
+
 ```

### 2025-02-28 paper/EDA.qmd
Write up for plots

@@
 @tbl-summary-1 shows the summary statistics of memory game scores before and after the treatment.
-The mean is similar across all groups, indicating no extreme changes in cognitive performance.
-However, the standard deviation (SD) is relatively high, suggesting some variation among participants.
-
-- The median game scores remain close to the mean, showing a nearly symmetric distribution.
-- The IQR (Interquartile Range) is smaller than the SD, meaning there may be outliers.
-- The cards memory task shows little change before and after treatment, suggesting that pain relievers may not have a major effect on this specific task.
+The mean is similar across all groups, however, the standard deviation (SD) is relatively high.
+The median game scores remain close to the mean, and the IQR (Interquartile Range) is smaller than the SD.
+The cards memory task shows little change before and after treatment, suggesting that pain relievers may not have a major effect on this specific task.
 
@@
 
-\newpage
+# Plots
+
+## Game Score Distribution Before and After Treatment
+
+@fig-boxplot-scores shows the distribution of memory game scores before and after treatment across different drug types using box plots.
+
+1. The median scores for all drugs appear similar before treatment.
+2. **Tramadol has a higher median** than other drugs both before and after treatment.
+3. The **Placebo group has a slightly lower median score** compared to other drugs.
+4. There is **one outlier in the Tramadol group before treatment**.
+5. The (IQR) is **similar across all drug types**.
+
+These boxplots provide an initial comparison of cognitive performance changes before and after drug administration.
 
 ```{r}
+#| label: fig-boxplot-scores
 #| echo: false
@@
 #| dpi: 300
-#| fig-cap: "Boxplot of Game Scores Before and After by Drug"
+#| fig-cap: "Boxplot of Memory Game Scores Before and After Treatment by Drug Type"
 
@@
 
+## Memory Card Score Distribution Before and After Treatment
+
+@fig-boxplot-cards shows the distribution of **memory card scores before and after treatment** across drug types.
+
+1. Before treatment, the scores are relatively high across all groups, with Paracetamol and Placebo showing slightly higher medians than the others.
+2. After treatment, the distributions remain similar, though there is a slight increase in spread  for Aspirin and Paracetamol.
+3. Outliers are present in all groups, indicating some variability in memory card performance across individuals.
+
 ```{r}
+#| label: fig-boxplot-cards
 #| echo: false

### 2025-03-02 paper/EDA.qmd
Updated dataset

@@
 format: pdf
+bibliography: references.bib
 ---
@@
 
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| fig.width: 9
-#| fig.height: 8
-#| dpi: 300
-#| fig-cap: "Assumption Check for Time taken after taking the Drug"
-
-# Fit ANOVA Model
-model <- aov(game_after ~ drug, data = clean_data)
-
-# Check Model Assumptions
-check_model(model, check = c("normality", "homogeneity"))
-```
+# Assumptions
 
@@
 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Assumption Check for Time taken after taking the Drug"
+
+# Fit ANOVA Model
+model <- aov(game_after ~ drug, data = clean_data)
+
+# Check Model Assumptions
+check_model(model, check = c("normality", "homogeneity"))
+```
+
 # References

### 2025-03-02 paper/EDA.qmd
Updates Install Package file
Assumption check complete recovered file

@@
 ---
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+# install.packages(c("tidyverse", "janitor", "here", "lubridate", "arrow", "dplyr", 
+#   "knitr", "performance", "kableExtra", #"ggpubr"))
+
+```
 
@@
 library(performance)
+library(ggpubr)
 
@@
 #| message: false
+
+# Note from pdf
+"In the performance package, it would alert you in red if any assumptions were heavily violated. If you noticed
+any, it would be useful to mention them.
+Unfortunately it is hard to create non-parametric versions. So if there is a violation for the sake of this
+course it is fine to mention there is a violation but you will proceed as if everything was fine."
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Assumption Check for Time taken after taking the Drug"
+
+# Fit ANOVA Model
+model <- aov(game_after ~ drug, data = clean_data)
+
+# Check Model Assumptions
+check_model(model, check = c("normality", "homogeneity"))
+
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
 # Barlett Test Homegenity of Variance: testing for ass
@@
 # print(bartlett_test)
+
 ```
@@
 check_model(model_b, check = c("normality", "homogeneity"))
+
 ```
@@
 #| message: false
-#| fig.width: 9
-#| fig.height: 8
-#| dpi: 300
-#| fig-cap: "Assumption Check for Time taken after taking the Drug"
+# Boxplot to visualize the distribution of `game_after`
+ggplot(clean_data, aes(x = drug, y = game_after, fill = dosage_level)) +
+  geom_boxplot() +
+  ggtitle("Boxplot of Game After Scores by Drug and Dosage Level")
 
-# Fit ANOVA Model
-model <- aov(game_after ~ drug, data = clean_data)
+```
 
-# Check Model Assumptions
-check_model(model, check = c("normality", "homogeneity"))
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
+anova_model <- aov(game_after ~ drug + dosage_level, data = clean_data)
+summary(anova_model)
+# install.packages("ggpubr")
+# QQ plot for residuals
+ggqqplot(residuals(anova_model))
+
+# Sharpio Test
+shapiro.test(residuals(anova_model))
+# p-value is greater than 0.05 we fail to reject Ho implies Normality
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
+model_cards_dose <- aov(cards_after ~ drug + dosage_level, data = clean_data)
+shapiro.test(residuals(model_cards_dose))
+ggqqplot(residuals(model_cards_dose))
 ```

### 2025-03-02 paper/EDA.qmd
Assumption check completed

@@
 
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 6
+#| fig.height: 4
+#| fig-cap: "Time Taken for Memory Game after taking Drugs"
+
+# Boxplot to visualize the distribution of time taken to solve Memory game after taking pain killers
+ggplot(clean_data, aes(x = drug, y = game_after, fill = dosage_level)) +
+  geom_boxplot() +
+  ggtitle("Time Taken for Memory Game after taking Drugs")
+
+```
+
 # Assumptions
@@
 course it is fine to mention there is a violation but you will proceed as if everything was fine."
-
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| fig.width: 9
-#| fig.height: 8
-#| dpi: 300
-#| fig-cap: "Assumption Check for Time taken after taking the Drug"
-
-# Fit ANOVA Model
-model <- aov(game_after ~ drug, data = clean_data)
-
-# Check Model Assumptions
-check_model(model, check = c("normality", "homogeneity"))
 
@@
 #| message: false
-#| fig.width: 9
-#| fig.height: 8
-#| dpi: 300
-#| fig-cap: "Assumption Check for Time taken before taking the Drug"
+#| fig.width: 6
+#| fig.height: 4
+#| fig-cap: "Time Taken for Memory Game after taking Drugs"
 
-# Fit ANOVA Model
-model_b <- aov(game_before ~ drug, data = clean_data)
+# we fit One-Way ANOVA Model for our research question 1
+model_1 <- aov(game_after ~ drug, data = clean_data)
 
 # Check Model Assumptions
-check_model(model_b, check = c("normality", "homogeneity"))
+check_model(model_1, check = c("normality", "homogeneity"))
+
+summary(model_1)
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+# bartlett_test_part1 <- bartlett.test(game_after ~ drug, data = clean_data)
+# print(bartlett_test_part1)
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 6
+#| fig.height: 4
+#| fig-cap: "Residual Plot Model 1"
+
+# QQ plot for Normality assumption
+ggqqplot(residuals(model_1)) +
+  ggtitle("QQ Plot for Residuals Model 1")
+
+# Shapiro-Wilk Tet
+# shapiro_test <- shapiro.test(residuals(model_1))
+# print(shapiro_test)
 
@@
 #| message: false
-# Boxplot to visualize the distribution of `game_after`
-ggplot(clean_data, aes(x = drug, y = game_after, fill = dosage_level)) +
-  geom_boxplot() +
-  ggtitle("Boxplot of Game After Scores by Drug and Dosage Level")
+#| fig.width: 6
+#| fig.height: 4
+#| fig-cap: "Normality & Homegenity"
+
+# Corrected Two-Way ANOVA Model for our reseearch question 2
+model_2 <- aov(game_after ~ drug + dosage_level, data = clean_data)
+
+# Check Model Assumptions
+check_model(model_2, check = c("normality", "homogeneity"))
 
@@
 
-anova_model <- aov(game_after ~ drug + dosage_level, data = clean_data)
-summary(anova_model)
-# install.packages("ggpubr")
-# QQ plot for residuals
-ggqqplot(residuals(anova_model))
-
-# Sharpio Test
-shapiro.test(residuals(anova_model))
-# p-value is greater than 0.05 we fail to reject Ho implies Normality
+# Shapiro-Wilk Test for Normality of Residuals
+# shapiro_test_part2 <- shapiro.test(residuals(model_part2))
+# print(shapiro_test_part2)
 
@@
 #| message: false
+#| fig.width: 6
+#| fig.height: 4
+#| fig-cap: "Residual Plot Model"
 
-model_cards_dose <- aov(cards_after ~ drug + dosage_level, data = clean_data)
-shapiro.test(residuals(model_cards_dose))
-ggqqplot(residuals(model_cards_dose))
+# QQ plot for residuals of Part 2
+ggqqplot(residuals(model_2)) +
+  ggtitle("QQ Plot Two-Way ANOVA Model")
+
 ```

### 2025-03-03 paper/EDA.qmd
Latest Changes, with assumptions explained

@@
 ## Study Design  
-This study involves *7 treatment groups*, with **30 participants** assigned to each. The groups are as follows:
+This study involves *8 treatment groups*, with **30 participants** assigned to each. The groups are as follows:
 
-1. Aspirin 500 mg
-2. Aspirin 1000 mg
-3. Paracetamol 500 mg
-4. Paracetamol 1000 mg
-5. Tramadol 50 mg
-6. Tramadol 100 mg
-7. Placebo
+1. Aspirin 500 mg (Low)
+2. Aspirin 1000 mg (High)
+3. Paracetamol 500 mg (Low)
+4. Paracetamol 1000 mg (High)
+5. Tramadol 50 mg (Low)
+6. Tramadol 100 mg (High)
+7. Placebo (Low) 
+8. Placebo (High)
 
-This results in **210 total observations** (7 × 30 = 210).
+This results in **240 total observations** (8 × 30 = 240).
 
@@
 
+## Quantitative and Qualitative Variables 
+In our study the quantitative and qualitative variables are as follows. 
+Quantitative variables: Memory Game Scores, Memory Test Cards Scores 
+Qualitative variables: Type of pain reliever, dosage level (low/high)
+
 ## Data Analysis Method   
-We will use **one-way ANOVA** to analyze the effects of pain reliever type on memory performance.
-and dosage levels on cognitive retention.
+We will use **one-way ANOVA** to analyze the effects of different pain relievers on memory performance
+Similarly, we will use **two-way ANOVA** to analyze the effects of different dosage levels per drug type on memory performance and cognitive retention.
 
@@
 
-@tbl-summary-2 shows the distribution of participants across drug types.
-Aspirin, Paracetamol, and Tramadol each have 60 participants (28.57\%), ensuring balance.
-However, the Placebo group is smaller (30 participants, 14.29\%).
+@tbl-summary-2 shows the distribution of participants across drug types. Aspirin, Paracetamol, and Tramadol, and Placebo each have 60 participants (25\%), ensuring balance.
 
-@tbl-summary-3 shows the dosage levels assigned to participants. There is an equal split between high-dose (90 participants, 50\%) and low-dose (90 participants, 50\%) conditions.
-
-@tbl-summary-4 provides an overview of participant locations.
-The distribution is relatively even across six different locations, with each site having either 30 (14.29\%) or 60 (28.57\%) participants.
+@tbl-summary-3 shows the dosage levels assigned to participants. There is an equal split between high-dose (120 participants, 50\%) and low-dose (120 participants, 50\%) conditions.
 
@@
 
-@tbl-summary-5 shows the breakdown of age groups, which is a confounding variable in this study. The three age groups: 18–34, 35–50, and 50+ each have 70 participants (33.33\%).
+@tbl-summary-5 shows the breakdown of age groups, which is a confounding variable in this study. The three age groups: 18–34, 35–50, and 50+ each have 80 participants (33.33\%).
 
@@
 kable(dosage_summary, format = "latex", booktabs = TRUE)
-
-```
-
-```{r}
-#| label: tbl-summary-4
-#| tbl-cap: "Summary of Locations"
-#| echo: false
-#| warning: false
-#| message: false
-
-# Count and percentage for Location
-location_counts <- table(clean_data$location)
-location_percentages <- prop.table(location_counts) * 100
-location_summary <- data.frame(Location = names(location_counts), Count = as.numeric(location_counts), Percentage = round(as.numeric(location_percentages), 2))
-
-kable(location_summary, format = "latex", booktabs = TRUE)
 
@@
 4. There is **one outlier in the Tramadol group before treatment**.
-5. The (IQR) is **similar across all drug types**.
+5. The (IQR) is **similar across all drug types**, though Tramadol sees a decrease in its IQR in the memory game scores after treatment.
 
@@
 1. Before treatment, the scores are relatively high across all groups, with Paracetamol and Placebo showing slightly higher medians than the others.
-2. After treatment, the distributions remain similar, though there is a slight increase in spread  for Aspirin and Paracetamol.
+2. After treatment, the distributions remain similar, though there is a slight increase in spread for Aspirin, Paracetamol, and Placebo.
+3. There is a slight decrease in the IQR of Tramadol. 
 3. Outliers are present in all groups, indicating some variability in memory card performance across individuals.
@@
 
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| fig.width: 7
-#| fig.height: 4
-#| dpi: 300
-#| fig-cap: "Distribution of Dosage Levels"
-
-ggplot(clean_data, aes(x = dosage_level, fill = dosage_level)) +
-  geom_bar() +
-  labs(title = "Distribution of Dosage Levels", x = "Dosage Level", y = "Count") +
-  theme_minimal()
-
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| fig.width: 6
-#| fig.height: 4
-#| fig-cap: "Time Taken for Memory Game after taking Drugs"
-
-# Boxplot to visualize the distribution of time taken to solve Memory game after taking pain killers
-ggplot(clean_data, aes(x = drug, y = game_after, fill = dosage_level)) +
-  geom_boxplot() +
-  ggtitle("Time Taken for Memory Game after taking Drugs")
-
-```
-
 # Assumptions
@@
 
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-# Barlett Test Homegenity of Variance: testing for ass
-# bartlett_test <- bartlett.test(game_after ~ drug, data = clean_data)
-# print(bartlett_test)
+## Checking Model Assumptions
 
-```
+We assessed the homogeneity of variance and normality of residuals using diagnostic plots to validate the assumptions of our ANOVA tests. (@fig-assump-one & @fig-assump-two).
+
+**One-way ANOVA**
+
+*Independence* For our one-way ANOVA model, we have independence because our observations are independent within and across the groups i.e all participants were randomly assigned a pain reliever, and there was no relationships between observations (i.e repeated  participants, treatments etc.)
+
+*Homogeneity of Variance:* 
+The reference line in @fig-assump-one relatively flat and horizontal which indicates that variance is approximately equal across groups.
+Thus, the assumption of homogeneity of variance is not significantly violated.
+
+*Normality of Residuals:* 
+The residuals are approximately normally distributed in @fig-assump-one since the density plot on the right appears close to a normal distribution.
+
+**Two-way ANOVA**
+
+*Independence*
+For our two-way ANOVA model, the different combinations of pain reliever type and dosage levels were randomly assigned to all participants, in random order.
+
+*Homogeneity of Variance:* 
+In @fig-assump-two the left plot shows some deviation from a perfectly flat line and has minor fluctuations, especially at certain levels of drug type and dosage.
+Despite some variation, the overall trend does not show extreme violations of homogeneity.
+
+*Normality of Residuals:* 
+In @fig-assump-two the density plot on the right shows that the residuals follow a roughly normal distribution even though minor deviations are present.
+
+**Conclusion**
+
+Both models satisfy the assumptions of homogeneity of variance and normality of residuals well enough.
+There are slight deviations in the two-way ANOVA model, but they are not severe enough to invalidate the analysis.
+Therefore, we proceed with the ANOVA tests.
 
 ```{r}
+#| label: fig-assump-one
 #| echo: false
@@
 #| fig.height: 4
-#| fig-cap: "Time Taken for Memory Game after taking Drugs"
+#| fig-cap: "Homogeneity and Normality (One-way ANOVA)"
 
@@
 
-summary(model_1)
 ```
@@
 ```{r}
-#| echo: false
-#| warning: false
-#| message: false
-# bartlett_test_part1 <- bartlett.test(game_after ~ drug, data = clean_data)
-# print(bartlett_test_part1)
-```
-
-```{r}
+#| label: fig-assump-two
 #| echo: false
@@
 #| fig.height: 4
-#| fig-cap: "Residual Plot Model 1"
-
-# QQ plot for Normality assumption
-ggqqplot(residuals(model_1)) +
-  ggtitle("QQ Plot for Residuals Model 1")
-
-# Shapiro-Wilk Tet
-# shapiro_test <- shapiro.test(residuals(model_1))
-# print(shapiro_test)
-
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| fig.width: 6
-#| fig.height: 4
-#| fig-cap: "Normality & Homegenity"
+#| fig-cap: "Normality & Homegenity (Two-way ANOVA)"
 
@@
 ```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-
-# Shapiro-Wilk Test for Normality of Residuals
-# shapiro_test_part2 <- shapiro.test(residuals(model_part2))
-# print(shapiro_test_part2)
-
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| fig.width: 6
-#| fig.height: 4
-#| fig-cap: "Residual Plot Model"
-
-# QQ plot for residuals of Part 2
-ggqqplot(residuals(model_2)) +
-  ggtitle("QQ Plot Two-Way ANOVA Model")
-
-```
-
-# References

### 2025-03-03 paper/EDA.qmd
Final go except update to 1.3 1.4

@@
 ## Data Analysis Method   
-We will use **one-way ANOVA** to analyze the effects of different pain relievers on memory performance
+We will use **one-way ANOVA** to analyze the effects of different pain relievers on memory performance.
 Similarly, we will use **two-way ANOVA** to analyze the effects of different dosage levels per drug type on memory performance and cognitive retention.
@@
 
+Evident through the results on @tbl-summary-6, Paracetamol is the drug that has the greatest mean & median improvement in the game scores after administering the drug (without dosage taken into account).
+Aspirin appears to negatively impact the results of the game after being given to people, this was seen through the mean and median improvements.
+
 ```{r}
+#| label: tbl-summary-6
+#| tbl-cap: "Mean Improvement in Game Scores by Drug"
 #| echo: false
@@
 
-kable(improvement_summary, format = "latex", booktabs = TRUE, caption = "Mean Improvement in Game Scores by Drug")
+kable(improvement_summary, format = "latex", booktabs = TRUE)
 
@@
 
-*Independence* For our one-way ANOVA model, we have independence because our observations are independent within and across the groups i.e all participants were randomly assigned a pain reliever, and there was no relationships between observations (i.e repeated  participants, treatments etc.)
+*Independence:* For our one-way ANOVA model, we have independence because our observations are independent within and across the groups i.e all participants were randomly assigned a pain reliever, and there was no relationships between observations (i.e repeated  participants, treatments etc.)
 
@@
 
-*Independence*
+*Independence:*
 For our two-way ANOVA model, the different combinations of pain reliever type and dosage levels were randomly assigned to all participants, in random order.
@@
 
-# Corrected Two-Way ANOVA Model for our reseearch question 2
+# Corrected Two-Way ANOVA Model for our research question 2
 model_2 <- aov(game_after ~ drug + dosage_level, data = clean_data)
@@
 ```
+
+\newpage
+
+# Appendix
+
+```{r}
+
+library(tidyverse)
+library(janitor)
+library(here)
+library(lubridate)
+library(arrow)
+library(dplyr)
+library(knitr)
+library(performance)
+library(kableExtra)
+library(performance)
+library(ggpubr)
+
+clean_data <- read.csv(here("data", "analysis_data", "clean_data.csv"))
+
+```
+
+```{r}
+
+# References:
+# https://tellingstorieswithdata.com/
+# https://q.utoronto.ca/courses/376099/pages/project-descriptions?module_item_id=6379323
+
+m1_game_before <- mean(clean_data$game_before, na.rm = TRUE)
+m2_game_before <- median(clean_data$game_before, na.rm = TRUE)
+m3_game_before <- sd(clean_data$game_before, na.rm = TRUE)
+m4_game_before <- IQR(clean_data$game_before, na.rm = TRUE)
+
+m1_game_after <- mean(clean_data$game_after, na.rm = TRUE)
+m2_game_after <- median(clean_data$game_after, na.rm = TRUE)
+m3_game_after <- sd(clean_data$game_after, na.rm = TRUE)
+m4_game_after <- IQR(clean_data$game_after, na.rm = TRUE)
+
+m1_cards_before <- mean(clean_data$cards_before, na.rm = TRUE)
+m2_cards_before <- median(clean_data$cards_before, na.rm = TRUE)
+m3_cards_before <- sd(clean_data$cards_before, na.rm = TRUE)
+m4_cards_before <- IQR(clean_data$cards_before, na.rm = TRUE)
+
+m1_cards_after <- mean(clean_data$cards_after, na.rm = TRUE)
+m2_cards_after <- median(clean_data$cards_after, na.rm = TRUE)
+m3_cards_after <- sd(clean_data$cards_after, na.rm = TRUE)
+m4_cards_after <- IQR(clean_data$cards_after, na.rm = TRUE)
+
+# Combine into a table
+summary_table <- data.frame(
+  Statistic = c("Mean", "Median", "SD", "IQR"),
+  Game_Before = c(m1_game_before, m2_game_before, m3_game_before, m4_game_before),
+  Game_After = c(m1_game_after, m2_game_after, m3_game_after, m4_game_after),
+  Cards_Before = c(m1_cards_before, m2_cards_before, m3_cards_before, m4_cards_before),
+  Cards_After = c(m1_cards_after, m2_cards_after, m3_cards_after, m4_cards_after)
+)
+
+kable(summary_table, format = "latex", booktabs = TRUE) 
+```
+
+```{r}
+# Count and percentage for Drug
+drug_counts <- table(clean_data$drug)
+drug_percentages <- prop.table(drug_counts) * 100
+drug_summary <- data.frame(Drug = names(drug_counts), Count = as.numeric(drug_counts), Percentage = round(as.numeric(drug_percentages), 2))
+colnames(drug_summary) <- c("Drug", "Count", "Percentage")
+kable(drug_summary, format = "latex", booktabs = TRUE) 
+```
+
+```{r}
+
+# Count and percentage for Dosage Level
+dosage_counts <- table(clean_data$dosage_level)
+dosage_percentages <- prop.table(dosage_counts) * 100
+dosage_summary <- data.frame(Dosage = names(dosage_counts), Count = as.numeric(dosage_counts), Percentage = round(as.numeric(dosage_percentages), 2))
+
+kable(dosage_summary, format = "latex", booktabs = TRUE)
+
+```
+
+```{r}
+# Count and percentage for Age Group
+age_counts <- table(clean_data$age_group)
+age_percentages <- prop.table(age_counts) * 100
+age_summary <- data.frame(Age_Group = names(age_counts), Count = as.numeric(age_counts), Percentage = round(as.numeric(age_percentages), 2))
+
+kable(age_summary, format = "latex", booktabs = TRUE) 
+```
+
+```{r}
+
+clean_data$improvement <- clean_data$game_after - clean_data$game_before
+
+improvement_summary <- clean_data %>%
+  group_by(drug) %>%
+  summarise(
+    Mean_Improvement = mean(improvement, na.rm = TRUE),
+    SD_Improvement = sd(improvement, na.rm = TRUE),
+    Median_Improvement = median(improvement, na.rm = TRUE)
+  )
+
+kable(improvement_summary, format = "latex", booktabs = TRUE)
+
+```
+
+```{r}
+
+library(ggplot2)
+library(patchwork)
+
+#References
+#https://r-graph-gallery.com/package/patchwork.html
+
+clean_data$drug <- factor(clean_data$drug, labels = c("Aspirin", "Paracetamol", "Placebo", "Tramadol"))
+
+# Create first boxplot
+p1 <- ggplot(clean_data, aes(x = drug, y = game_before, fill = drug)) + 
+  geom_boxplot() +
+  labs(title = "Memory Game Scores Before Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
+  theme_minimal()
+
+# Create second boxplot
+p2 <- ggplot(clean_data, aes(x = drug, y = game_after, fill = drug)) + 
+  geom_boxplot() +
+  labs(title = "Memory Game Scores After Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
+  theme_minimal()
+
+p1 / p2 + plot_annotation()
+```
+
+```{r}
+
+library(ggplot2)
+library(patchwork)
+
+clean_data$drug <- factor(clean_data$drug, labels = c("Aspirin", "Paracetamol", "Placebo", "Tramadol"))
+
+p1 <- ggplot(clean_data, aes(x = drug, y = cards_before, fill = drug)) + 
+  geom_boxplot() +
+  labs(title = "Memory Card Scores Before Treatment", x = "Drug Type", y = "Memory Card Score", fill = "Drug") +
+  theme_minimal()
+
+p2 <- ggplot(clean_data, aes(x = drug, y = cards_after, fill = drug)) + 
+  geom_boxplot() +
+  labs(title = "Memory Card Scores After Treatment", x = "Drug Type", y = "Memory Card Score", fill = "Drug") +
+  theme_minimal()
+
+p1 / p2 + plot_annotation()
+```
+
+```{r}
+
+# we fit One-Way ANOVA Model for our research question 1
+model_1 <- aov(game_after ~ drug, data = clean_data)
+
+# Check Model Assumptions
+check_model(model_1, check = c("normality", "homogeneity"))
+
+```
+
+```{r}
+#| fig.width: 6
+#| fig.height: 4
+#| fig-cap: "Normality & Homegenity (Two-way ANOVA)"
+
+# Corrected Two-Way ANOVA Model for our research question 2
+model_2 <- aov(game_after ~ drug + dosage_level, data = clean_data)
+
+# Check Model Assumptions
+check_model(model_2, check = c("normality", "homogeneity"))
+```

### 2025-03-03 paper/EDA.qmd
Final Changes to EDA

@@
 ## Relevant Background
-Pain can affect how well we perform everyday tasks in situations where focus and mental clarity
-are crucial. Aspirin, Paracetamol, and Tramadol are pain relievers used commonly to reduce
-physical discomfort, but we don’t know much about their impacts on cognitive functions. Tasks
-requiring mental effort, such as recalling information, are harder to perform while in pain.
-This study is interested in how different types of common pain relievers at standard dosages
-(Aspirin, Paracetamol, and Tramadol) may affect outcomes of tasks involving memory tests. We
-also analyze the effects of different dosages of each drug on memory function. The concept of
-recalling information is used in various settings, so understanding how pain relief can impact
-performance can be valuable to help with pain management without an impact on productivity.
+Pain can make everyday tasks harder, particularly when mental focus and clarity are required.
+Common pain relievers like Aspirin, Paracetamol, and Tramadol are often used to reduce physical discomfort, but their impact on cognitive functions is not well understood.
+Recalling information, a task that demands mental effort, becomes more difficult when we're in pain.
+This study investigates how different pain relievers (Aspirin, Paracetamol, and Tramadol) at standard dosages affect memory performance.
+It also looks at how varying dosages of each drug influence memory function.
+Since the ability to recall information is essential in many situations, understanding how pain relief might impact cognitive performance is important for managing pain without affecting productivity.
 
@@
 ## Study Design  
-This study involves *8 treatment groups*, with **30 participants** assigned to each. The groups are as follows:
+This study involves 2 factors, pain reliever type (4 levels) and dosage(2 levels).
+Crossing them provides us with *8 treatment groups*, with **30 participants** assigned to each.
+The groups are as follows:
 
@@
 ## Confounding Variable: Age  
-To reduce variability, we consider **age** as a **confounding variable**. Participants will be categorized into three groups:
-
+To reduce bias, we consider to control the experiment by controlling participant ages to be 18+. Hence in this study **age** acts as a **confounding variable**.
+Participants will be categorized into three groups evenly to prevent bias created through age. 
+The groups are as follows:
 1. 18–34 years
@@
 The cards memory task shows little change before and after treatment, suggesting that pain relievers may not have a major effect on this specific task.
+
+Evident through the results on @tbl-summary-6, Paracetamol is the drug that has the greatest mean & median improvement in the game scores after administering the drug (without dosage taken into account).
+Aspirin appears to negatively impact the results of the game after being given to people, this was seen through the mean and median improvements.
 
@@
 
+```{r}
+#| label: tbl-summary-6
+#| tbl-cap: "Mean Improvement in Game Scores by Drug"
+#| echo: false
+#| warning: false
+#| message: false
+
+clean_data$improvement <- clean_data$game_after - clean_data$game_before
+
+improvement_summary <- clean_data %>%
+  group_by(drug) %>%
+  summarise(
+    Mean_Improvement = mean(improvement, na.rm = TRUE),
+    SD_Improvement = sd(improvement, na.rm = TRUE),
+    Median_Improvement = median(improvement, na.rm = TRUE)
+  )
+
+kable(improvement_summary, format = "latex", booktabs = TRUE)
+
+```
 ## Summary of counts and percentage for qualitative variables
@@
 kable(age_summary, format = "latex", booktabs = TRUE) 
-```
-
-Evident through the results on @tbl-summary-6, Paracetamol is the drug that has the greatest mean & median improvement in the game scores after administering the drug (without dosage taken into account).
-Aspirin appears to negatively impact the results of the game after being given to people, this was seen through the mean and median improvements.
-
-```{r}
-#| label: tbl-summary-6
-#| tbl-cap: "Mean Improvement in Game Scores by Drug"
-#| echo: false
-#| warning: false
-#| message: false
-
-clean_data$improvement <- clean_data$game_after - clean_data$game_before
-
-improvement_summary <- clean_data %>%
-  group_by(drug) %>%
-  summarise(
-    Mean_Improvement = mean(improvement, na.rm = TRUE),
-    SD_Improvement = sd(improvement, na.rm = TRUE),
-    Median_Improvement = median(improvement, na.rm = TRUE)
-  )
-
-kable(improvement_summary, format = "latex", booktabs = TRUE)
-
 ```

### 2025-03-09 scripts/01-data_cleaning.R
data set update

@@ -7,6 +7,7 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(tidyr)
 library(janitor)
 library(lubridate)
 library(readxl)
@@ -19,24 +20,30 @@ library(stringr)
 
 # Reading dataset
 df  <- read.csv("data/raw_data/STA305 Dataset.csv")
-df$name <- trimws(df$name)  # Removes extra spaces
-df$drug_dosage <- trimws(df$drug_dosage)  # Cleans up drug_dosage
-
-sum(is.na(df$name))  # Check for missing names before split
 
 
-# Separate the 'drug_dosage' column into 'drug' and 'dosage_level'
-df <- df %>%
-  separate(drug_dosage, into = c("drug", "dosage_level"), sep = "_") %>%
-  select(name, drug, dosage_level, everything())  # Reorder columns
+df_long_game <- df %>%
+  pivot_longer(
+    cols = c(game_before, game_after),
+    names_to = "time",
+    values_to = "game_score"
+  ) %>%
+  mutate(
+    # Convert "game_before" => "Before", "game_after" => "After"
+    time = ifelse(time == "game_before", "Before", "After")
+  )
 
 
+df_long_cards <- df %>%
+  pivot_longer(
+    cols = c(cards_before, cards_after),
+    names_to = "time",
+    values_to = "cards_score"
+  ) %>%
+  mutate(
+    time = ifelse(time == "cards_before", "Before", "After")
+  )
 
-# Convert first letter of categorical variables to uppercase
-df$drug <- str_to_title(df$drug)
-df$dosage_level <- str_to_title(df$dosage_level)
-df$location <- str_to_title(df$location)
-df$age_group <- str_to_title(df$age_group)
 
 # Saving cleaned data
 write.csv(df, file = "data/analysis_data/clean_data.csv", row.names = FALSE)

### 2025-03-09 paper/EDA.qmd
Saving changes before rebase

@@
 The groups are as follows:
+
 1. 18–34 years
@@
 ## Quantitative and Qualitative Variables 
-In our study the quantitative and qualitative variables are as follows. 
-Quantitative variables: Memory Game Scores, Memory Test Cards Scores 
-Qualitative variables: Type of pain reliever, dosage level (low/high)
+In our study the quantitative and qualitative variables are as follows:
+
+1. Quantitative variables: Memory Game Scores, Memory Test Cards Scores 
+2. Qualitative variables: Type of pain reliever, dosage level (low/high)
 
@@
 1. The median scores for all drugs appear similar before treatment.
-2. **Tramadol has a higher median** than other drugs both before and after treatment.
-3. The **Placebo group has a slightly lower median score** compared to other drugs.
-4. There is **one outlier in the Tramadol group before treatment**.
+2. Tramadol has a higher median than other drugs both before and after treatment.
+3. The Placebo group has a slightly lower median score compared to other drugs.
+4. There is one outlier in the Tramadol group before treatment.
 5. The (IQR) is **similar across all drug types**, though Tramadol sees a decrease in its IQR in the memory game scores after treatment.

### 2025-03-09 scripts/01-data_cleaning.R
data update

@@ -19,25 +19,44 @@ library(stringr)
 
 # Reading dataset
 df  <- read.csv("data/raw_data/STA305 Dataset.csv")
-df$name <- trimws(df$name)  # Removes extra spaces
-df$drug_dosage <- trimws(df$drug_dosage)  # Cleans up drug_dosage
 
-sum(is.na(df$name))  # Check for missing names before split
-
-
-# Separate the 'drug_dosage' column into 'drug' and 'dosage_level'
-df <- df %>%
-  separate(drug_dosage, into = c("drug", "dosage_level"), sep = "_") %>%
-  select(name, drug, dosage_level, everything())  # Reorder columns
+# Reshape data for repeated anova measure 
+clean_data_long <- df %>%
+  pivot_longer(
+    cols = c(game_before, game_after, cards_before, cards_after),
+    names_to = c(".value", "Time"),
+    names_sep = "_"
+  )
 
 
 
-# Convert first letter of categorical variables to uppercase
-df$drug <- str_to_title(df$drug)
-df$dosage_level <- str_to_title(df$dosage_level)
-df$location <- str_to_title(df$location)
-df$age_group <- str_to_title(df$age_group)
+# Numeric value of time begore /after as 0/1 fr making plots
+clean_data_long <- clean_data_long %>%
+  mutate(Time_numeric = factor(Time, levels = c("before", "after"), labels = c(0, 1)))
+
+clean_data_long <- clean_data_long %>%
+  mutate(Time_numeric = as.numeric(as.character(Time_numeric)))
+
+
+clean_data_long <- clean_data_long %>%
+  select(name, drug, dosage_level, Time, Time_numeric, game, cards, location, age, age_group)
+
+
+clean_data_long <- clean_data_long %>%
+  rename(
+    Name = name,
+    Drug = drug,
+    DosageLevel = dosage_level,
+    Time = Time,
+    TimeNumeric = Time_numeric,
+    GameScore = game,
+    CardScore = cards,
+    Location = location,
+    Age = age,
+    AgeGroup = age_group
+  )
+
 
 # Saving cleaned data
-write.csv(df, file = "data/analysis_data/clean_data.csv", row.names = FALSE)
+write.csv(clean_data_long, file = "data/analysis_data/clean_data.csv", row.names = FALSE)
 

### 2025-03-10 paper/paper.qmd
summary stats rough update

@@
 ---
-title: "Analyzing How Organization Size, Sector, and Cybersecurity Strategies Influence Impacts on Cyberattacks"
-subtitle: "Based on Data Collected From the University of Queensland"
+title: "Effects of Different Pain Relievers and Dosages on Cognitive Retention"
+subtitle: "Exploratory Data Analysis (EDA)"
 author: 
+  - Navya Hooda
+  - Mohammed Yusuf Shaikh
   - Shivank Goel
-thanks: "Code and data are available at: https://github.com/shivankgoel003/DataBreach_Ransomware_Stats"
+  - Vanshika Vanshika
+  - Jena Shah
 date: today
 date-format: long
-abstract: "Undoubtedly as technology is progressing and we are stepping more closer to the digital world, the digital threats are also increasingly rapidly.
-This study discusses the influence of organizational size, sector, and cybersecurity strategies on cyberattack impacts.
-Utilizing a dataset from the University of Queensland about data breaches and ransomware attacks from 2004 to 2019, we analyze the trends and correlations and study how different factors contribute to the severity and frequency of these incidents.
-Our analysis reveals key insights: larger organizations report more cyber incidents, sectors like healthcare and education are frequent targets, and cybersecurity frameworks significantly help in reducing the user impact.
-These findings highlight critical areas for how organizations can improve their security and protect their data."
-header-includes:
-   - \usepackage{tikz}
-   - \usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, calc}
-   - \usepackage{pgfplots} 
-   - \usepackage{float}
-   - \usepackage{booktabs}
-   - \usepackage{longtable}
-
+number-sections: true
 format: pdf
-number-sections: true
 bibliography: references.bib
-toc: true
 ---
@@
 
-library(tidyverse)
-library(readxl)
-library(here)
+# install.packages(c("tidyverse", "janitor", "here", "lubridate", "arrow", "dplyr", 
+#   "knitr", "performance", "kableExtra", #"ggpubr"))
 
-breach_data <- read.csv(here("data/analysis_data/breach_data.csv"))
 ```
@@
 
-Therefore, in response to such attacks, there is a need for a plan, that not just keep the intruder or hackers out but also quickly alert if an attack does happen.
-Our study looks at cyber resilience, which is “ the ability to anticipate, withstand, recover from, and adapt to adverse conditions, stresses, attacks, or compromises on systems that use or are enabled by cyber resources.” as defined by National Institute of Standards and Technology [@NISTGlossary2023].
-We break our study into three major research questions, which forms the thesis of our study:
+## Relevant Background
+Pain can make everyday tasks harder, particularly when mental focus and clarity are required.
+Common pain relievers like Aspirin, Paracetamol, and Tramadol are often used to reduce physical discomfort, but their impact on cognitive functions is not well understood.
+Recalling information, a task that demands mental effort, becomes more difficult when we're in pain.
+This study investigates how different pain relievers (Aspirin, Paracetamol, and Tramadol) at standard dosages affect memory performance.
+It also looks at how varying dosages of each drug influence memory function.
+Since the ability to recall information is essential in many situations, understanding how pain relief might impact cognitive performance is important for managing pain without affecting productivity.
 
-**RQ1**: How do organizational factors such as size and sector, influence the severity of cyber breaches experienced by companies?
+## Research Questions
+1. *How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg, and Placebo) affect cognitive task performance?*
+2. *How does the dosage (low vs. high) of each drug affect cognitive retention, while accounting for confounding factors like age?*
 
-**RQ2**: Which cybersecurity strategies, including frameworks, policies, and preventive measures, are the most effective one, in reducing the damage caused by cyber attacks?
+## Study Design  
+This study involves 2 factors, pain reliever type (4 levels) and dosage(2 levels).
+Crossing them provides us with *8 treatment groups*, with **30 participants** assigned to each.
+The groups are as follows:
 
-**RQ3**: In what ways do the industry type and digital dependence of a business affect the overall impact of a cyber attack, in terms of preserving confidentiality, integrity and availability of data?
+1. Aspirin 500 mg (Low)
+2. Aspirin 1000 mg (High)
+3. Paracetamol 500 mg (Low)
+4. Paracetamol 1000 mg (High)
+5. Tramadol 50 mg (Low)
+6. Tramadol 100 mg (High)
+7. Placebo (Low) 
+8. Placebo (High)
 
-We also plotted a bar graph @fig-sector to count the number of incidents across various sectors.
-The bar chart clearly indicates that the 'Human Health Activities' sector has the highest count of incidents, standing out significantly from the other sectors.
-This might suggest that health sector is a more frequent target for cyber incidents or probably it is more diligent in reporting such events.
-The other sectors show a range of incident counts, with most appearing to have far fewer incidents in comparison.
-This could point to different levels of risk exposure, varying security measures, or reporting practices across these sectors.
+This results in **240 total observations** (8 × 30 = 240).
 
-\newpage
+## Confounding Variable: Age  
+To reduce bias, we consider to control the experiment by controlling participant ages to be 18+. Hence in this study **age** acts as a **confounding variable**.
+Participants will be categorized into three groups evenly to prevent bias created through age. 
+The groups are as follows:
 
-# References
+1. 18–34 years
+2. 35–50 years
+3. 50+ years
+
+## Quantitative and Qualitative Variables 
+In our study the quantitative and qualitative variables are as follows:
+
+1. Quantitative variables: Memory Game Scores, Memory Test Cards Scores 
+2. Qualitative variables: Type of pain reliever, dosage level (low/high)
+
+## Data Analysis Method   
+We will use **one-way ANOVA** to analyze the effects of different pain relievers on memory performance.
+Similarly, we will use **two-way ANOVA** to analyze the effects of different dosage levels per drug type on memory performance and cognitive retention.
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+library(tidyverse)
+library(janitor)
+library(here)
+library(lubridate)
+library(arrow)
+library(dplyr)
+library(knitr)
+library(performance)
+library(kableExtra)
+library(performance)
+library(ggpubr)
+
+clean_data <- read.csv(here("data", "analysis_data", "clean_data.csv"))
+
+```
+
+# Summary Statistics
+
+## Summary of quantitative variables
+
+@tbl-summary-1 shows the summary statistics of memory game scores before and after the treatment.
+The mean is similar across all groups, however, the standard deviation (SD) is relatively high.
+The median game scores remain close to the mean, and the IQR (Interquartile Range) is smaller than the SD.
+The cards memory task shows little change before and after treatment, suggesting that pain relievers may not have a major effect on this specific task.
+
+Evident through the results on @tbl-summary-6, Paracetamol is the drug that has the greatest mean & median improvement in the game scores after administering the drug (without dosage taken into account).
+Aspirin appears to negatively impact the results of the game after being given to people, this was seen through the mean and median improvements.
+
+```{r}
+#| label: tbl-summary-1
+#| tbl-cap: "Summary Statistics for Quantitative Variables"
+#| echo: false
+#| warning: false
+#| message: false
+library(knitr)
+library(stringr)
+
+# Calculate Means and SDs by Time for GameScore
+game_means <- tapply(clean_data$GameScore, clean_data$Time, mean, na.rm = TRUE)
+game_sds   <- tapply(clean_data$GameScore, clean_data$Time, sd, na.rm = TRUE)
+
+# Calculate Means and SDs by Time for CardScore
+cards_means <- tapply(clean_data$CardScore, clean_data$Time, mean, na.rm = TRUE)
+cards_sds   <- tapply(clean_data$CardScore, clean_data$Time, sd, na.rm = TRUE)
+
+# Combine into a data frame for kable
+summary_table <- data.frame(
+  Time = names(game_means),
+  Game_Mean = round(game_means, 2),
+  Game_SD   = round(game_sds, 2),
+  Cards_Mean = round(cards_means, 2),
+  Cards_SD   = round(cards_sds, 2)
+)
+
+summary_table$Time <- str_to_title(summary_table$Time)
+
+# Display table with no row names
+kable(summary_table, caption = "Summary Statistics by Time", booktabs = TRUE, row.names = FALSE)
+
+```
+
+```{r}
+library(dplyr)
+library(knitr)
+
+# Step 1: Create a wide dataset with Before/After side by side for GameScore
+game_wide <- clean_data %>%
+  select(Name, Drug, DosageLevel, Time, GameScore) %>%
+  pivot_wider(
+    names_from = Time,
+    values_from = GameScore
+  )
+
+# Step 2: Compute improvement (After - Before)
+game_wide <- game_wide %>%
+  mutate(improvement = after - before)
+
+# Step 3: Summarise improvements by Drug
+improvement_summary <- game_wide %>%
+  group_by(Drug) %>%
+  summarise(
+    Mean_Improvement = round(mean(improvement, na.rm = TRUE), 2),
+    SD_Improvement = round(sd(improvement, na.rm = TRUE), 2),
+    Median_Improvement = round(median(improvement, na.rm = TRUE), 2)
+  )
+
+# Step 4: Display the table
+kable(improvement_summary, caption = "Mean Improvement in Game Scores by Drug", booktabs = TRUE, row.names = FALSE)
+
+```
+
+```{r}
+#| label: tbl-summary-2
+#| tbl-cap: "Summary of Drug Types"
+#| echo: false
+#| warning: false
+#| message: false
+
+library(knitr)
+
+# Count and percentage for Drug
+drug_counts <- table(clean_data$Drug)  # Use capital "D" if that's your column name
+drug_percentages <- prop.table(drug_counts) * 100
+
+# Combine into a data frame
+drug_summary <- data.frame(
+  Drug = names(drug_counts),
+  Count = as.numeric(drug_counts),
+  Percentage = round(as.numeric(drug_percentages), 2)
+)
+
+# Display table
+kable(drug_summary, caption = "Summary of Drug Types", booktabs = TRUE, row.names = FALSE)
+
+```
+
+```{r}
+#| label: tbl-summary-3
+#| tbl-cap: "Summary of Dosage Levels"
+#| echo: false
+#| warning: false
+#| message: false
+
+library(knitr)
+
+# Count and percentage for Dosage Level
+dosage_counts <- table(clean_data$DosageLevel)
+dosage_percentages <- prop.table(dosage_counts) * 100
+
+# Combine into a data frame
+dosage_summary <- data.frame(
+  Dosage = names(dosage_counts),
+  Count = as.numeric(dosage_counts),
+  Percentage = round(as.numeric(dosage_percentages), 2)
+)
+
+# Display table
+kable(dosage_summary, caption = "Summary of Dosage Levels", booktabs = TRUE, row.names = FALSE)
+
+```
+
+```{r}
+#| label: tbl-summary-5
+#| tbl-cap: "Summary of Age Groups"
+#| echo: false
+#| warning: false
+#| message: false
+
+library(knitr)
+
+# Count and percentage for Age Group
+age_counts <- table(clean_data$AgeGroup)
+age_percentages <- prop.table(age_counts) * 100
+
+# Combine into a data frame
+age_summary <- data.frame(
+  Age_Group = names(age_counts),
+  Count = as.numeric(age_counts),
+  Percentage = round(as.numeric(age_percentages), 2)
+)
+
+# Display table
+kable(age_summary, caption = "Summary of Age Groups", booktabs = TRUE, row.names = FALSE)
+
+```
+
+## Summary of counts and percentage for qualitative variables
+
+@tbl-summary-2 shows the distribution of participants across drug types. Aspirin, Paracetamol, and Tramadol, and Placebo each have 60 participants (25\%), ensuring balance.
+
+@tbl-summary-3 shows the dosage levels assigned to participants. There is an equal split between high-dose (120 participants, 50\%) and low-dose (120 participants, 50\%) conditions.
+
+## Confounding Variable
+
+@tbl-summary-5 shows the breakdown of age groups, which is a confounding variable in this study. The three age groups: 18–34, 35–50, and 50+ each have 80 participants (33.33\%).
+
+# Plots
+
+## Game Score Distribution Before and After Treatment
+
+@fig-boxplot-scores shows the distribution of memory game scores before and after treatment across different drug types using box plots.
+
+1. The median scores for all drugs appear similar before treatment.
+2. Tramadol has a higher median than other drugs both before and after treatment.
+3. The Placebo group has a slightly lower median score compared to other drugs.
+4. There is one outlier in the Tramadol group before treatment.
+5. The (IQR) is **similar across all drug types**, though Tramadol sees a decrease in its IQR in the memory game scores after treatment.
+
+These boxplots provide an initial comparison of cognitive performance changes before and after drug administration.
+
+## Memory Card Score Distribution Before and After Treatment
+
+@fig-boxplot-cards shows the distribution of **memory card scores before and after treatment** across drug types.
+
+1. Before treatment, the scores are relatively high across all groups, with Paracetamol and Placebo showing slightly higher medians than the others.
+2. After treatment, the distributions remain similar, though there is a slight increase in spread for Aspirin, Paracetamol, and Placebo.
+3. There is a slight decrease in the IQR of Tramadol. 
+3. Outliers are present in all groups, indicating some variability in memory card performance across individuals.
+
+# Assumptions
+
+## Checking Model Assumptions
+
+We assessed the homogeneity of variance and normality of residuals using diagnostic plots to validate the assumptions of our ANOVA tests. (@fig-assump-one & @fig-assump-two).
+
+**One-way ANOVA**
+
+*Independence:* For our one-way ANOVA model, we have independence because our observations are independent within and across the groups i.e all participants were randomly assigned a pain reliever, and there was no relationships between observations (i.e repeated  participants, treatments etc.)
+
+*Homogeneity of Variance:* 
+The reference line in @fig-assump-one relatively flat and horizontal which indicates that variance is approximately equal across groups.
+Thus, the assumption of homogeneity of variance is not significantly violated.
+
+*Normality of Residuals:* 
+The residuals are approximately normally distributed in @fig-assump-one since the density plot on the right appears close to a normal distribution.
+
+**Two-way ANOVA**
+
+*Independence:*
+For our two-way ANOVA model, the different combinations of pain reliever type and dosage levels were randomly assigned to all participants, in random order.
+
+*Homogeneity of Variance:* 
+In @fig-assump-two the left plot shows some deviation from a perfectly flat line and has minor fluctuations, especially at certain levels of drug type and dosage.
+Despite some variation, the overall trend does not show extreme violations of homogeneity.
+
+*Normality of Residuals:* 
+In @fig-assump-two the density plot on the right shows that the residuals follow a roughly normal distribution even though minor deviations are present.
+
+**Conclusion**
+
+Both models satisfy the assumptions of homogeneity of variance and normality of residuals well enough.
+There are slight deviations in the two-way ANOVA model, but they are not severe enough to invalidate the analysis.
+Therefore, we proceed with the ANOVA tests.

### 2025-03-10 paper/paper.qmd
summary stats based on new dataset

@@
 # Display table with no row names
-kable(summary_table, caption = "Summary Statistics by Time", booktabs = TRUE, row.names = FALSE)
+kable(summary_table, booktabs = TRUE, row.names = FALSE)
 
@@
 # Display table
-kable(drug_summary, caption = "Summary of Drug Types", booktabs = TRUE, row.names = FALSE)
+kable(drug_summary, booktabs = TRUE, row.names = FALSE)
 
@@
 # Display table
-kable(dosage_summary, caption = "Summary of Dosage Levels", booktabs = TRUE, row.names = FALSE)
+kable(dosage_summary, booktabs = TRUE, row.names = FALSE)
 
@@
 # Display table
-kable(age_summary, caption = "Summary of Age Groups", booktabs = TRUE, row.names = FALSE)
+kable(age_summary, booktabs = TRUE, row.names = FALSE)
 

### 2025-03-11 paper/paper.qmd
box plots updated

@@
 library(knitr)
+library(dplyr)
 library(stringr)
@@
 ```{r}
-library(dplyr)
-library(knitr)
+
+#| label: tbl-summary-1
+#| tbl-cap: "Mean Improvement in Game Scores by Drug"
+#| echo: false
+#| warning: false
+#| message: false
 
@@
 # Step 4: Display the table
-kable(improvement_summary, caption = "Mean Improvement in Game Scores by Drug", booktabs = TRUE, row.names = FALSE)
+kable(improvement_summary, booktabs = TRUE, row.names = FALSE)
 
@@
 
+```{r}
+
+#| label: fig-boxplot-scores
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Boxplot of Memory Game Scores Before and After Treatment by Drug Type"
+
+ggplot(clean_data, aes(x = Drug, y = GameScore, fill = Time)) +
+  geom_boxplot(position = position_dodge(width = 0.8)) +
+  labs(
+    title = "Memory Game Scores by Drug Type and Time",
+    x = "Drug Type",
+    y = "Memory Game Score",
+    fill = "Time"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 16),
+    axis.title = element_text(size = 14),
+    axis.text = element_text(size = 12),
+    legend.title = element_text(size = 12)
+  )
+```
+
+```{r}
+#| label: fig-boxplot-cards
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Boxplot of Memory Card Scores Before and After Treatment by Drug Type"
+
+ggplot(clean_data, aes(x = Drug, y = CardScore, fill = Time)) +
+  geom_boxplot(position = position_dodge(width = 0.8)) +
+  labs(
+    title = "Memory Card Scores Before and After Treatment by Drug Type",
+    x = "Drug Type",
+    y = "Memory Card Score",
+    fill = "Time"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 16),
+    axis.title = element_text(size = 14),
+    axis.text = element_text(size = 12),
+    legend.title = element_text(size = 12)
+  )
+
+```
+
 ## Memory Card Score Distribution Before and After Treatment

### 2025-03-11 paper/paper.qmd
Assumptions

--- 2025-03-10 paper/paper.qmd
@@
 
+**Repeated Measures ANOVA**
+(To be changed)
+When performing a repeated measures ANOVA, it is essential to verify that the underlying assumptions of the test are met. These assumptions include:
+\begin{itemize}
+    \item \textbf{Normality}: The dependent variable should be normally distributed within each group.
+    \item \textbf{Sphericity}: The variances of the differences between all combinations of related groups should be equal.
+    \item \textbf{Homogeneity of Variance}: The variances of the dependent variable should be equal across groups.
+\end{itemize}
+
+This document outlines the methods and tests used to verify these assumptions.
+
+\section*{Normality}
+The assumption of normality was tested using the Shapiro-Wilk test.
+The Shapiro-Wilk test evaluates the null hypothesis that the data is normally distributed.
+The test statistic \( W \) and the corresponding \( p \)-value were calculated for each combination of the factors (Drug, DosageLevel, and Time).
+
+\subsection*{Hypotheses}
+\begin{itemize}
+    \item \( H_0 \): The data is normally distributed.
+    \item \( H_1 \): The data is not normally distributed.
+\end{itemize}
+
+\subsection*{Interpretation}
+If the \( p \)-value is greater than 0.05, we fail to reject the null hypothesis and assume normality. Otherwise, the normality assumption is violated.
+
+\subsection*{Visual Inspection}
+Q-Q plots were generated to visually inspect the normality assumption. If the points in the Q-Q plot lie approximately on the reference line, the data can be assumed to be normally distributed.
+
+\section*{Sphericity}
+The assumption of sphericity was tested using Mauchly's test. Sphericity refers to the condition where the variances of the differences between all combinations of related groups are equal.
+
+\subsection*{Hypotheses}
+\begin{itemize}
+    \item \( H_0 \): The variances of the differences are equal (sphericity is met).
+    \item \( H_1 \): The variances of the differences are not equal (sphericity is violated).
+\end{itemize}
+
+\subsection*{Interpretation}
+If the \( p \)-value from Mauchly's test is greater than 0.05, we fail to reject the null hypothesis and assume sphericity.
+If the assumption is violated, corrections such as Greenhouse-Geisser or Huynh-Feldt should be applied.
+
+\section*{Homogeneity of Variance}
+The assumption of homogeneity of variance was tested using Levene's test.
+This test evaluates whether the variances of the dependent variable are equal across all groups formed by the combinations of the factors (Drug, DosageLevel, and Time).
+
+\subsection*{Hypotheses}
+\begin{itemize}
+    \item \( H_0 \): The variances are equal across groups.
+    \item \( H_1 \): The variances are not equal across groups.
+\end{itemize}
+
+\subsection*{Interpretation}
+If the \( p \)-value from Levene's test is greater than 0.05, we fail to reject the null hypothesis and assume homogeneity of variance.
+If the assumption is violated, transformations or alternative statistical methods may be required.
+
+\subsection*{Visual Inspection}
+Boxplots were generated to visually inspect the homogeneity of variance. If the boxplots show similar spreads across groups, the assumption is likely met.
+
+\section*{Conclusion}
+The results of the assumption tests (Shapiro-Wilk, Mauchly's, and Levene's) were used to determine whether the assumptions of normality, sphericity, and homogeneity of variance were met.
+If any assumptions were violated, appropriate corrections or alternative methods were considered before proceeding with the repeated measures ANOVA.
+```{r}
+#| label: tbl-model1
+#| tbl-cap: "Summary of Age Groups"
+#| echo: false
+#| warning: false
+#| message: false
+
+# Load necessary libraries
+library(tidyverse)
+library(ggplot2)
+library(car)
+library(ez)
+
+# Assuming the dataset is loaded into a data frame called `data`
+# Convert necessary columns to factors
+clean_data$Drug <- as.factor(clean_data$Drug)
+clean_data$DosageLevel <- as.factor(clean_data$DosageLevel)
+clean_data$Time <- as.factor(clean_data$Time)
+clean_data$AgeGroup <- as.factor(clean_data$AgeGroup)
+
+# Check for Normality
+# We will use Shapiro-Wilk test for normality
+shapiro_test <- clean_data %>%
+  group_by(Drug, DosageLevel, Time) %>%
+  summarise(statistic = shapiro.test(GameScore)$statistic,
+            p.value = shapiro.test(GameScore)$p.value)
+
+print(shapiro_test)
+
+# Visual check for normality using Q-Q plots
+ggplot(clean_data, aes(sample = GameScore)) +
+  geom_qq() +
+  geom_qq_line() +
+  facet_grid(Drug ~ DosageLevel + Time) +
+  theme_minimal() +
+  ggtitle("Q-Q Plots for Normality Check")
+
+# Check for Sphericity using Mauchly's Test
+# We will use the `ezANOVA` function to check for sphericity
+ez_model <- ezANOVA(
+  data = clean_data,
+  dv = .(GameScore),
+  wid = .(Name),
+  within = .(Time),
+  between = .(Drug, DosageLevel),
+  type = 3,
+  detailed = TRUE
+)
+
+print(ez_model)
+
+# Check for Homogeneity of Variance using Levene's Test
+levene_test <- leveneTest(GameScore ~ Drug * DosageLevel * Time, data = clean_data)
+print(levene_test)
+
+# Visual check for homogeneity of variance using boxplots
+ggplot(clean_data, aes(x = interaction(Drug, DosageLevel, Time), y = GameScore)) +
+  geom_boxplot() +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  ggtitle("Boxplots for Homogeneity of Variance Check")
+
+```
+
 We assessed the homogeneity of variance and normality of residuals using diagnostic plots to validate the assumptions of our ANOVA tests. (@fig-assump-one & @fig-assump-two).

### 2025-03-11 paper/paper.qmd
minor changes

--- 2025-03-11 paper/paper.qmd
@@
 
-# Step 4: Display the table
 kable(improvement_summary, booktabs = TRUE, row.names = FALSE)
@@
   )
-
 ```

### 2025-03-20 paper/paper.qmd
summary stats and plots updated based on new data

--- 2025-03-11 paper/paper.qmd
@@
 library(performance)
+library(stringr)
 library(kableExtra)
@@
 #| message: false
-library(knitr)
-library(stringr)
 
-# Calculate Means and SDs by Time for GameScore
-game_means <- tapply(clean_data$GameScore, clean_data$Time, mean, na.rm = TRUE)
-game_sds   <- tapply(clean_data$GameScore, clean_data$Time, sd, na.rm = TRUE)
+# Compute statistics for Memory Game Score
+mean_game <- mean(clean_data$memory_game_score, na.rm = TRUE)
+median_game <- median(clean_data$memory_game_score, na.rm = TRUE)
+sd_game <- sd(clean_data$memory_game_score, na.rm = TRUE)
+iqr_game <- IQR(clean_data$memory_game_score, na.rm = TRUE)
 
-# Calculate Means and SDs by Time for CardScore
-cards_means <- tapply(clean_data$CardScore, clean_data$Time, mean, na.rm = TRUE)
-cards_sds   <- tapply(clean_data$CardScore, clean_data$Time, sd, na.rm = TRUE)
+# Compute statistics for Memory Cards Score
+mean_cards <- mean(clean_data$memory_cards_score, na.rm = TRUE)
+median_cards <- median(clean_data$memory_cards_score, na.rm = TRUE)
+sd_cards <- sd(clean_data$memory_cards_score, na.rm = TRUE)
+iqr_cards <- IQR(clean_data$memory_cards_score, na.rm = TRUE)
 
-# Combine into a data frame for kable
+# Combine into a summary table
 summary_table <- data.frame(
-  Time = names(game_means),
-  Game_Mean = round(game_means, 2),
-  Game_SD   = round(game_sds, 2),
-  Cards_Mean = round(cards_means, 2),
-  Cards_SD   = round(cards_sds, 2)
+  Statistic = c("Mean", "Median", "SD", "IQR"),
+  `Memory Game Score` = c(mean_game, median_game, sd_game, iqr_game),
+  `Memory Cards Score` = c(mean_cards, median_cards, sd_cards, iqr_cards)
 )
 
-summary_table$Time <- str_to_title(summary_table$Time)
+# Display the table
 
-# Display table with no row names
-kable(summary_table, booktabs = TRUE, row.names = FALSE)
+kable(summary_table, format = "latex", booktabs = TRUE)
 
@@
 ```{r}
-library(dplyr)
-library(knitr)
 

### 2025-03-20 scripts/01-data_cleaning.R

@@ -38,6 +38,3 @@ df$dosage_level <- str_to_title(df$dosage_level)
 df$location <- str_to_title(df$location)
 df$age_group <- str_to_title(df$age_group)
 
-# Saving cleaned data
-write.csv(df, file = "data/analysis_data/clean_data.csv", row.names = FALSE)
-

### 2025-03-20 paper/paper.qmd
summary stats and plots updated based on new dataset

@@
 
-# Display the table
+# Display table
 
 kable(summary_table, format = "latex", booktabs = TRUE)
-
-```
-
-```{r}
-
-# Step 1: Create a wide dataset with Before/After side by side for GameScore
-game_wide <- clean_data %>%
-  select(Name, Drug, DosageLevel, Time, GameScore) %>%
-  pivot_wider(
-    names_from = Time,
-    values_from = GameScore
-  )
-
-# Step 2: Compute improvement (After - Before)
-game_wide <- game_wide %>%
-  mutate(improvement = after - before)
-
-# Step 3: Summarise improvements by Drug
-improvement_summary <- game_wide %>%
-  group_by(Drug) %>%
-  summarise(
-    Mean_Improvement = round(mean(improvement, na.rm = TRUE), 2),
-    SD_Improvement = round(sd(improvement, na.rm = TRUE), 2),
-    Median_Improvement = round(median(improvement, na.rm = TRUE), 2)
-  )
-
-# Step 4: Display the table
-kable(improvement_summary, caption = "Mean Improvement in Game Scores by Drug", booktabs = TRUE, row.names = FALSE)
 
@@
 
-library(knitr)
+drug_counts <- table(clean_data$drug)
 
-# Count and percentage for Drug
-drug_counts <- table(clean_data$Drug)  # Use capital "D" if that's your column name
+# percentages
 drug_percentages <- prop.table(drug_counts) * 100
 
-# Combine into a data frame
+#  summary dataframe
 drug_summary <- data.frame(
@@
 # Display table
-kable(drug_summary, booktabs = TRUE, row.names = FALSE)
+kable(drug_summary, format = "latex", booktabs = TRUE)
 
@@
 
-library(knitr)
+dosage_counts <- table(clean_data$dosage_level)
 
-# Count and percentage for Dosage Level
-dosage_counts <- table(clean_data$DosageLevel)
+# percentage for each dosage level
 dosage_percentages <- prop.table(dosage_counts) * 100
 
-# Combine into a data frame
+# summary dataframe
 dosage_summary <- data.frame(
@@
 
-library(knitr)
+age_counts <- table(clean_data$age_group)
 
-# Count and percentage for Age Group
-age_counts <- table(clean_data$AgeGroup)
+# percentages for each age group
 age_percentages <- prop.table(age_counts) * 100
 
-# Combine into a data frame
+# summary dataframe
 age_summary <- data.frame(
@@
 # Plots
+
+```{r}
+
+#| label: fig-boxplot-game-scores
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Memory Game Scores by Drug Type and Dosage Level"
+
+clean_data$dosage_level <- factor(clean_data$dosage_level, levels = c("Low", "High"))
+
+# Boxplot of Memory Game Scores by Drug, colored by Dosage Level
+ggplot(clean_data, aes(x = drug, y = memory_game_score, fill = dosage_level)) +
+  geom_boxplot() +
+  labs(
+    x = "Drug Type",
+    y = "Memory Game Score",
+    fill = "Dosage Level"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 14, face = "bold"),
+    axis.title = element_text(size = 12)
+  )
+
+```
+
+```{r}
+#| label: fig-boxplot-card-scores
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Memory Game Scores by Drug Type and Dosage Level"
+
+ggplot(clean_data, aes(x = drug, y = memory_cards_score, fill = dosage_level)) +
+  geom_boxplot() +
+  labs(
+    x = "Drug Type",
+    y = "Memory Cards Score",
+    fill = "Dosage Level"
+  ) +
+  theme_minimal()
+
+```
 

### 2025-03-20 paper/paper.qmd

@@
+this is all i want in main:
 ---

### 2025-03-20 paper/paper.qmd
resolving git issues

@@
 If any assumptions were violated, appropriate corrections or alternative methods were considered before proceeding with the repeated measures ANOVA.
-```{r}
-#| label: tbl-model1
-#| tbl-cap: "Summary of Age Groups"
-#| echo: false
-#| warning: false
-#| message: false
-
-# Load necessary libraries
-library(tidyverse)
-library(ggplot2)
-library(car)
-library(ez)
-
-# Assuming the dataset is loaded into a data frame called `data`
-# Convert necessary columns to factors
-clean_data$Drug <- as.factor(clean_data$Drug)
-clean_data$DosageLevel <- as.factor(clean_data$DosageLevel)
-clean_data$Time <- as.factor(clean_data$Time)
-clean_data$AgeGroup <- as.factor(clean_data$AgeGroup)
-
-# Check for Normality
-# We will use Shapiro-Wilk test for normality
-shapiro_test <- clean_data %>%
-  group_by(Drug, DosageLevel, Time) %>%
-  summarise(statistic = shapiro.test(GameScore)$statistic,
-            p.value = shapiro.test(GameScore)$p.value)
-
-print(shapiro_test)
-
-# Visual check for normality using Q-Q plots
-ggplot(clean_data, aes(sample = GameScore)) +
-  geom_qq() +
-  geom_qq_line() +
-  facet_grid(Drug ~ DosageLevel + Time) +
-  theme_minimal() +
-  ggtitle("Q-Q Plots for Normality Check")
-
-# Check for Sphericity using Mauchly's Test
-# We will use the `ezANOVA` function to check for sphericity
-ez_model <- ezANOVA(
-  data = clean_data,
-  dv = .(GameScore),
-  wid = .(Name),
-  within = .(Time),
-  between = .(Drug, DosageLevel),
-  type = 3,
-  detailed = TRUE
-)
-
-print(ez_model)
 

### 2025-03-20 scripts/01-data_cleaning.R

@@ -56,10 +56,3 @@ clean_data_long <- clean_data_long %>%
     AgeGroup = age_group
   )
 
-
-<<<<<<< HEAD
-# Saving cleaned data
-write.csv(clean_data_long, file = "data/analysis_data/clean_data.csv", row.names = FALSE)
-
-=======
->>>>>>> Vanshika

### 2025-03-20 paper/paper.qmd
plots and stats

@@
-this is all i want in main:
 ---
@@
 ---
-
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-
-# install.packages(c("tidyverse", "janitor", "here", "lubridate", "arrow", "dplyr", 
-#   "knitr", "performance", "kableExtra", #"ggpubr"))
-
-```
 
@@
 
+colnames(summary_table) <- c("Statistic", "Memory Game Score", "Memory Cards Score")
+
 # Display table
@@
 ```{r}
-
 #| label: fig-boxplot-game-scores

### 2025-03-21 paper/paper.qmd
Updated code  uner assumption

@@
 
+## Model
+
+$$
+\text{memory\_game\_score}_i = \beta_0 + \beta_1 \cdot \text{drug}_i + \beta_2 \cdot \text{dosage\_level}_i + \beta_3 \cdot (\text{drug}_i \times \text{dosage\_level}_i) + \varepsilon_i
+$$
+
+Where:
+
+- $\beta_0$ is the intercept.
+
+- $\beta_1$, $\beta_2$, and $\beta_3$ are coefficients for the predictors and interaction term.
+
+- $\varepsilon_i$ is the random error term.
+
+```{r}
+
+# Regression Model results
+anova_model <- lm(memory_game_score ~ drug * dosage_level, data = clean_data)
+summary(anova_model)
+
+```
+
+$$
+Y_{ijk} = \mu + \alpha_i + \beta_j + (\alpha\beta)_{ij} + \varepsilon_{ijk}
+$$
+
+Where:
+
+- $Y_{ijk}$: Memory score
+- $\mu$: Overall mean  
+- $\alpha_i$: Effect of the $i^{\text{th}}$ drug  
+- $\beta_j$: Effect of the $j^{\text{th}}$ dosage level  
+- $(\alpha\beta)_{ij}$: Interaction effect between drug and dosage  
+- $\varepsilon_{ijk} \sim \mathcal{N}(0, \sigma^2)$: Random error
+
+```{r}
+# Two way ANOVA result
+anova(anova_model)
+```
+```{r}
+# Normality Check
+ggqqplot(residuals(anova_model)) + ggtitle("Q-Q Plot of Residuals")
+# Shapiro-Wilk Normality Test
+shapiro_test <- shapiro.test(residuals(anova_model))
+shapiro_test
+```
+
+```{r}
+# Scale-Location Plot
+plot(anova_model, which = 3)
+```
+```{r}
+# Perform Bartlett’s test for homogeneity of variance
+bartlett_test <- bartlett.test(memory_game_score ~ interaction(drug, dosage_level), data = clean_data)
+
+# Display test results
+bartlett_test
+```
+
 ## Checking Model Assumptions
 
-**Repeated Measures ANOVA**
+**Two Way ANOVA**
 (To be changed)

### 2025-03-21 paper/paper.qmd
only writeup left

@@
 library(lubridate)
+library(patchwork)
 library(arrow)
@@
 library(performance)
-library(stringr)
+library(modelsummary)
 library(kableExtra)
@@
 
+```{r}
+#| label: fig-interaction
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Interaction Plot: Drug Type vs. Dosage Level"
+
+p1 <- ggplot(clean_data, aes(x = drug, y = memory_game_score, color = dosage_level, group = dosage_level)) +
+  stat_summary(fun = mean, geom = "point", size = 3) +
+  stat_summary(fun = mean, geom = "line", size = 1) +
+  labs(title = "Memory Game Scores",
+       x = "Drug Type",
+       y = "Mean Memory Game Score",
+       color = "Dosage Level") +
+  theme_minimal()
+
+# Interaction plot for Memory Cards Scores
+p2 <- ggplot(clean_data, aes(x = drug, y = memory_cards_score, color = dosage_level, group = dosage_level)) +
+  stat_summary(fun = mean, geom = "point", size = 3) +
+  stat_summary(fun = mean, geom = "line", size = 1) +
+  labs(title = "Memory Cards Scores",
+       x = "Drug Type",
+       y = "Mean Memory Cards Score",
+       color = "Dosage Level") +
+  theme_minimal()
+
+# Combine the two plots vertically
+combined_plot <- p1 / p2
+combined_plot
+```
+
 # Plots
@@
 ```{r}
+#| label: tbl-model-result
+#| tbl-cap: "Regression Results for Memory Game Score"
+#| echo: false
+#| warning: false
+#| message: false
+
+# References: https://cran.r-project.org/web/packages/broom/vignettes/broom.html
+
+library(broom)
 
@@
 anova_model <- lm(memory_game_score ~ drug * dosage_level, data = clean_data)
-summary(anova_model)
 
+model_tidy <- tidy(anova_model)
+
+kable(model_tidy, format = "latex", booktabs = TRUE)
+
+```
+
+```{r}
+#| label: tbl-model-fit
+#| tbl-cap: "Model Fit Statistics for Memory Game Score"
+#| echo: false
+#| warning: false
+#| message: false
+
+model_glance <- glance(anova_model)
+kable(model_glance, format = "latex", booktabs = TRUE) %>%
+   kable_styling(latex_options = "scale_down")
 ```
@@
 ```{r}
+#| label: tbl-anova-model
+#| tbl-cap: "Two-Way ANOVA Results for Memory Game Score"
+#| echo: false
+#| warning: false
+#| message: false
+
 # Two way ANOVA result
-anova(anova_model)
-```
-```{r}
-# Normality Check
-ggqqplot(residuals(anova_model)) + ggtitle("Q-Q Plot of Residuals")
-# Shapiro-Wilk Normality Test
-shapiro_test <- shapiro.test(residuals(anova_model))
-shapiro_test
+anova_result <- anova(anova_model)
+
+anova_table_df <- as.data.frame(anova_result)
+
+kable(anova_table_df, format = "latex", booktabs = TRUE)
+
 ```
@@
 ```{r}
+#| label: fig-normal-plot
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Q-Q Plot of Residuals"
+
+# Normality Check
+ggqqplot(residuals(anova_model))
+```
+
+```{r}
+#| label: tbl-shapiro
+#| tbl-cap: "Shapiro-Wilk Test for Normality"
+#| echo: false
+#| warning: false
+#| message: false
+
+# Shapiro-Wilk Normality Test
+shapiro_test <- shapiro.test(residuals(anova_model))
+shapiro_table <- data.frame(
+  Statistic = round(shapiro_test$statistic, 4),
+  P_Value = round(shapiro_test$p.value, 4),
+  Method = shapiro_test$method
+)
+
+kable(shapiro_table, format = "latex", booktabs = TRUE)
+```
+
+```{r}
+#| label: tbl-bartlett
+#| tbl-cap: "Bartlett’s Test for Homogeneity of Variance"
+#| echo: false
+#| warning: false
+#| message: false
+
 # Scale-Location Plot
 plot(anova_model, which = 3)
-```
-```{r}
+
 # Perform Bartlett’s test for homogeneity of variance
@@
 
-# Display test results
-bartlett_test
+bartlett_table <- data.frame(
+  Statistic = round(bartlett_test$statistic, 4),
+  DF = bartlett_test$parameter,
+  P_Value = round(bartlett_test$p.value, 4),
+  Method = bartlett_test$method
+)
+
+kable(bartlett_table, format = "latex", booktabs = TRUE)
 ```
-
-## Checking Model Assumptions
-
-**Two Way ANOVA**
-(To be changed)
-When performing a repeated measures ANOVA, it is essential to verify that the underlying assumptions of the test are met. These assumptions include:
-\begin{itemize}
-    \item \textbf{Normality}: The dependent variable should be normally distributed within each group.
-    \item \textbf{Sphericity}: The variances of the differences between all combinations of related groups should be equal.
-    \item \textbf{Homogeneity of Variance}: The variances of the dependent variable should be equal across groups.
-\end{itemize}
-
-This document outlines the methods and tests used to verify these assumptions.
-
-\section*{Normality}
-The assumption of normality was tested using the Shapiro-Wilk test.
-The Shapiro-Wilk test evaluates the null hypothesis that the data is normally distributed.
-The test statistic \( W \) and the corresponding \( p \)-value were calculated for each combination of the factors (Drug, DosageLevel, and Time).
-
-\subsection*{Hypotheses}
-\begin{itemize}
-    \item \( H_0 \): The data is normally distributed.
-    \item \( H_1 \): The data is not normally distributed.
-\end{itemize}
-
-\subsection*{Interpretation}
-If the \( p \)-value is greater than 0.05, we fail to reject the null hypothesis and assume normality. Otherwise, the normality assumption is violated.
-
-\subsection*{Visual Inspection}
-Q-Q plots were generated to visually inspect the normality assumption. If the points in the Q-Q plot lie approximately on the reference line, the data can be assumed to be normally distributed.
-
-\section*{Sphericity}
-The assumption of sphericity was tested using Mauchly's test. Sphericity refers to the condition where the variances of the differences between all combinations of related groups are equal.
-
-\subsection*{Hypotheses}
-\begin{itemize}
-    \item \( H_0 \): The variances of the differences are equal (sphericity is met).
-    \item \( H_1 \): The variances of the differences are not equal (sphericity is violated).
-\end{itemize}
-
-\subsection*{Interpretation}
-If the \( p \)-value from Mauchly's test is greater than 0.05, we fail to reject the null hypothesis and assume sphericity.
-If the assumption is violated, corrections such as Greenhouse-Geisser or Huynh-Feldt should be applied.
-
-\section*{Homogeneity of Variance}
-The assumption of homogeneity of variance was tested using Levene's test.
-This test evaluates whether the variances of the dependent variable are equal across all groups formed by the combinations of the factors (Drug, DosageLevel, and Time).
-
-\subsection*{Hypotheses}
-\begin{itemize}
-    \item \( H_0 \): The variances are equal across groups.
-    \item \( H_1 \): The variances are not equal across groups.
-\end{itemize}
-
-\subsection*{Interpretation}
-If the \( p \)-value from Levene's test is greater than 0.05, we fail to reject the null hypothesis and assume homogeneity of variance.
-If the assumption is violated, transformations or alternative statistical methods may be required.
-
-\subsection*{Visual Inspection}
-Boxplots were generated to visually inspect the homogeneity of variance. If the boxplots show similar spreads across groups, the assumption is likely met.
-
-\section*{Conclusion}
-The results of the assumption tests (Shapiro-Wilk, Mauchly's, and Levene's) were used to determine whether the assumptions of normality, sphericity, and homogeneity of variance were met.
-If any assumptions were violated, appropriate corrections or alternative methods were considered before proceeding with the repeated measures ANOVA.
-
-# Check for Homogeneity of Variance using Levene's Test
-levene_test <- leveneTest(GameScore ~ Drug * DosageLevel * Time, data = clean_data)
-print(levene_test)
-
-# Visual check for homogeneity of variance using boxplots
-ggplot(clean_data, aes(x = interaction(Drug, DosageLevel, Time), y = GameScore)) +
-  geom_boxplot() +
-  theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  ggtitle("Boxplots for Homogeneity of Variance Check")
-
-```
-
-We assessed the homogeneity of variance and normality of residuals using diagnostic plots to validate the assumptions of our ANOVA tests. (@fig-assump-one & @fig-assump-two).
-
-**One-way ANOVA**
-
-*Independence:* For our one-way ANOVA model, we have independence because our observations are independent within and across the groups i.e all participants were randomly assigned a pain reliever, and there was no relationships between observations (i.e repeated  participants, treatments etc.)
-
-*Homogeneity of Variance:* 
-The reference line in @fig-assump-one relatively flat and horizontal which indicates that variance is approximately equal across groups.
-Thus, the assumption of homogeneity of variance is not significantly violated.
-
-*Normality of Residuals:* 
-The residuals are approximately normally distributed in @fig-assump-one since the density plot on the right appears close to a normal distribution.
-
-**Two-way ANOVA**
-
-*Independence:*
-For our two-way ANOVA model, the different combinations of pain reliever type and dosage levels were randomly assigned to all participants, in random order.
-
-*Homogeneity of Variance:* 
-In @fig-assump-two the left plot shows some deviation from a perfectly flat line and has minor fluctuations, especially at certain levels of drug type and dosage.
-Despite some variation, the overall trend does not show extreme violations of homogeneity.
-
-*Normality of Residuals:* 
-In @fig-assump-two the density plot on the right shows that the residuals follow a roughly normal distribution even though minor deviations are present.
-
-**Conclusion**
-
-Both models satisfy the assumptions of homogeneity of variance and normality of residuals well enough.
-There are slight deviations in the two-way ANOVA model, but they are not severe enough to invalidate the analysis.
-Therefore, we proceed with the ANOVA tests.

### 2025-03-21 paper/paper.qmd
appendix n acknowledgement

@@
 date-format: long
+abstract: Painkillers are commonly used to manage pain, but their effects extend beyond physical relief.
+While they provide immediate physical comfort, their impact on cognitive performance is often overlooked.
+This study explores how different painkillers and dosages influence cognitive function.
+Using simulated testing, participants were randomly assigned a treatment (drug type and dosage) while controlling for variables such as age.
+Our findings indicate no significant relationship between drug type, dosage, and overall cognitive performance post-treatment.
+However, we observed some correlation between certain drug-dosage combinations and memory improvement, suggesting a potential area for further research.
+While the results were not statistically significant, this study contributes to a deeper understanding of the cognitive effects of painkillers and highlights the need for further investigation into their potential impact on memory and cognition.
 number-sections: true
@@
 bibliography: references.bib
+toc: true
 ---
+
+# Acknowledgements
+
+We extend our gratitude to the academic community for their contributions to this research.No auto-complete tools such as co-pilot were used in the course of this project, however, Language Learning Model ChatGPT was used while writing this paper.
+It was used for the purpose of code debugging, understanding models, and knowledge of certain topics, which we were not aware of.
+The chat with the AI bot is also attached as a reference under @sec-appendix
 
@@
 ```{r}
+#| label: fig-variance-plot
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Q-Q Plot of Residuals"
+
+plot(anova_model, which = 3)
+```
+
+```{r}
 #| label: tbl-bartlett
@@
 # Scale-Location Plot
-plot(anova_model, which = 3)
 
@@
 ```
+
+# Appendix {#sec-appendix}
+
+```{r}
+
+library(tidyverse)
+library(janitor)
+library(here)
+library(lubridate)
+library(patchwork)
+library(arrow)
+library(dplyr)
+library(knitr)
+library(performance)
+library(modelsummary)
+library(kableExtra)
+library(performance)
+library(ggpubr)
+
+clean_data <- read.csv(here("data", "analysis_data", "clean_data.csv"))
+```
+
+```{r}
+
+# Compute statistics for Memory Game Score
+mean_game <- mean(clean_data$memory_game_score, na.rm = TRUE)
+median_game <- median(clean_data$memory_game_score, na.rm = TRUE)
+sd_game <- sd(clean_data$memory_game_score, na.rm = TRUE)
+iqr_game <- IQR(clean_data$memory_game_score, na.rm = TRUE)
+
+# Compute statistics for Memory Cards Score
+mean_cards <- mean(clean_data$memory_cards_score, na.rm = TRUE)
+median_cards <- median(clean_data$memory_cards_score, na.rm = TRUE)
+sd_cards <- sd(clean_data$memory_cards_score, na.rm = TRUE)
+iqr_cards <- IQR(clean_data$memory_cards_score, na.rm = TRUE)
+
+# Combine into a summary table
+summary_table <- data.frame(
+  Statistic = c("Mean", "Median", "SD", "IQR"),
+  `Memory Game Score` = c(mean_game, median_game, sd_game, iqr_game),
+  `Memory Cards Score` = c(mean_cards, median_cards, sd_cards, iqr_cards)
+)
+
+colnames(summary_table) <- c("Statistic", "Memory Game Score", "Memory Cards Score")
+
+# Display table
+
+kable(summary_table, format = "latex", booktabs = TRUE)
+```
+
+```{r}
+
+drug_counts <- table(clean_data$drug)
+
+# percentages
+drug_percentages <- prop.table(drug_counts) * 100
+
+#  summary dataframe
+drug_summary <- data.frame(
+  Drug = names(drug_counts),
+  Count = as.numeric(drug_counts),
+  Percentage = round(as.numeric(drug_percentages), 2)
+)
+
+# Display table
+kable(drug_summary, format = "latex", booktabs = TRUE)
+
+```
+
+```{r}
+
+dosage_counts <- table(clean_data$dosage_level)
+
+# percentage for each dosage level
+dosage_percentages <- prop.table(dosage_counts) * 100
+
+# summary dataframe
+dosage_summary <- data.frame(
+  Dosage = names(dosage_counts),
+  Count = as.numeric(dosage_counts),
+  Percentage = round(as.numeric(dosage_percentages), 2)
+)
+
+# Display table
+kable(dosage_summary, booktabs = TRUE, row.names = FALSE)
+
+```
+
+```{r}
+age_counts <- table(clean_data$age_group)
+
+# percentages for each age group
+age_percentages <- prop.table(age_counts) * 100
+
+# summary dataframe
+age_summary <- data.frame(
+  Age_Group = names(age_counts),
+  Count = as.numeric(age_counts),
+  Percentage = round(as.numeric(age_percentages), 2)
+)
+
+# Display table
+kable(age_summary, booktabs = TRUE, row.names = FALSE)
+
+```
+
+```{r}
+
+p1 <- ggplot(clean_data, aes(x = drug, y = memory_game_score, color = dosage_level, group = dosage_level)) +
+  stat_summary(fun = mean, geom = "point", size = 3) +
+  stat_summary(fun = mean, geom = "line", size = 1) +
+  labs(title = "Memory Game Scores",
+       x = "Drug Type",
+       y = "Mean Memory Game Score",
+       color = "Dosage Level") +
+  theme_minimal()
+
+# Interaction plot for Memory Cards Scores
+p2 <- ggplot(clean_data, aes(x = drug, y = memory_cards_score, color = dosage_level, group = dosage_level)) +
+  stat_summary(fun = mean, geom = "point", size = 3) +
+  stat_summary(fun = mean, geom = "line", size = 1) +
+  labs(title = "Memory Cards Scores",
+       x = "Drug Type",
+       y = "Mean Memory Cards Score",
+       color = "Dosage Level") +
+  theme_minimal()
+
+# Combine the two plots vertically
+combined_plot <- p1 / p2
+combined_plot
+```
+
+```{r}
+
+clean_data$dosage_level <- factor(clean_data$dosage_level, levels = c("Low", "High"))
+
+# Boxplot of Memory Game Scores by Drug, colored by Dosage Level
+ggplot(clean_data, aes(x = drug, y = memory_game_score, fill = dosage_level)) +
+  geom_boxplot() +
+  labs(
+    x = "Drug Type",
+    y = "Memory Game Score",
+    fill = "Dosage Level"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 14, face = "bold"),
+    axis.title = element_text(size = 12)
+  )
+
+```
+
+```{r}
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+
+ggplot(clean_data, aes(x = drug, y = memory_cards_score, fill = dosage_level)) +
+  geom_boxplot() +
+  labs(
+    x = "Drug Type",
+    y = "Memory Cards Score",
+    fill = "Dosage Level"
+  ) +
+  theme_minimal()
+```
+
+```{r}
+
+# References: https://cran.r-project.org/web/packages/broom/vignettes/broom.html
+
+library(broom)
+
+# Regression Model results
+anova_model <- lm(memory_game_score ~ drug * dosage_level, data = clean_data)
+
+model_tidy <- tidy(anova_model)
+
+kable(model_tidy, format = "latex", booktabs = TRUE)
+
+```
+
+```{r}
+
+model_glance <- glance(anova_model)
+kable(model_glance, format = "latex", booktabs = TRUE) %>%
+   kable_styling(latex_options = "scale_down")
+```
+
+```{r}
+#| warning: false
+#| message: false
+
+# Two way ANOVA result
+anova_result <- anova(anova_model)
+
+anova_table_df <- as.data.frame(anova_result)
+
+kable(anova_table_df, format = "latex", booktabs = TRUE)
+```
+
+```{r}
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Q-Q Plot of Residuals"
+
+# Normality Check
+ggqqplot(residuals(anova_model))
+```
+
+```{r}
+
+# Shapiro-Wilk Normality Test
+shapiro_test <- shapiro.test(residuals(anova_model))
+shapiro_table <- data.frame(
+  Statistic = round(shapiro_test$statistic, 4),
+  P_Value = round(shapiro_test$p.value, 4),
+  Method = shapiro_test$method
+)
+
+kable(shapiro_table, format = "latex", booktabs = TRUE)
+```
+
+```{r}
+
+plot(anova_model, which = 3)
+```

### 2025-03-22 paper/paper.qmd
update
New changes to the paper

@@
 date-format: long
-abstract: Painkillers are commonly used to manage pain, but their effects extend beyond physical relief.
+abstract: Painkillers are commonly used to manage pain, and their effects are often associated with  physical relief.
 While they provide immediate physical comfort, their impact on cognitive performance is often overlooked.
 This study explores how different painkillers and dosages influence cognitive function.
-Using simulated testing, participants were randomly assigned a treatment (drug type and dosage) while controlling for variables such as age.
+Using simulated testing from a virtual population, participants were randomly assigned a treatment (drug type and dosage) while controlling for variables such as age.
 Our findings indicate no significant relationship between drug type, dosage, and overall cognitive performance post-treatment.
@@
 
-## Relevant Background
 Pain can make everyday tasks harder, particularly when mental focus and clarity are required.
-Common pain relievers like Aspirin, Paracetamol, and Tramadol are often used to reduce physical discomfort, but their impact on cognitive functions is not well understood.
-Recalling information, a task that demands mental effort, becomes more difficult when we're in pain.
+Study has shown that individuals with pain tend to have cognitive dysfunction symptoms (Hu, 2010).
+Common pain relievers like Aspirin, Paracetamol, and Tramadol are often used to reduce physical discomfort, but their impact on cognitive functions are not well understood.
+Memory retention is a process that requires mental effort – which becomes more difficult when we're in pain.
 This study investigates how different pain relievers (Aspirin, Paracetamol, and Tramadol) at standard dosages affect memory performance.
-It also looks at how varying dosages of each drug influence memory function.
-Since the ability to recall information is essential in many situations, understanding how pain relief might impact cognitive performance is important for managing pain without affecting productivity.
+We will also look at how the interaction between drug type and dosage level influence memory function.
+Since the ability to recall information is a basis for optimized human function, understanding how pain relief might impact cognitive performance is important for managing pain without affecting productivity.
 
@@
 1. *How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg, and Placebo) affect cognitive task performance?*
+- Null Hypothesis: All pain relievers at normal dosages act the same for cognitive retention game performances.
+- Alternative Hypothesis: There exists at least one pair of distinct pain relievers at normal dosages which act differently for cognitive retention game performances.
+
 2. *How does the dosage (low vs. high) of each drug affect cognitive retention, while accounting for confounding factors like age?*
+- Null Hypothesis: There is no interaction effect between the type of pain reliever and dosage level on the improvement in memory task performance.
+- Alternative Hypothesis: There is an interaction effect between at least one of the types of pain reliever and dosage level on the improvement in memory task performance.
 
@@
 #| message: false
+#| echo: false  # Hides code
 
@@
 ```
+
+The structure of the paper is as follows: Section 2 outlines our data and methodology.
+Section 3 presents our quantitative analysis.
+In Section 4, we discuss the results and address our findings from the analysis.
+Section 5 covers the limitations of our study, and Section 6 presents a conclusion to our analysis.
+After that, we have the bibliography in Section 7.
+Lastly, we attached the code for our study into the Appendix at Section 8.
 
@@
 ```
+## Section 3: Analysis
+The method of two-way ANOVA is used to estimate the mean of a memory game score  changes according to the levels of two categorical variables that is drug and dosage level.
+The research question explores if there is an interaction effect between at least one of the types of pain reliever and dosage level on the improvement in memory task performance.
+We verified the assumption of the two-way ANOVA model as seen from graph normality, using Q-Q plot.
+The Shapiro-Wilk Test confirms a p-value = 0.05553, so we fail to reject the null hypothesis and the result confirms that the dataset is normally distributed.
+Our second assumption of Homogeneity of Variance is verified by the p-value = 0.3346 from the Bartlett test, which is greater than 0.05. Due to this, we fail to reject the null hypothesis.
+Thirdly, for our two-way ANOVA model, the different combinations of pain reliever type and dosage levels were randomly assigned to all participants, in random order. 
+The two-way ANOVA factorial design involves the linear regression model followed by the ANOVA model.
+The model uses the reference (baseline) group which is Aspirin (Drug) & High (Dosage level).
+The regression model from the ‘table’ shows the intercept(beta_0) which represents the predicted mean of memory game score for participants receiving high dosage of aspirin is 62.20 and the p-value = 0.00000 indicates the intercept is statistically significant.
+The variance explained by the model is R^2 = 0.03983, approximately 4% of the response variable.
+And the p-value = 0.2167 of the model can be interpreted as not statistically significant
+
+## Section 4: Discussion
+## Interpretation of Results  
+The two-way ANOVA analysis revealed no statistically significant main effects of drug type (p = 0.25) or dosage level (p = 0.26) on memory game scores.
+Similarly, the interaction effect between drug type and dosage level was not significant (p = 0.24).
+These results suggest that neither the type of pain reliever (Aspirin, Paracetamol, Tramadol, or Placebo) nor its dosage (low vs.
+high) had a meaningful impact on cognitive retention in this study.
+The lack of significance persisted even after accounting for age as a confounding variable, which was controlled through participant stratification into three balanced groups (18–34, 35–50, and 50+ years).
+
+### Exploratory Observations  
+Despite the absence of statistical significance, exploratory insights emerged:  
+1. **Paracetamol** showed the largest mean improvement in memory game scores (+1.33 points, Table 5), though this effect was not robust enough to reject the null hypothesis (p = 0.74).  
+2.
+**Tramadol** exhibited higher median memory scores both before and after treatment compared to other drugs (@fig-interaction).
+However, its high-dosage group saw a slight decline in mean scores (−4.88 points), hinting at a potential dosage-dependent response that warrants further investigation.
+3. The **Placebo** group consistently underperformed relative to active drugs in median scores (@fig-interaction), though this difference was not statistically significant.
+
+## Section 5: Limitations 
+Our study is overall focused on memory, which may have links to one’s education and IQ level as they are all related to mental function and cognition.
+In the future, we could test everyone for IQ scores and their highest level of education – these two nuisance variables can be taken care of by using the four principles of experimental design.
+Additionally, we used 30 observations for each treatment group which may not be large enough.
+We can increase this number for future studies.
+To add on, not all participants were in pain, so the efficacy of the improvement of pain killers may be biased and using a virtual population may not ensure whether this aspect could be captured.
+Lastly, cognitive retention was measured immediately post-treatment – the long term impacts are not yet explored.
+To improve our study, we can only consider individuals of equal pain levels before the study to ensure a reduction of bias.
+Additionally, carrying the experiment out in the long-term would help with understanding the effects of painkillers and dosages on memory.
+
+## Section 6: Conclusion
+This study found no conclusive evidence that pain relievers or their dosages significantly affect cognitive retention.
+However, the exploratory trends observed, particularly with Paracetamol and Tramadol, highlight the need for larger-scale studies to investigate subtle or context-dependent effects.
+Future research could incorporate longitudinal designs, broader age-specific analyses, and alternative cognitive metrics to deepen understanding of painkillers’ cognitive implications.
+
+## Section 7: References
+(Ha, 2010) https://journals.lww.com/ejanaesthesiology/FullText/2010/02000/Amitriptyline_rather_than_lornoxicam_ameliorates.6.aspx
+
+\newpage
 
@@
 ```{r}
-
 # Compute statistics for Memory Game Score

### 2025-03-22 paper/paper.qmd
fixed the errors

@@
 
-Evident through the results on @tbl-summary-6, Paracetamol is the drug that has the greatest mean & median improvement in the game scores after administering the drug (without dosage taken into account).
+Evident through the results, Paracetamol is the drug that has the greatest mean & median improvement in the game scores after administering the drug (without dosage taken into account).
 Aspirin appears to negatively impact the results of the game after being given to people, this was seen through the mean and median improvements.
@@
 
-@fig-boxplot-scores shows the distribution of memory game scores before and after treatment across different drug types using box plots.
+@fig-boxplot-game-scores shows the distribution of memory game scores before and after treatment across different drug types using box plots.
 
@@
 
-@fig-boxplot-cards shows the distribution of **memory card scores before and after treatment** across drug types.
+@fig-boxplot-card-scores shows the distribution of **memory card scores before and after treatment** across drug types.
 
@@
 ```
-## Section 3: Analysis
+# Section 3: Analysis
 The method of two-way ANOVA is used to estimate the mean of a memory game score  changes according to the levels of two categorical variables that is drug and dosage level.
@@
 
-## Section 4: Discussion
+# Section 4: Discussion
 ## Interpretation of Results  
@@
 
-## Section 5: Limitations 
+# Section 5: Limitations 
 Our study is overall focused on memory, which may have links to one’s education and IQ level as they are all related to mental function and cognition.
@@
 
-## Section 6: Conclusion
+# Section 6: Conclusion
 This study found no conclusive evidence that pain relievers or their dosages significantly affect cognitive retention.
@@
 
-## Section 7: References
+# Section 7: References
 (Ha, 2010) https://journals.lww.com/ejanaesthesiology/FullText/2010/02000/Amitriptyline_rather_than_lornoxicam_ameliorates.6.aspx

### 2025-03-22 paper/paper.qmd
index errors fixed

@@
 ```
-# Section 3: Analysis
+# Analysis
 The method of two-way ANOVA is used to estimate the mean of a memory game score  changes according to the levels of two categorical variables that is drug and dosage level.
@@
 
-# Section 4: Discussion
+# Discussion
 ## Interpretation of Results  
@@
 
-# Section 5: Limitations 
+# Limitations 
 Our study is overall focused on memory, which may have links to one’s education and IQ level as they are all related to mental function and cognition.
@@
 
-# Section 6: Conclusion
+# Conclusion
 This study found no conclusive evidence that pain relievers or their dosages significantly affect cognitive retention.
@@
 
-# Section 7: References
+# References
 (Ha, 2010) https://journals.lww.com/ejanaesthesiology/FullText/2010/02000/Amitriptyline_rather_than_lornoxicam_ameliorates.6.aspx

### 2025-03-22 paper/paper.qmd
final changes

@@
 ## Research Questions
-1. *How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg, and Placebo) affect cognitive task performance?*
+1. *How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg, and Placebo) affect cognitive retention game performance?*
 - Null Hypothesis: All pain relievers at normal dosages act the same for cognitive retention game performances.
@@
 
-2. *How does the dosage (low vs. high) of each drug affect cognitive retention, while accounting for confounding factors like age?*
+2. *Is there an interaction effect between the type of pain reliever and dosage level on the improvement in memory task performance?*
 - Null Hypothesis: There is no interaction effect between the type of pain reliever and dosage level on the improvement in memory task performance.
@@
 
-## Study Design  
-This study involves 2 factors, pain reliever type (4 levels) and dosage(2 levels).
-Crossing them provides us with *8 treatment groups*, with **30 participants** assigned to each.
+# Methodology
+
+In February, our group members collected observations from participants belonging to a virtual population to assess whether the treatment had any effect on memory performance, this resulted in a total of 240 observations.
+Each participant was **randomly** assigned a treatment.
+
+The experiment utilized a two-way ANOVA design, where the experimental unit was the participant, the explanatory variables were the type of painkiller and dosage level (low/high), and the response variable was the memory performance, measured by the memory game score.
+
+## Study Design and Treatments   
+We selected three brands of painkillers: Aspirin, Paracetamol, and Tramadol.
+Additionally, we considered a placebo treatment.
+As a result, this study involves 2 factors: pain reliever type (4 levels - Aspirin, Paracetamol, Tramadol, Placebo) and dosage (2 levels - Low, High).
+Crossing the two factors provides us with a total of *8 treatment groups*, with **30 participants** assigned to each.
 The groups are as follows:
@@
 
-## Confounding Variable: Age  
-To reduce bias, we consider to control the experiment by controlling participant ages to be 18+. Hence in this study **age** acts as a **confounding variable**.
-Participants will be categorized into three groups evenly to prevent bias created through age. 
+For each treatment, we selected 30 different people (n = 30).
+Through randomly picking the virtual citizens, we replicated 30 experimental units per treatment.
+The even observations per treatment group ensures we have a balanced design.
+
+### Nuisance Variable: Age  
+To reduce bias, we consider **controlling** the experiment by limiting participant ages to be strictly 18+. Hence in this study **age** acts as a **nuisance variable**.
+We also used **blocking** for age by ensuring participants were categorized into three even groups to prevent bias created through age. 
 The groups are as follows:
-
-1. 18–34 years
-2. 35–50 years
-3. 50+ years
+1. 18–34 years old.
+2. 35–50 years old.
+3. 50+ years old.
 
@@
 2. Qualitative variables: Type of pain reliever, dosage level (low/high)
-
-## Data Analysis Method   
-We will use **one-way ANOVA** to analyze the effects of different pain relievers on memory performance.
-Similarly, we will use **two-way ANOVA** to analyze the effects of different dosage levels per drug type on memory performance and cognitive retention.
 
@@
 Lastly, we attached the code for our study into the Appendix at Section 8.
-
-# Summary Statistics
 

### 2025-03-28 paper/paper.qmd
Your commit message

@@
 title: "Effects of Different Pain Relievers and Dosages on Cognitive Retention"
-subtitle: "Exploratory Data Analysis (EDA)"
+subtitle: Results
 author: 
@@
 
-We extend our gratitude to the academic community for their contributions to this research.No auto-complete tools such as co-pilot were used in the course of this project, however, Language Learning Model ChatGPT was used while writing this paper.
+No auto-complete tools such as co-pilot were used in the course of this project, however, Language Learning Model ChatGPT was used while writing this paper.
 It was used for the purpose of code debugging, understanding models, and knowledge of certain topics, which we were not aware of.
@@
 
-1. Aspirin 500 mg (Low)
-2. Aspirin 1000 mg (High)
-3. Paracetamol 500 mg (Low)
-4. Paracetamol 1000 mg (High)
-5. Tramadol 50 mg (Low)
-6. Tramadol 100 mg (High)
-7. Placebo (Low) 
-8. Placebo (High)
+```{r, echo = FALSE}
+
+library(knitr)
+library(kableExtra)
+
+# Create a dataframe for the table
+study_table <- data.frame(
+  Dosage = c("Low", "High"),
+  Aspirin = c("500 mg", "1000 mg"),
+  Paracetamol = c("500 mg", "1000 mg"),
+  Tramadol = c("50 mg", "100 mg"),
+  Placebo = c("Low", "High")
+)
+
+# Render the table
+kable(study_table, caption = "Treatment Groups",
+      align = "c") %>%
+  kable_styling(full_width = FALSE, position = "center")
+```
 
@@
 To reduce bias, we consider **controlling** the experiment by limiting participant ages to be strictly 18+. Hence in this study **age** acts as a **nuisance variable**.
-We also used **blocking** for age by ensuring participants were categorized into three even groups to prevent bias created through age. 
-The groups are as follows:
-1. 18–34 years old.
-2. 35–50 years old.
-3. 50+ years old.
+We also used **blocking** for age by ensuring participants were categorized into three even groups to prevent bias created through age. @tbl-summary-5 shows the breakdown.
 
@@
 clean_data <- read.csv(here("data", "analysis_data", "clean_data.csv"))
+
+```
+
+```{r}
+#| label: tbl-summary-5
+#| tbl-cap: "Summary of Age Groups"
+#| echo: false
+#| warning: false
+#| message: false
+
+age_counts <- table(clean_data$age_group)
+
+# percentages for each age group
+age_percentages <- prop.table(age_counts) * 100
+
+# summary dataframe
+age_summary <- data.frame(
+  `Age Group` = names(age_counts),
+  Count = as.numeric(age_counts),
+  Percentage = round(as.numeric(age_percentages), 2)
+)
+
+colnames(age_summary)[colnames(age_summary) == "Age.Group"] <- "Age Group"
+
+# Display table
+kable(age_summary, booktabs = TRUE, row.names = FALSE)
 
@@
 
-```{r}
-#| label: tbl-summary-5
-#| tbl-cap: "Summary of Age Groups"
-#| echo: false
-#| warning: false
-#| message: false
-
-age_counts <- table(clean_data$age_group)
-
-# percentages for each age group
-age_percentages <- prop.table(age_counts) * 100
-
-# summary dataframe
-age_summary <- data.frame(
-  Age_Group = names(age_counts),
-  Count = as.numeric(age_counts),
-  Percentage = round(as.numeric(age_percentages), 2)
-)
-
-# Display table
-kable(age_summary, booktabs = TRUE, row.names = FALSE)
-
-```
-
 ## Summary of counts and percentage for qualitative variables
@@
 
-## Confounding Variable
-
-@tbl-summary-5 shows the breakdown of age groups, which is a confounding variable in this study. The three age groups: 18–34, 35–50, and 50+ each have 80 participants (33.33\%).
+# Plots
 
@@
 #| message: false
-#| fig.width: 9
-#| fig.height: 8
+#| fig.width: 12  # Increased width
+#| fig.height: 5  # Reduced height
 #| dpi: 300
-#| fig-cap: "Interaction Plot: Drug Type vs. Dosage Level"
+#| fig-cap: "Interaction Plots: Drug Type vs. Dosage Level"
+
+library(ggplot2)
+library(patchwork)  # For arranging plots
 
 p1 <- ggplot(clean_data, aes(x = drug, y = memory_game_score, color = dosage_level, group = dosage_level)) +
-  stat_summary(fun = mean, geom = "point", size = 3) +
+  stat_summary(fun = mean, geom = "point", size = 2) +
   stat_summary(fun = mean, geom = "line", size = 1) +
@@
 
-# Interaction plot for Memory Cards Scores
 p2 <- ggplot(clean_data, aes(x = drug, y = memory_cards_score, color = dosage_level, group = dosage_level)) +
-  stat_summary(fun = mean, geom = "point", size = 3) +
+  stat_summary(fun = mean, geom = "point", size = 2) +
   stat_summary(fun = mean, geom = "line", size = 1) +
@@
 
-# Combine the two plots vertically
-combined_plot <- p1 / p2
-combined_plot
+# Arrange plots side by side with better spacing
+p1 + p2 + plot_layout(widths = c(1, 1))
+
 ```
-
-# Plots
 
@@
 #| message: false
-#| fig.width: 9
-#| fig.height: 8
+#| fig.width: 12  # Increased width
+#| fig.height: 5  # Reduced height
 #| dpi: 300
-#| fig-cap: "Memory Game Scores by Drug Type and Dosage Level"
+#| fig-cap: "Boxplots: Memory Game & Cards Scores by Drug Type and Dosage Level"
 
-clean_data$dosage_level <- factor(clean_data$dosage_level, levels = c("Low", "High"))
+p3 <- ggplot(clean_data, aes(x = drug, y = memory_game_score, fill = dosage_level)) +
+  geom_boxplot() +
+  labs(x = "Drug Type", y = "Memory Game Score", fill = "Dosage Level") +
+  theme_minimal()
 
-# Boxplot of Memory Game Scores by Drug, colored by Dosage Level
-ggplot(clean_data, aes(x = drug, y = memory_game_score, fill = dosage_level)) +
+p4 <- ggplot(clean_data, aes(x = drug, y = memory_cards_score, fill = dosage_level)) +
   geom_boxplot() +
-  labs(
-    x = "Drug Type",
-    y = "Memory Game Score",
-    fill = "Dosage Level"
-  ) +
-  theme_minimal() +
-  theme(
-    plot.title = element_text(size = 14, face = "bold"),
-    axis.title = element_text(size = 12)
-  )
+  labs(x = "Drug Type", y = "Memory Cards Score", fill = "Dosage Level") +
+  theme_minimal()
 
-```
-
-```{r}
-#| label: fig-boxplot-card-scores
-#| echo: false
-#| warning: false
-#| message: false
-#| fig.width: 9
-#| fig.height: 8
-#| dpi: 300
-#| fig-cap: "Memory Game Scores by Drug Type and Dosage Level"
-
-ggplot(clean_data, aes(x = drug, y = memory_cards_score, fill = dosage_level)) +
-  geom_boxplot() +
-  labs(
-    x = "Drug Type",
-    y = "Memory Cards Score",
-    fill = "Dosage Level"
-  ) +
-  theme_minimal()
+# Arrange boxplots side by side with better spacing
+p3 + p4 + plot_layout(widths = c(1, 1))
 
@@
 
-@fig-boxplot-card-scores shows the distribution of **memory card scores before and after treatment** across drug types.
+@fig-boxplot-game-scores on right, shows the distribution of **memory card scores before and after treatment** across drug types.
 
@@
 
-```{r}
+```{r, echo = FALSE}
 #| label: tbl-model-result
@@
 
-```{r}
+```{r, echo = FALSE}
 #| label: tbl-model-fit
@@
 
-```{r}
+```{r, echo = FALSE}
 #| label: tbl-anova-model
@@
 
-```{r}
+```{r, echo = FALSE}
 #| label: fig-normal-plot
@@
 #| message: false
-#| fig.width: 9
-#| fig.height: 8
+#| fig.width: 6  # Reduced width
+#| fig.height: 5  # Reduced height
 #| dpi: 300
+#| fig.align: "center"
 #| fig-cap: "Q-Q Plot of Residuals"
@@
 ggqqplot(residuals(anova_model))
+
 ```
 
-```{r}
+```{r, echo = FALSE}
 #| label: tbl-shapiro
@@
   Statistic = round(shapiro_test$statistic, 4),
-  P_Value = round(shapiro_test$p.value, 4),
-  Method = shapiro_test$method
+  `P-Value` = round(shapiro_test$p.value, 4),
+  Method = shapiro_test$method,
+  check.names = FALSE  # Prevents automatic renaming
 )
@@
 #| message: false
-#| fig.width: 9
-#| fig.height: 8
+#| fig.width: 6  # Smaller width
+#| fig.height: 5  # Smaller height
 #| dpi: 300
@@
 
-plot(anova_model, which = 3)
+plot(anova_model, which = 3, main = "", sub = "", caption = "")
+
 ```
@@
   DF = bartlett_test$parameter,
-  P_Value = round(bartlett_test$p.value, 4),
-  Method = bartlett_test$method
+  `P-Value` = round(bartlett_test$p.value, 4),
+  Method = bartlett_test$method,
+  check.names = FALSE
 )
@@
 These results suggest that neither the type of pain reliever (Aspirin, Paracetamol, Tramadol, or Placebo) nor its dosage (low vs.
-high) had a meaningful impact on cognitive retention in this study.
+high) had a meaningful impact on memory game or card scores representative of cognitive improvement in this study.
 The lack of significance persisted even after accounting for age as a confounding variable, which was controlled through participant stratification into three balanced groups (18–34, 35–50, and 50+ years).
@@
 Lastly, cognitive retention was measured immediately post-treatment – the long term impacts are not yet explored.
-To improve our study, we can only consider individuals of equal pain levels before the study to ensure a reduction of bias.
+To improve our study, we can try to  consider individuals with real pain symptoms before the study to ensure a reduction of bias, and provide a realistic test setting.
 Additionally, carrying the experiment out in the long-term would help with understanding the effects of painkillers and dosages on memory.
@@
 age_summary <- data.frame(
-  Age_Group = names(age_counts),
+  `Age Group` = names(age_counts),
   Count = as.numeric(age_counts),
@@
 )
+colnames(age_summary)[colnames(age_summary) == "Age.Group"] <- "Age Group"
 
@@
 
-```{r}
+```{r, echo = FALSE}
 

### 2025-03-31 paper/paper.qmd
fixed plots and feedback fixes x2

@@
 ## Research Questions
-1. *How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg, and Placebo) affect cognitive retention game performance?*
+1. *How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg, and Placebo) affect memory game performance?*
 - Null Hypothesis: All pain relievers at normal dosages act the same for cognitive retention game performances.
@@
 
-2. *Is there an interaction effect between the type of pain reliever and dosage level on the improvement in memory task performance?*
+2. *Is there an interaction effect between the type of pain reliever and dosage level on the improvement in memory game performance?*
 - Null Hypothesis: There is no interaction effect between the type of pain reliever and dosage level on the improvement in memory task performance.
@@
 ### Nuisance Variable: Age  
-To reduce bias, we consider **controlling** the experiment by limiting participant ages to be strictly 18+. Hence in this study **age** acts as a **nuisance variable**.
-We also used **blocking** for age by ensuring participants were categorized into three even groups to prevent bias created through age. @tbl-summary-5 shows the breakdown.
+To reduce bias, we consider **controlling** the experiment by limiting participant ages to be strictly 18+. Hence in this study, **age** acts as a **nuisance variable**.
+We also used **blocking** for age by ensuring participants were categorized into three even groups to prevent bias created through age. @tbl-summary-5 shows the breakdown of the groups.
 
@@
 After that, we have the bibliography in Section 7.
-Lastly, we attached the code for our study into the Appendix at Section 8.
+Lastly, we attached the code for our study into the Appendix in Section 8.
 
@@
 
+\newpage
 # Plots
+
+```{r, echo=FALSE}
+#| label: fig-boxplot-game-scores
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 6
+#| fig.height: 5
+#| dpi: 300
+#| out.width: 60%   # Adjust output width to 60% of the page width
+#| out.height: 40%  # Adjust output height to 40% of the page height
+#| fig-cap: "Boxplots: Memory Game Scores by Drug Type and Dosage Level"
+#| layout-ncol: 2  # Ensures plots are side by side
+
+p3 <- ggplot(clean_data, aes(x = drug, y = memory_game_score, fill = dosage_level)) +
+  geom_boxplot() +
+  labs(x = "Drug Type", y = "Memory Game Score", fill = "Dosage Level") +
+  theme_minimal()
+p3 
+```
 
@@
 #| message: false
-#| fig.width: 12  # Increased width
+#| fig.width: 6  # Increased width
 #| fig.height: 5  # Reduced height
 #| dpi: 300
-#| fig-cap: "Interaction Plots: Drug Type vs. Dosage Level"
+#| fig-cap: "Interaction Plot: Drug Type vs. Dosage Level"
+#| layout-ncol: 2  # Ensures plots are side by side
 
@@
 
-p2 <- ggplot(clean_data, aes(x = drug, y = memory_cards_score, color = dosage_level, group = dosage_level)) +
-  stat_summary(fun = mean, geom = "point", size = 2) +
-  stat_summary(fun = mean, geom = "line", size = 1) +
-  labs(title = "Memory Cards Scores",
-       x = "Drug Type",
-       y = "Mean Memory Cards Score",
-       color = "Dosage Level") +
-  theme_minimal()
-
 # Arrange plots side by side with better spacing
-p1 + p2 + plot_layout(widths = c(1, 1))
+p1
 
 ```
-
 ```{r}
-#| label: fig-boxplot-game-scores
+#| label: fig-combined
 #| echo: false
@@
 #| message: false
-#| fig.width: 12  # Increased width
-#| fig.height: 5  # Reduced height
-#| dpi: 300
-#| fig-cap: "Boxplots: Memory Game & Cards Scores by Drug Type and Dosage Level"
+#| fig.width: 12
+#| fig.height: 6
+#| fig-cap: "Interaction Plot and Boxplot: Memory Game Scores by Drug Type and Dosage Level"
 
-p3 <- ggplot(clean_data, aes(x = drug, y = memory_game_score, fill = dosage_level)) +
-  geom_boxplot() +
-  labs(x = "Drug Type", y = "Memory Game Score", fill = "Dosage Level") +
-  theme_minimal()
-
-p4 <- ggplot(clean_data, aes(x = drug, y = memory_cards_score, fill = dosage_level)) +
-  geom_boxplot() +
-  labs(x = "Drug Type", y = "Memory Cards Score", fill = "Dosage Level") +
-  theme_minimal()
-
-# Arrange boxplots side by side with better spacing
-p3 + p4 + plot_layout(widths = c(1, 1))
-
+# Combine the plots side by side
+p1 + p3
 ```
 
-## Game Score Distribution Before and After Treatment
+## Game Score Distribution by Drug and Dosage Level
 
-@fig-boxplot-game-scores shows the distribution of memory game scores before and after treatment across different drug types using box plots.
+@fig-combined shows the distribution of memory game scores across different drug types using box plots.
 
-1. The median scores for all drugs appear similar before treatment.
-2. Tramadol has a higher median than other drugs both before and after treatment.
+1. The median scores for all drugs appear similar.
+2. All drugs have a higher median on the higher dosage, level expect for Tramadol which is lower.
 3. The Placebo group has a slightly lower median score compared to other drugs.
-4. There is one outlier in the Tramadol group before treatment.
-5. The (IQR) is **similar across all drug types**, though Tramadol sees a decrease in its IQR in the memory game scores after treatment.
+4. The (IQR) is **similar across all drug types**, though Tramadol and Placebo see a higher IQR in the memory game scores in the high dosage.
 
-These boxplots provide an initial comparison of cognitive performance changes before and after drug administration.
-
-## Memory Card Score Distribution Before and After Treatment
-
-@fig-boxplot-game-scores on right, shows the distribution of **memory card scores before and after treatment** across drug types.
-
-1. Before treatment, the scores are relatively high across all groups, with Paracetamol and Placebo showing slightly higher medians than the others.
-2. After treatment, the distributions remain similar, though there is a slight increase in spread for Aspirin, Paracetamol, and Placebo.
-3. There is a slight decrease in the IQR of Tramadol. 
-3. Outliers are present in all groups, indicating some variability in memory card performance across individuals.
+This boxplot provides an initial comparison of memory game performance and drug administration.
 
@@
 ## Model
+Let Y denote the memory game score, then
 
 $$
-\text{memory\_game\_score}_i = \beta_0 + \beta_1 \cdot \text{drug}_i + \beta_2 \cdot \text{dosage\_level}_i + \beta_3 \cdot (\text{drug}_i \times \text{dosage\_level}_i) + \varepsilon_i
+\text{Y}_i = \beta_0 + \beta_1 \cdot \text{drug}_i + \beta_2 \cdot \text{dosage\_level}_i + \beta_3 \cdot (\text{drug}_i \times \text{dosage\_level}_i) + \varepsilon_i
 $$
@@
 #| message: false
-#| fig.width: 6  # Reduced width
-#| fig.height: 5  # Reduced height
+#| fig.width: 9  # Reduced width
+#| fig.height: 8  # Reduced height
 #| dpi: 300
+#| out.width: 60%
+#| out.height: 50%
 #| fig.align: "center"
@@
 #| message: false
-#| fig.width: 6  # Smaller width
-#| fig.height: 5  # Smaller height
+#| fig.width: 9  # Smaller width
+#| fig.height: 8  # Smaller height
+#| out.width: 60%
+#| out.height: 50%
 #| dpi: 300
@@
 # Analysis
-The method of two-way ANOVA is used to estimate the mean of a memory game score  changes according to the levels of two categorical variables that is drug and dosage level.
-The research question explores if there is an interaction effect between at least one of the types of pain reliever and dosage level on the improvement in memory task performance.
-We verified the assumption of the two-way ANOVA model as seen from graph normality, using Q-Q plot.
-The Shapiro-Wilk Test confirms a p-value = 0.05553, so we fail to reject the null hypothesis and the result confirms that the dataset is normally distributed.
-Our second assumption of Homogeneity of Variance is verified by the p-value = 0.3346 from the Bartlett test, which is greater than 0.05. Due to this, we fail to reject the null hypothesis.
+The method of two-way ANOVA is used to estimate the mean of a memory game score changes according to the levels of two categorical variables, being drug type and dosage level.
+Our research question explores if there is an interaction effect between at least one of the types of pain reliever and dosage level on the improvement in memory task performance.
+
+We verified the assumption of the two-way ANOVA model as seen from graph normality, using Q-Q plot as seen in @fig-normal-plot.
+The Shapiro-Wilk Test confirms a p-value = 0.05553 as per @tbl-shapiro, so we fail to reject the null hypothesis and the result confirms that the data-set is normally distributed.
+Our second assumption of Homogeneity of Variance is verified by the p-value = 0.3346 from the Bartlett test in @tbl-bartlett, which is greater than 0.05.
+Due to this, we fail to reject the null hypothesis.
 Thirdly, for our two-way ANOVA model, the different combinations of pain reliever type and dosage levels were randomly assigned to all participants, in random order.
+
 The two-way ANOVA factorial design involves the linear regression model followed by the ANOVA model.
 The model uses the reference (baseline) group which is Aspirin (Drug) & High (Dosage level).
-The regression model from the ‘table’ shows the intercept(beta_0) which represents the predicted mean of memory game score for participants receiving high dosage of aspirin is 62.20 and the p-value = 0.00000 indicates the intercept is statistically significant.
+The regression model from the @tbl-model-result shows the intercept(beta_0) which represents the predicted mean of memory game score for participants receiving high dosage of aspirin is 62.20 and the p-value = 0.00000 indicates the intercept is statistically significant.
 The variance explained by the model is R^2 = 0.03983, approximately 4% of the response variable.
@@
 These results suggest that neither the type of pain reliever (Aspirin, Paracetamol, Tramadol, or Placebo) nor its dosage (low vs.
-high) had a meaningful impact on memory game or card scores representative of cognitive improvement in this study.
+high) had a meaningful impact on memory game scores, which is representative of cognitive improvement in this study.
 The lack of significance persisted even after accounting for age as a confounding variable, which was controlled through participant stratification into three balanced groups (18–34, 35–50, and 50+ years).
-
-### Exploratory Observations  
-Despite the absence of statistical significance, exploratory insights emerged:  
-1. **Paracetamol** showed the largest mean improvement in memory game scores (+1.33 points, Table 5), though this effect was not robust enough to reject the null hypothesis (p = 0.74).  
-2.
-**Tramadol** exhibited higher median memory scores both before and after treatment compared to other drugs (@fig-interaction).
-However, its high-dosage group saw a slight decline in mean scores (−4.88 points), hinting at a potential dosage-dependent response that warrants further investigation.
-3. The **Placebo** group consistently underperformed relative to active drugs in median scores (@fig-interaction), though this difference was not statistically significant.
 
@@
 ```{r}
-#| fig.width: 9
-#| fig.height: 8
+#| fig.width: 4
+#| fig.height: 3
+#| out.width: 40%
+#| out.height: 40%
 #| dpi: 300
@@
 ```{r}
+
+#| fig.width: 9
+#| fig.height: 8
+#| dpi: 300
+#| fig-cap: "Q-Q Plot of Residuals"
 

### 2025-04-01 paper/paper.qmd
feedback fixes, streamlined tables, equations fixed x3

@@
 ## Research Questions
-1. *How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg, and Placebo) affect memory game performance?*
-- Null Hypothesis: All pain relievers at normal dosages act the same for cognitive retention game performances.
-- Alternative Hypothesis: There exists at least one pair of distinct pain relievers at normal dosages which act differently for cognitive retention game performances.
+1. *How does the type of drug (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg, and Placebo) affect memory game performance?*
+- Null Hypothesis: All drug types at normal dosages act the same for cognitive retention game performances.
+- Alternative Hypothesis: There exists at least one pair of distinct drug types at normal dosages which act differently for cognitive retention game performances.
 
 2. *Is there an interaction effect between the type of pain reliever and dosage level on the improvement in memory game performance?*
-- Null Hypothesis: There is no interaction effect between the type of pain reliever and dosage level on the improvement in memory task performance.
-- Alternative Hypothesis: There is an interaction effect between at least one of the types of pain reliever and dosage level on the improvement in memory task performance.
+- Null Hypothesis: There is no interaction effect between the type of drug and dosage level on the improvement in memory task performance.
+- Alternative Hypothesis: There is an interaction effect between at least one of the types of drug and dosage level on the improvement in memory task performance.
 
@@
 Additionally, we considered a placebo treatment.
-As a result, this study involves 2 factors: pain reliever type (4 levels - Aspirin, Paracetamol, Tramadol, Placebo) and dosage (2 levels - Low, High).
+As a result, this study involves 2 factors: drug type (4 levels - Aspirin, Paracetamol, Tramadol, Placebo) and dosage (2 levels - Low, High).
 Crossing the two factors provides us with a total of *8 treatment groups*, with **30 participants** assigned to each.
@@
 To reduce bias, we consider **controlling** the experiment by limiting participant ages to be strictly 18+. Hence in this study, **age** acts as a **nuisance variable**.
-We also used **blocking** for age by ensuring participants were categorized into three even groups to prevent bias created through age. @tbl-summary-5 shows the breakdown of the groups.
+We also used **blocking** for age by ensuring participants were categorized into three even groups to prevent bias created through age.These groups are 18-34, 35-50, and 50+.
 
@@
 1. Quantitative variables: Memory Game Scores, Memory Test Cards Scores 
-2. Qualitative variables: Type of pain reliever, dosage level (low/high)
+2. Qualitative variables: Type of drug, dosage level (low/high)
 
@@
 
-```{r}
-#| label: tbl-summary-5
-#| tbl-cap: "Summary of Age Groups"
-#| echo: false
-#| warning: false
-#| message: false
-
-age_counts <- table(clean_data$age_group)
-
-# percentages for each age group
-age_percentages <- prop.table(age_counts) * 100
-
-# summary dataframe
-age_summary <- data.frame(
-  `Age Group` = names(age_counts),
-  Count = as.numeric(age_counts),
-  Percentage = round(as.numeric(age_percentages), 2)
-)
-
-colnames(age_summary)[colnames(age_summary) == "Age.Group"] <- "Age Group"
-
-# Display table
-kable(age_summary, booktabs = TRUE, row.names = FALSE)
-
-```
-
 The structure of the paper is as follows: Section 2 outlines our data and methodology.
@@
 The median game scores remain close to the mean, and the IQR (Interquartile Range) is smaller than the SD.
-The cards memory task shows little change before and after treatment, suggesting that pain relievers may not have a major effect on this specific task.
+The cards memory task shows little change before and after treatment, suggesting that drug types may not have a major effect on this specific task.
 
@@
 
-```{r}
-#| label: tbl-summary-3
-#| tbl-cap: "Summary of Dosage Levels"
-#| echo: false
-#| warning: false
-#| message: false
-
-dosage_counts <- table(clean_data$dosage_level)
-
-# percentage for each dosage level
-dosage_percentages <- prop.table(dosage_counts) * 100
-
-# summary dataframe
-dosage_summary <- data.frame(
-  Dosage = names(dosage_counts),
-  Count = as.numeric(dosage_counts),
-  Percentage = round(as.numeric(dosage_percentages), 2)
-)
-
-# Display table
-kable(dosage_summary, booktabs = TRUE, row.names = FALSE)
-
-```
-
 ## Summary of counts and percentage for qualitative variables
@@
 @tbl-summary-2 shows the distribution of participants across drug types. Aspirin, Paracetamol, and Tramadol, and Placebo each have 60 participants (25\%), ensuring balance.
-
-@tbl-summary-3 shows the dosage levels assigned to participants. There is an equal split between high-dose (120 participants, 50\%) and low-dose (120 participants, 50\%) conditions.
 
@@
 $$
-\text{Y}_i = \beta_0 + \beta_1 \cdot \text{drug}_i + \beta_2 \cdot \text{dosage\_level}_i + \beta_3 \cdot (\text{drug}_i \times \text{dosage\_level}_i) + \varepsilon_i
+\text{Y}_i = \beta_0 + \beta_1 \cdot \text{X}_i + \beta_2 \cdot \text{Z}_i + \beta_3 \cdot (\text{X}_i \times \text{Z}_i) + \varepsilon_i
 $$
@@
 - $\beta_0$ is the intercept.
-
+- $X_i$ is the dummy variable for drug type.
+- $Z_i$ is the dummy variable for dosage level.
 - $\beta_1$, $\beta_2$, and $\beta_3$ are coefficients for the predictors and interaction term.
-
 - $\varepsilon_i$ is the random error term.
@@
 The method of two-way ANOVA is used to estimate the mean of a memory game score changes according to the levels of two categorical variables, being drug type and dosage level.
-Our research question explores if there is an interaction effect between at least one of the types of pain reliever and dosage level on the improvement in memory task performance.
+Our research question explores if there is an interaction effect between at least one of the types of drug types and dosage level on the improvement in memory task performance.
 
@@
 Due to this, we fail to reject the null hypothesis.
-Thirdly, for our two-way ANOVA model, the different combinations of pain reliever type and dosage levels were randomly assigned to all participants, in random order.
+Thirdly, for our two-way ANOVA model, the different combinations of drug type and dosage levels were randomly assigned to all participants, in random order.
 
@@
 Similarly, the interaction effect between drug type and dosage level was not significant (p = 0.24).
-These results suggest that neither the type of pain reliever (Aspirin, Paracetamol, Tramadol, or Placebo) nor its dosage (low vs.
+These results suggest that neither the type of drug (Aspirin, Paracetamol, Tramadol, or Placebo) nor its dosage (low vs.
 high) had a meaningful impact on memory game scores, which is representative of cognitive improvement in this study.
@@
 # Conclusion
-This study found no conclusive evidence that pain relievers or their dosages significantly affect cognitive retention.
+This study found no conclusive evidence that drug types or their dosages significantly affect cognitive retention.
 However, the exploratory trends observed, particularly with Paracetamol and Tramadol, highlight the need for larger-scale studies to investigate subtle or context-dependent effects.

### 2025-04-02 paper/paper.qmd
model changes

--- 2025-03-31 paper/paper.qmd
@@
 ## Model
-Let Y denote the memory game score, then
+
+We model the memory game score using a two-way ANOVA with interaction between drug type and dosage level. The general statistical form of the model is
 
 $$
-\text{Y}_i = \beta_0 + \beta_1 \cdot \text{drug}_i + \beta_2 \cdot \text{dosage\_level}_i + \beta_3 \cdot (\text{drug}_i \times \text{dosage\_level}_i) + \varepsilon_i
+Y_{ijk} = \mu + \alpha_i + \beta_j + (\alpha\beta)_{ij} + \varepsilon_{ijk}
 $$
 
-Where:
+Where
 
-- $\beta_0$ is the intercept.
+- $Y_{ijk}$: Memory score for the $k$-th participant receiving the $i$-th drug and $j$-th dosage level  
+- $\mu$: Overall mean  
+- $\alpha_i$: Effect of the $i$-th drug (categorical with 4 levels)  
+- $\beta_j$: Effect of the $j$-th dosage level (categorical with 2 levels)  
+- $(\alpha\beta)_{ij}$: Interaction effect between drug and dosage  
+- $\epsilon_{ijk} \sim N(0, \sigma^2)$ : Random error
 
-- $\beta_1$, $\beta_2$, and $\beta_3$ are coefficients for the predictors and interaction term.
+After dummy coding the categorical variables, the model used in our analysis can be expressed as:
 
-- $\varepsilon_i$ is the random error term.
+ \begin{align*}
+Y_i =\ & \beta_0 
++ \beta_1 \cdot \text{Paracetamol}_i 
++ \beta_2 \cdot \text{Placebo}_i 
++ \beta_3 \cdot \text{Tramadol}_i \\
+& + \beta_4 \cdot \text{LowDosage}_i 
++ \beta_5 \cdot (\text{Paracetamol}_i \times \text{LowDosage}_i) \\
+& + \beta_6 \cdot (\text{Placebo}_i \times \text{LowDosage}_i) 
++ \beta_7 \cdot (\text{Tramadol}_i \times \text{LowDosage}_i)
++ \varepsilon_i
+\end{align*}
+
+Where
+
+- $\beta_0$: Intercept (Aspirin at High dosage — the reference group)  
+- $\beta_1, \beta_2, \beta_3$: Main effects of Paracetamol, Placebo, and Tramadol relative to Aspirin  
+- $\beta_4$: Effect of Low dosage relative to High  
+- $\beta_5, \beta_6, \beta_7$: Interaction effects for each drug under Low dosage  
+- $\epsilon_i$: Residual error for the $i$-th participant
 
@@
 #| label: tbl-model-result
-#| tbl-cap: "Regression Results for Memory Game Score"
+#| tbl-cap: "Coefficient Estimates from Linear Model for Memory Game Score"
 #| echo: false
@@
 
-# Regression Model results
 anova_model <- lm(memory_game_score ~ drug * dosage_level, data = clean_data)
 
-model_tidy <- tidy(anova_model)
+model_tidy <- tidy(anova_model) %>%
+  rename(
+    `Predictor Term` = term,
+    `Estimate` = estimate,
+    `Std. Error` = std.error,
+    `t-statistic` = statistic,
+    `p-value` = p.value
+  )
 
 kable(model_tidy, format = "latex", booktabs = TRUE)
-
 ```
@@
 #| label: tbl-model-fit
-#| tbl-cap: "Model Fit Statistics for Memory Game Score"
+#| tbl-cap: "Model Summary Statistics for Memory Game Score"
 #| echo: false
@@
 
-model_glance <- glance(anova_model)
+model_glance <- glance(anova_model) %>%
+  transmute(
+    `F-Statistic` = statistic,
+    `Model df` = df,
+    `Residual df` = df.residual,
+    `p-value` = p.value,
+    `Residual Std. Error` = sigma,
+    `Sample Size (n)` = nobs
+  )
+
 kable(model_glance, format = "latex", booktabs = TRUE) %>%
   kable_styling(latex_options = "scale_down")
+
 ```
-
-$$
-Y_{ijk} = \mu + \alpha_i + \beta_j + (\alpha\beta)_{ij} + \varepsilon_{ijk}
-$$
-
-Where:
-
-- $Y_{ijk}$: Memory score
-- $\mu$: Overall mean  
-- $\alpha_i$: Effect of the $i^{\text{th}}$ drug  
-- $\beta_j$: Effect of the $j^{\text{th}}$ dosage level  
-- $(\alpha\beta)_{ij}$: Interaction effect between drug and dosage  
-- $\varepsilon_{ijk} \sim \mathcal{N}(0, \sigma^2)$: Random error
 

### 2025-04-02 paper/paper.qmd
fixed model

@@
 - $\mu$: Overall mean  
-- $\alpha_i$: Effect of the $i$-th drug (categorical with 4 levels)  
-- $\beta_j$: Effect of the $j$-th dosage level (categorical with 2 levels)  
+- $\alpha_i$: Effect of the $i$-th drug ((Aspirin, Tramadol, Paracetamol, Placebo))  
+- $\beta_j$: Effect of the $j$-th dosage level (High Dosage, Low dosage) 
 - $(\alpha\beta)_{ij}$: Interaction effect between drug and dosage  
@@
 
+\newpage
+
 # References
-(Ha, 2010) https://journals.lww.com/ejanaesthesiology/FullText/2010/02000/Amitriptyline_rather_than_lornoxicam_ameliorates.6.aspx
 

### 2025-04-02 paper/paper.qmd
Added Section 5.1 Model and section 5.2 assumption check.

@@
 
-# Assumptions
+# Analysis
 
@@
 
-We model the memory game score using a two-way ANOVA with interaction between drug type and dosage level. The general statistical form of the model is
+The method of Wwo-way ANOVA is used to estimate the mean of a memory game score changes according to the levels of two categorical variables that is drug and dosage level.
+The general statistical form of the model is:
 
@@
 
-After dummy coding the categorical variables, the model used in our analysis can be expressed as:
+In this analysis where our focus in on Two-Way ANOVA Model and so we fit using linear regression model using dummy variable coding using Treatment Aspirin-High dosage as the baseline group.
+The aim is to interpret estimated coefficients relative to reference group.
+The model we used in our analysis can be expressed as:
 
@@
 - $\epsilon_i$: Residual error for the $i$-th participant
+
+The Intercept term $\beta_0$ accounts for the reference group.
+All other coefficients $\beta_j$ represent the mean difference between the specified group and the reference group, holding other factors constant for j = *1, 2, 3, 4, 5, 6, 7*
 
@@
 ```
-# Analysis
-The method of two-way ANOVA is used to estimate the mean of a memory game score changes according to the levels of two categorical variables, being drug type and dosage level.
-Our research question explores if there is an interaction effect between at least one of the types of pain reliever and dosage level on the improvement in memory task performance.
 
-We verified the assumption of the two-way ANOVA model as seen from graph normality, using Q-Q plot as seen in @fig-normal-plot.
-The Shapiro-Wilk Test confirms a p-value = 0.05553 as per @tbl-shapiro, so we fail to reject the null hypothesis and the result confirms that the data-set is normally distributed.
-Our second assumption of Homogeneity of Variance is verified by the p-value = 0.3346 from the Bartlett test in @tbl-bartlett, which is greater than 0.05.
+## Assumption Checks
+
+We verified the assumption of the two-way ANOVA model as seen from using Q-Q plot as seen in @fig-normal-plot.
+The Shapiro-Wilk Test confirms a p-value = 0.05553 as per @tbl-shapiro, so we fail to reject the null hypothesis and the result confirms that the dataset is *normally distributed*.
+Our second assumption of *homogeneity of variance* is verified by the p-value = 0.3346 from the Bartlett test in @tbl-bartlett, which is greater than 0.05.
 Due to this, we fail to reject the null hypothesis.
-Thirdly, for our two-way ANOVA model, the different combinations of pain reliever type and dosage levels were randomly assigned to all participants, in random order.
+Thirdly, for our two-way ANOVA model, the different combinations of pain reliever type and dosage levels, the treatments were randomly assigned to all participants which ensures *independence*.
 
-The two-way ANOVA factorial design involves the linear regression model followed by the ANOVA model.
+## need to work on it
+"The two-way ANOVA factorial design involves the linear regression model followed by the ANOVA model.
 The model uses the reference (baseline) group which is Aspirin (Drug) & High (Dosage level).
@@
 The variance explained by the model is R^2 = 0.03983, approximately 4% of the response variable.
-And the p-value = 0.2167 of the model can be interpreted as not statistically significant
+And the p-value = 0.2167 of the model can be interpreted as not statistically significant"
 

### 2025-04-02 paper/paper.qmd
References fixed
Format changes

@@
 title: "Effects of Different Pain Relievers and Dosages on Cognitive Retention"
-subtitle: Results
 author: 
@@
 
-No auto-complete tools such as co-pilot were used in the course of this project, however, Language Learning Model ChatGPT was used while writing this paper.
+No auto-complete tools such as co-pilot were used in the course of this project, however, the Language Learning Model 'ChatGPT' was used while writing this paper.
 It was used for the purpose of code debugging, understanding models, and knowledge of certain topics, which we were not aware of.
-The chat with the AI bot is also attached as a reference under @sec-appendix
+The chat with the AI bot is also attached as a reference under @sec-appendix.
 
@@
 Pain can make everyday tasks harder, particularly when mental focus and clarity are required.
-Study has shown that individuals with pain tend to have cognitive dysfunction symptoms (Hu, 2010).
+Study has shown that individuals with pain tend to have cognitive dysfunction symptoms [@Hu].
 Common pain relievers like Aspirin, Paracetamol, and Tramadol are often used to reduce physical discomfort, but their impact on cognitive functions are not well understood.
@@
 ## Research Questions
-1. *How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg, and Placebo) affect memory game performance?*
+
+Research Question 1.
+*How does the type of pain reliever (Aspirin 500 mg, Paracetamol 500 mg, Tramadol 50 mg, and Placebo) affect memory game performance?*
+
 -   Null Hypothesis: All pain relievers at normal dosages act the same for cognitive retention game performances.
@@
 
-2. *Is there an interaction effect between the type of pain reliever and dosage level on the improvement in memory game performance?*
+Research Question 2.
+*Is there an interaction effect between the type of pain reliever and dosage level on the improvement in memory game performance?*
+
 -   Null Hypothesis: There is no interaction effect between the type of pain reliever and dosage level on the improvement in memory task performance.
@@
 ## Study Design and Treatments
+
 We selected three brands of painkillers: Aspirin, Paracetamol, and Tramadol.
@@
 Crossing the two factors provides us with a total of *8 treatment groups*, with **30 participants** assigned to each.
-The groups are as follows:
+The total crossed treatment groups are shown in @tbl-total-groups.
 
-```{r, echo = FALSE}
+This results in **240 total observations** (8 × 30 = 240).
+
+For each treatment, we selected 30 different people (n = 30).
+Through randomly picking the virtual citizens, we replicated 30 experimental units per treatment.
+The even observations per treatment group ensures we have a balanced design.
+
+```{r}
+#| label: tbl-total-groups
+#| tbl-cap: "Treatment Groups"
+#| echo: false
+#| warning: false
+#| message: false
 
@@
   Dosage = c("Low", "High"),
-  Aspirin = c("500 mg", "1000 mg"),
-  Paracetamol = c("500 mg", "1000 mg"),
-  Tramadol = c("50 mg", "100 mg"),
-  Placebo = c("Low", "High")
+  Aspirin = c("Aspirin 500 mg", "Aspirin 1000 mg"),
+  Paracetamol = c("Paracetamol 500 mg", "Paracetamol 1000 mg"),
+  Tramadol = c("Tramadol 50 mg", "Tramadol 100 mg"),
+  Placebo = c("Placebo 1 Tablet", "Placebo 2 Tablets")
 )
@@
 # Render the table
-kable(study_table, caption = "Treatment Groups",
-      align = "c") %>%
+kable(study_table, align = "c") %>%
+  add_header_above(c(" " = 1, "Drug Type" = 4)) %>%
   kable_styling(full_width = FALSE, position = "center")
@@
 
-This results in **240 total observations** (8 × 30 = 240).
+### Nuisance Variable: Age
 
-For each treatment, we selected 30 different people (n = 30).
-Through randomly picking the virtual citizens, we replicated 30 experimental units per treatment.
-The even observations per treatment group ensures we have a balanced design.
-
-### Nuisance Variable: Age  
-To reduce bias, we consider **controlling** the experiment by limiting participant ages to be strictly 18+. Hence in this study, **age** acts as a **nuisance variable**.
-We also used **blocking** for age by ensuring participants were categorized into three even groups to prevent bias created through age. @tbl-summary-5 shows the breakdown of the groups.
+To reduce bias, we consider **controlling** the experiment by limiting participant ages to be strictly 18+.
+Hence in this study, **age** acts as a **nuisance variable**.
+We also used **blocking** for age by ensuring participants were categorized into three even groups to prevent bias created through age.
+@tbl-summary-5 shows the breakdown of the groups.
 
 ## Quantitative and Qualitative Variables
+
 In our study the quantitative and qualitative variables are as follows:
@@
 
-@tbl-summary-2 shows the distribution of participants across drug types. Aspirin, Paracetamol, and Tramadol, and Placebo each have 60 participants (25\%), ensuring balance.
+@tbl-summary-2 shows the distribution of participants across drug types.
+Aspirin, Paracetamol, and Tramadol, and Placebo each have 60 participants (25%), ensuring balance.
 
-@tbl-summary-3 shows the dosage levels assigned to participants. There is an equal split between high-dose (120 participants, 50\%) and low-dose (120 participants, 50\%) conditions.
+@tbl-summary-3 shows the dosage levels assigned to participants.
+There is an equal split between high-dose (120 participants, 50%) and low-dose (120 participants, 50%) conditions.
 
 \newpage
+
 # Plots
@@
 ```
+
 ```{r}
@@
 
-- $Y_{ijk}$: Memory score for the $k$-th participant receiving the $i$-th drug and $j$-th dosage level  
-- $\mu$: Overall mean  
-- $\alpha_i$: Effect of the $i$-th drug ((Aspirin, Tramadol, Paracetamol, Placebo))  
+-   $Y_{ijk}$: Memory score for the $k$-th participant receiving the $i$-th drug and $j$-th dosage level\
+-   $\mu$: Overall mean\
+-   $\alpha_i$: Effect of the $i$-th drug ((Aspirin, Tramadol, Paracetamol, Placebo))\
 -   $\beta_j$: Effect of the $j$-th dosage level (High Dosage, Low dosage)
-- $(\alpha\beta)_{ij}$: Interaction effect between drug and dosage  
+-   $(\alpha\beta)_{ij}$: Interaction effect between drug and dosage\
 -   $\epsilon_{ijk} \sim N(0, \sigma^2)$ : Random error
@@
 
-- $\beta_0$: Intercept (Aspirin at High dosage — the reference group)  
-- $\beta_1, \beta_2, \beta_3$: Main effects of Paracetamol, Placebo, and Tramadol relative to Aspirin  
-- $\beta_4$: Effect of Low dosage relative to High  
-- $\beta_5, \beta_6, \beta_7$: Interaction effects for each drug under Low dosage  
+-   $\beta_0$: Intercept (Aspirin at High dosage — the reference group)\
+-   $\beta_1, \beta_2, \beta_3$: Main effects of Paracetamol, Placebo, and Tramadol relative to Aspirin\
+-   $\beta_4$: Effect of Low dosage relative to High\
+-   $\beta_5, \beta_6, \beta_7$: Interaction effects for each drug under Low dosage\
 -   $\epsilon_i$: Residual error for the $i$-th participant
@@
 ## need to work on it
+
 "The two-way ANOVA factorial design involves the linear regression model followed by the ANOVA model.
@@
 The regression model from the @tbl-model-result shows the intercept(beta_0) which represents the predicted mean of memory game score for participants receiving high dosage of aspirin is 62.20 and the p-value = 0.00000 indicates the intercept is statistically significant.
-The variance explained by the model is R^2 = 0.03983, approximately 4% of the response variable.
+The variance explained by the model is R\^2 = 0.03983, approximately 4% of the response variable.
 And the p-value = 0.2167 of the model can be interpreted as not statistically significant"
@@
 # Discussion
+
 ## Interpretation of Results
+
 The two-way ANOVA analysis revealed no statistically significant main effects of drug type (p = 0.25) or dosage level (p = 0.26) on memory game scores.
@@
 # Limitations
+
 Our study is overall focused on memory, which may have links to one’s education and IQ level as they are all related to mental function and cognition.
@@
 # Conclusion
-This study found no conclusive evidence that pain relievers or their dosages significantly affect cognitive retention.
+
+This study found no conclusive evidence of pain relievers or their dosages significantly affecting cognitive retention.
 However, the exploratory trends observed, particularly with Paracetamol and Tramadol, highlight the need for larger-scale studies to investigate subtle or context-dependent effects.
 Future research could incorporate longitudinal designs, broader age-specific analyses, and alternative cognitive metrics to deepen understanding of painkillers’ cognitive implications.
-
-\newpage
-
-# References
 
@@
 ```
+
+\newpage
+
+# References

### 2025-04-02 paper/paper.qmd
Some edits and Limitations

@@
 ## Research Questions
+
+This study aims to explore and answer the following questions.
 
@@
 
-Our study is overall focused on memory, which may have links to one’s education and IQ level as they are all related to mental function and cognition.
+Our study is overall focused on memory, which may have links to one’s education and IQ level, as they are all related to mental function and cognition.
 In the future, we could test everyone for IQ scores and their highest level of education – these two nuisance variables can be taken care of by using the four principles of experimental design.
@@
 
+There’s also a chance that the participants’ expectations influenced their results if they knew which treatment they were getting (we cannot expand on this as it was a virtual experiment).
+In the future, bias could be minimized through having a double-blind design in which neither the participants nor the researchers know who’s getting what.
+We only tested low and high dosages, so we might be missing more subtle effects that show up with intermediate doses.
+So if we were to include a wider range of dosages in future studies, it could give a fuller picture.
+Another issue is that our sample might not fully represent the general population since we selected participants from specific clusters of locations -- not all locations were covered equally.
+This means our findings might not apply to everyone.
+Next time, we could choose more diverse and evenly spread-out clusters to make the results more general.
+Lastly, despite our efforts to control for confounding factors, there are still some variables (like sleep quality, stress levels, or baseline cognitive function) that could affect memory performance.
+Being more thorough in accounting for these factors could improve the accuracy of the results.
+
 # Conclusion
 
-This study found no conclusive evidence of pain relievers or their dosages significantly affecting cognitive retention.
+This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention.
 However, the exploratory trends observed, particularly with Paracetamol and Tramadol, highlight the need for larger-scale studies to investigate subtle or context-dependent effects.

### 2025-04-05 paper/paper.qmd
google doc - writeup - update

@@
 date-format: long
-abstract: Painkillers are commonly used to manage pain, and their effects are often associated with  physical relief.
+abstract: Painkillers are commonly used to manage pain and their effects are often associated with physical relief.
 While they provide immediate physical comfort, their impact on cognitive performance is often overlooked.
@@
 Common pain relievers like Aspirin, Paracetamol, and Tramadol are often used to reduce physical discomfort, but their impact on cognitive functions are not well understood.
-Memory retention is a process that requires mental effort – which becomes more difficult when we're in pain.
+Memory retention is a process that requires mental effort – which becomes more difficult when we are in pain.
 This study investigates how different pain relievers (Aspirin, Paracetamol, and Tramadol) at standard dosages affect memory performance.
-We will also look at how the interaction between drug type and dosage level influence memory function.
-Since the ability to recall information is a basis for optimized human function, understanding how pain relief might impact cognitive performance is important for managing pain without affecting productivity.
+We will also take a look at how the interaction between drug type and dosage level influence memory function.
+Understanding how pain relief might impact cognitive performance is important since the ability to recall information is a basis for optimized human function.
 
@@
 
-This study aims to explore and answer the following questions.
+Our study consists of the following research questions.
 
@@
 
-# Methodology
+The structure of this paper is as follows. @sec-method outlines our data and methodology. Section 3 presents our quantitative analysis. In Section 4, we discuss the results and address our findings
+
+# Methodology {#sec-method}
 
@@
 
-1.  Quantitative variables: Memory Game Scores, Memory Test Cards Scores
+1.  Quantitative variables: Memory Game Scores, Memory Card Scores
 2.  Qualitative variables: Type of pain reliever, dosage level (low/high)
@@
 
-The structure of the paper is as follows: Section 2 outlines our data and methodology.
-Section 3 presents our quantitative analysis.
-In Section 4, we discuss the results and address our findings from the analysis.
-Section 5 covers the limitations of our study, and Section 6 presents a conclusion to our analysis.
-After that, we have the bibliography in Section 7.
-Lastly, we attached the code for our study into the Appendix in Section 8.
-
 ## Summary of quantitative variables
 
-@tbl-summary-1 shows the summary statistics of memory game scores before and after the treatment.
-The mean is similar across all groups, however, the standard deviation (SD) is relatively high.
-The median game scores remain close to the mean, and the IQR (Interquartile Range) is smaller than the SD.
-The cards memory task shows little change before and after treatment, suggesting that pain relievers may not have a major effect on this specific task.
-
-Evident through the results, Paracetamol is the drug that has the greatest mean & median improvement in the game scores after administering the drug (without dosage taken into account).
-Aspirin appears to negatively impact the results of the game after being given to people, this was seen through the mean and median improvements.
+@tbl-summary-1 shows the summary statistics of the post-treatment memory game scores and memory card scores.
+The mean memory game score is 62.58 seconds, with a median of 61.50 seconds, which indicates that the distribution is fairly symmetric.
+The standard deviation (SD) is relatively high, indicating there is variability in overall participant performance.
+Looking at the  IQR (Interquartile Range), it is smaller than the SD, which suggests that most scores fall within a moderate range,  but there are some values  likely further from the center.
+For the memory card scores, the mean is 7.95/10 and the median is 9.00/10, which indicates a slight left skew in the distribution.
+Overall, the SD and IQR are both low, suggesting limited variability in these scores.
+While the summary statistics highlight some variability, they don’t directly indicate the presence of outliers; further visual analysis is required to assess this.
 
@@
 
+## Confounding Variable
+
+@tbl-summary-5 shows the breakdown of age groups, which is a confounding variable in this study. The three age groups: 18–34, 35–50, and 50+ each have 80 participants (33.33\%).
+
 \newpage
@@
   theme_minimal()
-p3 
+
 ```
@@
 
-# Arrange plots side by side with better spacing
-p1
-
 ```
-
 ```{r}
@@
 
-## Game Score Distribution by Drug and Dosage Level
+@fig-combined shows the distribution of memory game scores across different drug types using box plots and interaction plot.
 
-@fig-combined shows the distribution of memory game scores across different drug types using box plots.
+From the box plots, we observe:
 
-1.  The median scores for all drugs appear similar.
-2.  All drugs have a higher median on the higher dosage, level expect for Tramadol which is lower.
-3.  The Placebo group has a slightly lower median score compared to other drugs.
-4.  The (IQR) is **similar across all drug types**, though Tramadol and Placebo see a higher IQR in the memory game scores in the high dosage.
+1. The median scores vary by both drug type and dosage level.
+2. Tramadol (high dosage) appears to have a wider spread in scores compared to other groups.
+3. The Placebo groups, both low and high dosage, show relatively similar median scores.
+4. There is noticeable variability within each drug type, with some groups showing larger interquartile ranges (IQR) than others.
+5. The boxplots indicate potential outliers in several groups, as shown by individual points beyond the whiskers.
 
-This boxplot provides an initial comparison of memory game performance and drug administration.
+These boxplots provide an initial comparison of cognitive performance across drug types and dosages, highlighting both central tendency and variability in memory game scores.
+
+The interaction plot suggests an interaction effect between drug type and dosage level, as the lines are not parallel.
+The low-dosage line shows a sharp increase in memory scores for Tramadol and a dip for Placebo.
+However, the high-dosage line follows a more gradual trend.
+This indicates that the effect of dosage on memory performance may depend on the type of pain reliever administered.
+
+Although the visual pattern indicates potential interaction, a formal Two-Way ANOVA is required to determine the statistical significance of this relationship.
 
@@
 
+## Assumption Checks
+
+The method of two-way ANOVA is used to estimate the mean of memory game score changes according to the levels of two categorical variables that are drug and dosage level.
+Before performing the Two-Way ANOVA, we verified the assumptions of the model as seen from using Q-Q plot as seen in @fig-normal-plot.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
+anova_model <- lm(memory_game_score ~ drug * dosage_level, data = clean_data)
+
+model_tidy <- tidy(anova_model) %>%
+  rename(
+    `Predictor Term` = term,
+    `Estimate` = estimate,
+    `Std. Error` = std.error,
+    `t-statistic` = statistic,
+    `p-value` = p.value
+  )
+```
+
+```{r, echo = FALSE}
+#| label: fig-normal-plot
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9  # Reduced width
+#| fig.height: 8  # Reduced height
+#| dpi: 300
+#| out.width: 60%
+#| out.height: 50%
+#| fig.align: "center"
+#| fig-cap: "Q-Q Plot of Residuals"
+
+# Normality Check
+ggqqplot(residuals(anova_model))
+
+```
+
+The Shapiro-Wilk Test confirms a p-value = 0.05553 as per @tbl-shapiro, so we fail to reject the null hypothesis and the result confirms that the dataset is *normally distributed*.
+
+```{r, echo = FALSE}
+#| label: tbl-shapiro
+#| tbl-cap: "Shapiro-Wilk Test for Normality"
+#| echo: false
+#| warning: false
+#| message: false
+
+# Shapiro-Wilk Normality Test
+shapiro_test <- shapiro.test(residuals(anova_model))
+shapiro_table <- data.frame(
+  Statistic = round(shapiro_test$statistic, 4),
+  `P-Value` = round(shapiro_test$p.value, 4),
+  Method = shapiro_test$method,
+  check.names = FALSE  # Prevents automatic renaming
+)
+
+kable(shapiro_table, format = "latex", booktabs = TRUE)
+```
+
+Our second assumption of *homogeneity of variance* is verified by the p-value = 0.3346 from the Bartlett test in @tbl-bartlett, which is greater than 0.05.
+Due to this, we fail to reject the null hypothesis.
+Lastly, for our two-way ANOVA model, the different combinations of pain reliever type and dosage levels, the treatments were randomly assigned to all participants which ensures *independence*.
+
+```{r}
+#| label: tbl-bartlett
+#| tbl-cap: "Bartlett’s Test for Homogeneity of Variance"
+#| echo: false
+#| warning: false
+#| message: false
+
+# Scale-Location Plot
+
+# Perform Bartlett’s test for homogeneity of variance
+bartlett_test <- bartlett.test(memory_game_score ~ interaction(drug, dosage_level), data = clean_data)
+
+bartlett_table <- data.frame(
+  Statistic = round(bartlett_test$statistic, 4),
+  DF = bartlett_test$parameter,
+  `P-Value` = round(bartlett_test$p.value, 4),
+  Method = bartlett_test$method,
+  check.names = FALSE
+)
+
+kable(bartlett_table, format = "latex", booktabs = TRUE)
+```
+
 ## Model
 
-The method of Wwo-way ANOVA is used to estimate the mean of a memory game score changes according to the levels of two categorical variables that is drug and dosage level.
+The method of Two-way ANOVA is used to estimate the mean of a memory game score changes according to the levels of two categorical variables that is drug and dosage level.
 The general statistical form of the model is:
@@
 -   $\alpha_i$: Effect of the $i$-th drug ((Aspirin, Tramadol, Paracetamol, Placebo))\
--   $\beta_j$: Effect of the $j$-th dosage level (High Dosage, Low dosage)
+-   $\beta_j$: Effect of the $j$-th dosage level (High Dosage, Low dosage)\
 -   $(\alpha\beta)_{ij}$: Interaction effect between drug and dosage\
@@
   transmute(
+    `R - sqaured` = r.squared,
     `F-Statistic` = statistic,
@@
 
-```{r, echo = FALSE}
-#| label: fig-normal-plot
-#| echo: false
-#| warning: false
-#| message: false
-#| fig.width: 9  # Reduced width
-#| fig.height: 8  # Reduced height
-#| dpi: 300
-#| out.width: 60%
-#| out.height: 50%
-#| fig.align: "center"
-#| fig-cap: "Q-Q Plot of Residuals"
-
-# Normality Check
-ggqqplot(residuals(anova_model))
-
-```
-
-```{r, echo = FALSE}
-#| label: tbl-shapiro
-#| tbl-cap: "Shapiro-Wilk Test for Normality"
-#| echo: false
-#| warning: false
-#| message: false
-
-# Shapiro-Wilk Normality Test
-shapiro_test <- shapiro.test(residuals(anova_model))
-shapiro_table <- data.frame(
-  Statistic = round(shapiro_test$statistic, 4),
-  `P-Value` = round(shapiro_test$p.value, 4),
-  Method = shapiro_test$method,
-  check.names = FALSE  # Prevents automatic renaming
-)
-
-kable(shapiro_table, format = "latex", booktabs = TRUE)
-```
-
-```{r}
-#| label: fig-variance-plot
-#| echo: false
-#| warning: false
-#| message: false
-#| fig.width: 9  # Smaller width
-#| fig.height: 8  # Smaller height
-#| out.width: 60%
-#| out.height: 50%
-#| dpi: 300
-#| fig-cap: "Q-Q Plot of Residuals"
-
-plot(anova_model, which = 3, main = "", sub = "", caption = "")
-
-```
-
-```{r}
-#| label: tbl-bartlett
-#| tbl-cap: "Bartlett’s Test for Homogeneity of Variance"
-#| echo: false
-#| warning: false
-#| message: false
-
-# Scale-Location Plot
-
-# Perform Bartlett’s test for homogeneity of variance
-bartlett_test <- bartlett.test(memory_game_score ~ interaction(drug, dosage_level), data = clean_data)
-
-bartlett_table <- data.frame(
-  Statistic = round(bartlett_test$statistic, 4),
-  DF = bartlett_test$parameter,
-  `P-Value` = round(bartlett_test$p.value, 4),
-  Method = bartlett_test$method,
-  check.names = FALSE
-)
-
-kable(bartlett_table, format = "latex", booktabs = TRUE)
-```
-
-## Assumption Checks
-
-We verified the assumption of the two-way ANOVA model as seen from using Q-Q plot as seen in @fig-normal-plot.
-The Shapiro-Wilk Test confirms a p-value = 0.05553 as per @tbl-shapiro, so we fail to reject the null hypothesis and the result confirms that the dataset is *normally distributed*.
-Our second assumption of *homogeneity of variance* is verified by the p-value = 0.3346 from the Bartlett test in @tbl-bartlett, which is greater than 0.05.
-Due to this, we fail to reject the null hypothesis.
-Thirdly, for our two-way ANOVA model, the different combinations of pain reliever type and dosage levels, the treatments were randomly assigned to all participants which ensures *independence*.
-
-## need to work on it
-
-"The two-way ANOVA factorial design involves the linear regression model followed by the ANOVA model.
-The model uses the reference (baseline) group which is Aspirin (Drug) & High (Dosage level).
-The regression model from the @tbl-model-result shows the intercept(beta_0) which represents the predicted mean of memory game score for participants receiving high dosage of aspirin is 62.20 and the p-value = 0.00000 indicates the intercept is statistically significant.
-The variance explained by the model is R\^2 = 0.03983, approximately 4% of the response variable.
-And the p-value = 0.2167 of the model can be interpreted as not statistically significant"
+The two-way ANOVA factorial design was implemented using a linear regression model with dummy coding, followed by an ANOVA test.
+The reference group (baseline) is participants receiving Aspirin as the drug and High dosage as the dosage level.
 
@@
 
-The two-way ANOVA analysis revealed no statistically significant main effects of drug type (p = 0.25) or dosage level (p = 0.26) on memory game scores.
-Similarly, the interaction effect between drug type and dosage level was not significant (p = 0.24).
-These results suggest that neither the type of pain reliever (Aspirin, Paracetamol, Tramadol, or Placebo) nor its dosage (low vs.
-high) had a meaningful impact on memory game scores, which is representative of cognitive improvement in this study.
-The lack of significance persisted even after accounting for age as a confounding variable, which was controlled through participant stratification into three balanced groups (18–34, 35–50, and 50+ years).
+The two-way ANOVA results @tbl-anova-model revealed no statistically significant main effects of drug type ($p = 0.25$) or dosage level ($p = 0.26$) on memory game scores, as both p-values exceed the 0.05 threshold.
+
+For **Research Question 1**, which asked whether the type of pain reliever impacts memory performance, we found no significant differences in memory scores between the drug groups (Aspirin, Paracetamol, Tramadol, or Placebo).
+Therefore, we fail to reject the null hypothesis for Research Question 1.
+
+Similarly, the **interaction effect** between drug type and dosage level was not statistically significant ($p = 0.24$), suggesting that the impact of drug type on memory retention does not vary by dosage level.
+This directly addresses **Research Question 2**, and we again fail to reject the null hypothesis, concluding that there is no interaction effect between the type of pain reliever and dosage on memory task performance.
+
+Since no interaction effect was present, we examined the main effects independently.
+As mentioned, drug type was not significant, and neither was **dosage level** (\(p = 0.26\)), indicating that neither factor significantly influenced cognitive performance.
+
+The lack of statistically significant findings persisted even after **controlling for age** as a potential confounding variable.
+Participants were stratified into balanced age groups (18–34, 35–50, and 50+ years) to minimize age-related bias.
+
+## Effect Size
+
+Although the ANOVA model yielded no statistically significant results, we also considered the practical significance of the findings.
+The model’s $R^2 = 0.0398$ suggests that approximately 4\% of the variability in memory performance was accounted for by the treatment factors.
+However, in the context of ANOVA, $R^2$ is not typically used for interpretation, as it does not directly reflect differences between group means.
+
+Instead, we refer to Cohen’s \(f\) as a more appropriate measure of effect size in ANOVA.
+Cohen’s \(f\) is based on the proportion of variance explained and provides context for the magnitude of the observed effects.
+For this study, we assume a medium effect size, corresponding to Cohen’s $f \approx 0.25$, based on conventional benchmarks from lecture materials.
+
+Even though the statistical test did not yield significant results.
+This suggests a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.
 

### 2025-04-05 paper/paper.qmd
minor fix

@@
 
+This study followed all four principles of experimental design: **Control, Block, Randomization and Replication**.
+
 In February, our group members collected observations from participants belonging to a virtual population to assess whether the treatment had any effect on memory performance, this resulted in a total of 240 observations.
@@
 For each treatment, we selected 30 different people (n = 30).
-Through randomly picking the virtual citizens, we replicated 30 experimental units per treatment.
+Through randomly picking the virtual citizens, we **replicated** 30 experimental units per treatment.
 The even observations per treatment group ensures we have a balanced design.
@@
 
-1. The median scores vary by both drug type and dosage level.
-2. Tramadol (high dosage) appears to have a wider spread in scores compared to other groups.
-3. The Placebo groups, both low and high dosage, show relatively similar median scores.
-4. There is noticeable variability within each drug type, with some groups showing larger interquartile ranges (IQR) than others.
-5. The boxplots indicate potential outliers in several groups, as shown by individual points beyond the whiskers.
-
-These boxplots provide an initial comparison of cognitive performance across drug types and dosages, highlighting both central tendency and variability in memory game scores.
+1. The median scores for all drugs appear similar before treatment.
+2. Tramadol has a higher median than other drugs both before and after treatment.
+3. The Placebo group has a slightly lower median score compared to other drugs.
+4. There is one outlier in the Tramadol group before treatment.
+5. The (IQR) is similar across all drug types, though Tramadol sees a decrease in its
+IQR in the memory game scores after treatment.
+These boxplots provide an initial comparison of cognitive performance changes before and after
+drug administration.
 

### 2025-04-05 paper/paper.qmd
Effect Size and Power Analysis

@@
 
-## Effect Size
+## Effect Size and Power Analysis
 
@@
 Cohen’s \(f\) is based on the proportion of variance explained and provides context for the magnitude of the observed effects.
-For this study, we assume a medium effect size, corresponding to Cohen’s $f \approx 0.25$, based on conventional benchmarks from lecture materials.
+[[[SHOULD WE STILL INCLUDE THIS?: For this study, we assume a medium effect size, corresponding to Cohen’s $f \approx 0.25$, based on conventional benchmarks from lecture materials.
+Even though the statistical test did not yield significant results.
+This suggests a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.]]]
 
-Even though the statistical test did not yield significant results.
-This suggests a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.
+We did a post-hoc power analysis using @WebPower.
+Based on the overall $\eta^2$ from the ANOVA model, we calculated a Cohen's f value of 0.204.
+This suggests a small-medium effect size, which means that the type of drug and dosage level may still have had a meaningful impact on memory task performance.
+
+The estimated power of the study was around 59.6%.
+This means that our study was moderately able to detect an effect with the size we have, if there was an effect.
+Despite being less than the ideal 80% power value, this suggests that the study is still able to detect large & meaningful differences -- just not smaller ones.
 
@@
 
+```{r}
+# EFFECT SIZE AND POWER ANALYSIS
+eta_sq <- eta_squared(anova_model, partial = FALSE)
+
+etasquare <- sum(eta_sq$Eta2)  # sum of all eta^2 values
+cohens_f <- sqrt(etasquare / (1 - etasquare))
+
+power_result <- wp.kanova(
+  n = 240,
+  ndf = 7, # because 8 - 1 = 7
+  f = cohens_f,
+  ng = 8, # because 8 treatment groups
+  alpha = 0.05
+)
+
+```
+
 \newpage

### 2025-04-05 paper/paper.qmd
Minor changes

@@
 
-Instead, we refer to Cohen’s \(f\) as a more appropriate measure of effect size in ANOVA.
-Cohen’s \(f\) is based on the proportion of variance explained and provides context for the magnitude of the observed effects.
+Instead, we refer to Cohen’s $f$ as a more appropriate measure of effect size in ANOVA.
+Cohen’s $f$ is based on the proportion of variance explained and provides context for the magnitude of the observed effects.
 [[[SHOULD WE STILL INCLUDE THIS?: For this study, we assume a medium effect size, corresponding to Cohen’s $f \approx 0.25$, based on conventional benchmarks from lecture materials.
@@
 
-We did a post-hoc power analysis using @WebPower.
-Based on the overall $\eta^2$ from the ANOVA model, we calculated a Cohen's f value of 0.204.
+We did a post-hoc power analysis.
+Based on the overall $\eta^2$ from the ANOVA model, we calculated a Cohen's $f$ value of 0.204.
 This suggests a small-medium effect size, which means that the type of drug and dosage level may still have had a meaningful impact on memory task performance.
@@
 library(arrow)
+library(effectsize)
 library(dplyr)
@@
 library(performance)
+library(WebPower)
 library(ggpubr)

### 2025-04-05 paper/paper.qmd
Added dummy variable table

@@
 
+The @tbl-model-result show the intercept ($\beta_0$ = 60.02) is the average memory game score for individuals given High dosage and Aspirin Drug (reference group).
+While comparing other treatments to reference level, we observe most coefficients from @tbl-model-result  are not statistically significant at 5% level.
+The coefficient of Drug Paracetamol (p-value = 0.741), Tramadol (p-value = 0.528), Placebo (p-value = 0.448) indicates that mean memory game scores for these groups are not statistically different from the reference group.
+Similarly, the evidence for all the Interaction terms are suggest no statistical significance between drug type and dosage level has any effect on the memory game score performance as p value are greater than 5% significance level.
+The lack of significance indicates that the effect of dosage does not vary meaningfully across drug types and dosage levels, indicating an absence of interaction between the two factors.
+
 ```{r, echo = FALSE}
@@
 ```
-
-The two-way ANOVA factorial design was implemented using a linear regression model with dummy coding, followed by an ANOVA test.
-The reference group (baseline) is participants receiving Aspirin as the drug and High dosage as the dosage level.
 

### 2025-04-06 paper/paper.qmd
Paper structure updated

@@
 
-The structure of this paper is as follows. @sec-method outlines our data and methodology. Section 3 presents our quantitative analysis. In Section 4, we discuss the results and address our findings
+The structure of this paper is as follows.
+@sec-method outlines our data and methodology.
+@sec-plots presents our findings into graphs and charts to visualize the data better.
+@sec-analysis presents our quantitative analysis.
+In @sec-disc, we discuss the results and address our findings.
+We end off, we have the limitations and conclusion in @sec-lims and @sec-conc, respectively.
+All of the code used for this study can be found in @sec-appendix. The references are found in @sec-references.
 
@@
 
-# Plots
+# Plots {#sec-plots}
 
@@
 
-# Analysis
+# Analysis {#sec-analysis}
 
@@
 
-# Discussion
+# Discussion {#sec-disc}
 
@@
 
-# Limitations
+# Limitations {#sec-lims}
 
@@
 
-# Conclusion
+# Conclusion {#sec-conc}
 
@@
 
-# References
+# References {#sec-references}

### 2025-04-06 paper/paper.qmd
File discussion done new updates

@@
 
-# Introduction
+# Introduction {#sec-intro}
 
@@
 Through randomly picking the virtual citizens, we **replicated** 30 experimental units per treatment.
-The even observations per treatment group ensures we have a balanced design.
+The even observations per treatment group ensures we have a **balanced design**.
 
@@
 
-1.  Quantitative variables: Memory Game Scores, Memory Card Scores
+1.  Quantitative variables: Memory Game Scores
 2.  Qualitative variables: Type of pain reliever, dosage level (low/high)
@@
 
-@tbl-summary-1 shows the summary statistics of the post-treatment memory game scores and memory card scores.
+@tbl-summary-1 shows the summary statistics of the treatment memory game scores.
 The mean memory game score is 62.58 seconds, with a median of 61.50 seconds, which indicates that the distribution is fairly symmetric.
-The standard deviation (SD) is relatively high, indicating there is variability in overall participant performance.
-Looking at the  IQR (Interquartile Range), it is smaller than the SD, which suggests that most scores fall within a moderate range,  but there are some values  likely further from the center.
-For the memory card scores, the mean is 7.95/10 and the median is 9.00/10, which indicates a slight left skew in the distribution.
-Overall, the SD and IQR are both low, suggesting limited variability in these scores.
-While the summary statistics highlight some variability, they don’t directly indicate the presence of outliers; further visual analysis is required to assess this.
 
@@
 
-# Compute statistics for Memory Game Score
 mean_game <- mean(clean_data$memory_game_score, na.rm = TRUE)
@@
 
-# Compute statistics for Memory Cards Score
-mean_cards <- mean(clean_data$memory_cards_score, na.rm = TRUE)
-median_cards <- median(clean_data$memory_cards_score, na.rm = TRUE)
-sd_cards <- sd(clean_data$memory_cards_score, na.rm = TRUE)
-iqr_cards <- IQR(clean_data$memory_cards_score, na.rm = TRUE)
-
-# Combine into a summary table
+# Create summary table with clean column header
 summary_table <- data.frame(
   Statistic = c("Mean", "Median", "SD", "IQR"),
-  `Memory Game Score` = c(mean_game, median_game, sd_game, iqr_game),
-  `Memory Cards Score` = c(mean_cards, median_cards, sd_cards, iqr_cards)
+  "Memory Game Score" = c(mean_game, median_game, sd_game, iqr_game),  check.names = FALSE
 )
 
-colnames(summary_table) <- c("Statistic", "Memory Game Score", "Memory Cards Score")
-
 # Display table
-
 kable(summary_table, format = "latex", booktabs = TRUE)
@@
   theme_minimal()
+```
 
-```
 ```{r}
@@
 #| fig.height: 6
-#| fig-cap: "Interaction Plot and Boxplot: Memory Game Scores by Drug Type and Dosage Level"
+#| fig-cap: "Interaction and Boxplots for Drug and Dosage Effects"
 
@@
 
-1. The median scores for all drugs appear similar before treatment.
-2. Tramadol has a higher median than other drugs both before and after treatment.
-3. The Placebo group has a slightly lower median score compared to other drugs.
-4. There is one outlier in the Tramadol group before treatment.
-5. The (IQR) is similar across all drug types, though Tramadol sees a decrease in its
-IQR in the memory game scores after treatment.
-These boxplots provide an initial comparison of cognitive performance changes before and after
-drug administration.
+1. The median memory game scores are relatively similar across most drug types.
+2. Tramadol (high dosage) shows a higher median score compared to other treatments.
+3. The Placebo group has a slightly lower median score than the others.
+4. The interquartile range (IQR) is consistent across all groups, although Tramadol (high dosage) has slightly more variability.
 
@@
 
-Our second assumption of *homogeneity of variance* is verified by the p-value = 0.3346 from the Bartlett test in @tbl-bartlett, which is greater than 0.05.
-Due to this, we fail to reject the null hypothesis.
+Our second assumption of Homogeneity of Variance appears to be satisfied.
+As shown in the @fig-residual-plot, the spread of the residual remains relatively consistent across the of fitted values.
+Further the result of the Bartlett test for homogeneity of variances from @tbl-bartlett, suggests the p-value is 0.3346.
+Since this p-value is greater than the 0.05 significance level, we fail to reject the null hypothesis of equal variances.
+Hence, the assumption is verified.
 Lastly, for our two-way ANOVA model, the different combinations of pain reliever type and dosage levels, the treatments were randomly assigned to all participants which ensures *independence*.
@@
 
+```{r}
+#| label: fig-residual-plot
+#| echo: false
+#| warning: false
+#| message: false
+#| fig.width: 9  
+#| fig.height: 8  
+#| dpi: 300
+#| out.width: 60%
+#| out.height: 50%
+#| fig.align: "center"
+#| fig-cap: "Residual plot: Check for Homoscedasticity"
+
+plot(anova_model, which = 3, main = "", sub = "")
+```
+
 ## Model
@@
 -   $\mu$: Overall mean\
--   $\alpha_i$: Effect of the $i$-th drug ((Aspirin, Tramadol, Paracetamol, Placebo))\
+-   $\alpha_i$: Effect of the $i$-th drug (Aspirin, Tramadol, Paracetamol, Placebo)
 -   $\beta_j$: Effect of the $j$-th dosage level (High Dosage, Low dosage)\
@@
 
-The @tbl-model-result show the intercept ($\beta_0$ = 60.02) is the average memory game score for individuals given High dosage and Aspirin Drug (reference group).
+The @tbl-model-result show the intercept ($\beta_0$ = 62.20) is the average memory game score for individuals given High dosage and Aspirin Drug (reference group).
 While comparing other treatments to reference level, we observe most coefficients from @tbl-model-result  are not statistically significant at 5% level.
-The coefficient of Drug Paracetamol (p-value = 0.741), Tramadol (p-value = 0.528), Placebo (p-value = 0.448) indicates that mean memory game scores for these groups are not statistically different from the reference group.
-Similarly, the evidence for all the Interaction terms are suggest no statistical significance between drug type and dosage level has any effect on the memory game score performance as p value are greater than 5% significance level.
+The coefficient of Drug Paracetamol ($p-value = 0.9927$), Tramadol ($p-value = 0.5281$), Placebo ($p-value = 0.3893$) indicates that mean memory game scores for these groups are not statistically different from the reference group.
+Similarly, the evidence for all the Interaction terms suggests no statistical significance between drug type and dosage level has any effect on the memory game score performance as p value are greater than 5% significance level.
 The lack of significance indicates that the effect of dosage does not vary meaningfully across drug types and dosage levels, indicating an absence of interaction between the two factors.
@@
 Since no interaction effect was present, we examined the main effects independently.
-As mentioned, drug type was not significant, and neither was **dosage level** (\(p = 0.26\)), indicating that neither factor significantly influenced cognitive performance.
+As mentioned, drug type was not significant, and neither was **dosage level** ($p = 0.26$), indicating that neither factor significantly influenced cognitive performance.
 
@@
 
-Although the ANOVA model yielded no statistically significant results, we also considered the practical significance of the findings.
-The model’s $R^2 = 0.0398$ suggests that approximately 4\% of the variability in memory performance was accounted for by the treatment factors.
-However, in the context of ANOVA, $R^2$ is not typically used for interpretation, as it does not directly reflect differences between group means.
-
-Instead, we refer to Cohen’s $f$ as a more appropriate measure of effect size in ANOVA.
-Cohen’s $f$ is based on the proportion of variance explained and provides context for the magnitude of the observed effects.
-[[[SHOULD WE STILL INCLUDE THIS?: For this study, we assume a medium effect size, corresponding to Cohen’s $f \approx 0.25$, based on conventional benchmarks from lecture materials.
-Even though the statistical test did not yield significant results.
-This suggests a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.]]]
+Since the interaction effect was not statistically significant ($p > 0.05$), we proceeded to assess the effect size with the purpose to evaluate the practical significance of our findings.
+Our model yields  $R^2 = 0.0398$.
+While $R^2$ commonly used in regression analysis to a measure explained variance, determining the goodness of fit of a model.
+However, in ANOVA Model the $R^2$ value doesn't have a direct interpretation as the proportion of variance explained by regression model and it also does not directly reflect differences between group means.
+We use the $R^2$ value to report the effect that corresponds to Cohen’s f guidelines i.e.
+$| f |$ is approximately 0.25 as our  $R^2$ falls between the small-medium categories.Even though the statistical test did not yield significant results, this quantity suggests we have a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.
 
@@
 
+library(knitr)
+library(kableExtra)
+
+# Create a dataframe for the table
+study_table <- data.frame(
+  Dosage = c("Low", "High"),
+  Aspirin = c("Aspirin 500 mg", "Aspirin 1000 mg"),
+  Paracetamol = c("Paracetamol 500 mg", "Paracetamol 1000 mg"),
+  Tramadol = c("Tramadol 50 mg", "Tramadol 100 mg"),
+  Placebo = c("Placebo 1 Tablet", "Placebo 2 Tablets")
+)
+
+# Render the table
+kable(study_table, align = "c") %>%
+  add_header_above(c(" " = 1, "Drug Type" = 4)) %>%
+  kable_styling(full_width = FALSE, position = "center")
+```
+
+```{r}
+
 library(tidyverse)
@@
 ```{r}
-# Compute statistics for Memory Game Score
+age_counts <- table(clean_data$age_group)
+
+# percentages for each age group
+age_percentages <- prop.table(age_counts) * 100
+
+# summary dataframe
+age_summary <- data.frame(
+  `Age Group` = names(age_counts),
+  Count = as.numeric(age_counts),
+  Percentage = round(as.numeric(age_percentages), 2)
+)
+
+colnames(age_summary)[colnames(age_summary) == "Age.Group"] <- "Age Group"
+
+# Display table
+kable(age_summary, booktabs = TRUE, row.names = FALSE)
+
+```
+
+```{r}
 mean_game <- mean(clean_data$memory_game_score, na.rm = TRUE)
@@
 
-# Compute statistics for Memory Cards Score
-mean_cards <- mean(clean_data$memory_cards_score, na.rm = TRUE)
-median_cards <- median(clean_data$memory_cards_score, na.rm = TRUE)
-sd_cards <- sd(clean_data$memory_cards_score, na.rm = TRUE)
-iqr_cards <- IQR(clean_data$memory_cards_score, na.rm = TRUE)
-
-# Combine into a summary table
+# Create summary table with clean column header
 summary_table <- data.frame(
   Statistic = c("Mean", "Median", "SD", "IQR"),
-  `Memory Game Score` = c(mean_game, median_game, sd_game, iqr_game),
-  `Memory Cards Score` = c(mean_cards, median_cards, sd_cards, iqr_cards)
+  "Memory Game Score" = c(mean_game, median_game, sd_game, iqr_game),  check.names = FALSE
 )
 
-colnames(summary_table) <- c("Statistic", "Memory Game Score", "Memory Cards Score")
+# Display table
+kable(summary_table, format = "latex", booktabs = TRUE)
 
-# Display table
-
-kable(summary_table, format = "latex", booktabs = TRUE)
 ```
@@
 kable(drug_summary, format = "latex", booktabs = TRUE)
-
 ```
@@
 ```{r}
-
-dosage_counts <- table(clean_data$dosage_level)
-
-# percentage for each dosage level
-dosage_percentages <- prop.table(dosage_counts) * 100
-
-# summary dataframe
-dosage_summary <- data.frame(
-  Dosage = names(dosage_counts),
-  Count = as.numeric(dosage_counts),
-  Percentage = round(as.numeric(dosage_percentages), 2)
-)
-
-# Display table
-kable(dosage_summary, booktabs = TRUE, row.names = FALSE)
-
+p3 <- ggplot(clean_data, aes(x = drug, y = memory_game_score, fill = dosage_level)) +
+  geom_boxplot() +
+  labs(x = "Drug Type", y = "Memory Game Score", fill = "Dosage Level") +
+  theme_minimal()
 ```
@@
 ```{r}
-age_counts <- table(clean_data$age_group)
-
-# percentages for each age group
-age_percentages <- prop.table(age_counts) * 100
-
-# summary dataframe
-age_summary <- data.frame(
-  `Age Group` = names(age_counts),
-  Count = as.numeric(age_counts),
-  Percentage = round(as.numeric(age_percentages), 2)
-)
-colnames(age_summary)[colnames(age_summary) == "Age.Group"] <- "Age Group"
-
-# Display table
-kable(age_summary, booktabs = TRUE, row.names = FALSE)
-
-```
-
-```{r}
-
 p1 <- ggplot(clean_data, aes(x = drug, y = memory_game_score, color = dosage_level, group = dosage_level)) +
-  stat_summary(fun = mean, geom = "point", size = 3) +
+  stat_summary(fun = mean, geom = "point", size = 2) +
   stat_summary(fun = mean, geom = "line", size = 1) +
@@
   theme_minimal()
+```
 
-# Interaction plot for Memory Cards Scores
-p2 <- ggplot(clean_data, aes(x = drug, y = memory_cards_score, color = dosage_level, group = dosage_level)) +
-  stat_summary(fun = mean, geom = "point", size = 3) +
-  stat_summary(fun = mean, geom = "line", size = 1) +
-  labs(title = "Memory Cards Scores",
-       x = "Drug Type",
-       y = "Mean Memory Cards Score",
-       color = "Dosage Level") +
-  theme_minimal()
-
-# Combine the two plots vertically
-combined_plot <- p1 / p2
-combined_plot
+```{r}
+# Combine the plots side by side
+p1 + p3
 ```

### 2025-04-06 paper/paper.qmd
Update
updated Cohen f

@@
 We use the $R^2$ value to report the effect that corresponds to Cohen’s f guidelines i.e.
-$| f |$ is approximately 0.25 as our  $R^2$ falls between the small-medium categories.Even though the statistical test did not yield significant results, this quantity suggests we have a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.
+$| f |$ is approximately 0.20 as our  $R^2$ falls between the small-medium categories.Even though the statistical test did not yield significant results, this quantity suggests we have a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.
 
 We did a post-hoc power analysis.
-Based on the overall $\eta^2$ from the ANOVA model, we calculated a Cohen's $f$ value of 0.204.
+Based on the overall $\eta^2$ from the ANOVA model, we calculated a Cohen's $f$ value of 0.20.
 This suggests a small-medium effect size, which means that the type of drug and dosage level may still have had a meaningful impact on memory task performance.

### 2025-04-08 paper/paper.qmd
Update paper.qmd
Effect Size and Power Analysis

@@
 We did a post-hoc power analysis.
-Based on the overall $\eta^2$ from the ANOVA model, we calculated a Cohen's $f$ value of 0.20.
-This suggests a small-medium effect size, which means that the type of drug and dosage level may still have had a meaningful impact on memory task performance.
+Based on our two-way ANOVA model, we calculated the power for the two main effects and the interaction effect (ie.
+drug, dosage_level, and drug:dosage_level, respectively).
 
-The estimated power of the study was around 59.6%.
-This means that our study was moderately able to detect an effect with the size we have, if there was an effect.
-Despite being less than the ideal 80% power value, this suggests that the study is still able to detect large & meaningful differences -- just not smaller ones.
+We achieved the following effect sizes (Cohen's f) and powers.
+For drug type, we got the effect size of 0.134 and a power of 37.6%.
+For the dosage level, we got the effect size of 0.074 and a power of 20.8%.
+And for the interaction effect for the drug and dosage level, we got the effect size of 0.135 and a power of 38.2%.
+
+These results show that the statistical power for all three effects were low.
+In other words, our study had a limited ability to detect real effects, should they exist.
+With power values of 37.6%, 20.8%, and 38.2% for the drug, dosage level, and interaction effects respectively, we had less than a 40% chance of identifying a true effect under the conditions of our study.
+
+This suggests that while our ANOVA results were not statistically significant, this may be due to insufficient power rather than the absence of any real effect.
+The observed effect sizes fall into the small range according to Cohen’s conventions, which typically require a larger sample size to detect reliably.
+
+We discuss about addressing this limitation in the next section.
 
@@
 # EFFECT SIZE AND POWER ANALYSIS
-eta_sq <- eta_squared(anova_model, partial = FALSE)
+eta_sq <- eta_squared(anova_model, partial = TRUE)
 
-etasquare <- sum(eta_sq$Eta2)  # sum of all eta^2 values
-cohens_f <- sqrt(etasquare / (1 - etasquare))
+eta2drug <- eta_sq$Eta2[1]  
+cohenfdrug <- sqrt(eta2drug / (1 - eta2drug))
+print(cohenfdrug)
 
-power_result <- wp.kanova(
+eta2dos <- eta_sq$Eta2[2]  
+cohenfdos <- sqrt(eta2dos / (1 - eta2dos))
+print(cohenfdos)
+
+eta2drugdos <- eta_sq$Eta2[3]  
+cohenfdrugdos <- sqrt(eta2drugdos / (1 - eta2drugdos))
+print(cohenfdrugdos)
+
+powerdrug <- wp.kanova(
   n = 240,
-  ndf = 7, # because 8 - 1 = 7
-  f = cohens_f,
-  ng = 8, # because 8 treatment groups
+  ndf = 3,
+  f = cohenfdrug,
+  ng = 8,
   alpha = 0.05
@@
 
+powerdos <- wp.kanova(
+  n = 240,
+  ndf = 1, 
+  f = cohenfdos,
+  ng = 8,
+  alpha = 0.05
+)
+
+powerdrugdos <- wp.kanova(
+  n = 240,
+  ndf = 3,
+  f = cohenfdrugdos,
+  ng = 8,
+  alpha = 0.05
+)
+
+print(powerdrug)
+print(powerdos)
+print(powerdrugdos)
 ```

### 2025-04-08 paper/paper.qmd
Completed conclusion

@@
 
+We performed a Two- way ANOVA to evaluate whether different types of pain relievers (Aspirin, Paracetamol, Tramadol, and Placebo) influence cognitive performance measured through memory game performance to address our research question 1.
+The null hypothesis proposed that all pain relievers produce equal effects on memory performance, while the alternative hypothesis suggests that at least one type differs significantly.
+The ANOVA results indicated that there was no statistical significant difference in memory game score between the four pain relievers under main effects.
+These results indicate that, at the standard dosages, none of the pain relievers significantly affected cognitive performance.
+This supports the interpretation that commonly used pain relievers neither impair nor enhance cognitive performance in the context of memory games performance.
+To answer research question 2, we employed the same Two-way ANOVA model to assess whether an interaction exists between the type of pain reliever (Aspirin, Paracetamol, Tramadol, and Placebo) and dosage level (low/high) on memory game performance.
+The analysis revealed no statistically significant interaction effect (p=0.24), leading us to fail to reject the null hypothesis.
+This indicates that the effect of pain reliever type on cognitive performance does not vary meaningfully across dosage levels, and vice versa.
+Specifically, the ANOVA results demonstrated that the interaction term between drug type and dosage level did not reach significance, suggesting that dosage adjustments do not modify the cognitive effects of the tested pain relievers.
 This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention.

### 2025-04-09 paper/paper.qmd
Edits to Effect Size and Power Analysis

--- 2025-04-08 paper/paper.qmd
@@
 Our model yields  $R^2 = 0.0398$.
-While $R^2$ commonly used in regression analysis to a measure explained variance, determining the goodness of fit of a model.
-However, in ANOVA Model the $R^2$ value doesn't have a direct interpretation as the proportion of variance explained by regression model and it also does not directly reflect differences between group means.
-We use the $R^2$ value to report the effect that corresponds to Cohen’s f guidelines i.e.
-$| f |$ is approximately 0.20 as our  $R^2$ falls between the small-medium categories.Even though the statistical test did not yield significant results, this quantity suggests we have a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.
+While $R^2$ is commonly used in regression analysis to measure the proportion of variance and goodness of fit of the model, it can also be applied into ANOVA models.
+In that case, the $R^2$ value shows how much of the variation in the results can be explained by the different groups.
+However, it doesn't tell us how big or important the differences between the groups actually are.
+
+We use this $R^2$ value to report the effect that corresponds to Cohen’s f guidelines, i.e.
+$| f |$ is about 0.20 since our $R^2$ falls between the small-medium categories.
+Even though the statistical test did not yield significant results, this quantity suggests we have approximately a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.
 
@@
 
-This suggests that while our ANOVA results were not statistically significant, this may be due to insufficient power rather than the absence of any real effect.
+This suggests that while our ANOVA results were not statistically significant -- possibly due to insufficient power rather than the absence of any real effect.
 The observed effect sizes fall into the small range according to Cohen’s conventions, which typically require a larger sample size to detect reliably.

### 2025-04-09 paper/paper.qmd
Power/Effect Size
Limitations

@@
 In the future, we could test everyone for IQ scores and their highest level of education – these two nuisance variables can be taken care of by using the four principles of experimental design.
-Additionally, we used 30 observations for each treatment group which may not be large enough.
+
+Additionally, we used 30 observations for each treatment group, which may not be large enough.
 We can increase this number for future studies.
+In fact, our post-hoc power analysis showed that the statistical power for all three effects were quite low (ranging between 20% and 38%) with the effect sizes falling in the small-medium range.
+This suggests that the insignificance of our findings may have been due to limited power instead of the absence of a true effect.
+Future studies could prevent this issue by increasing the sample size or using stronger manipulations in order to improve the likelihood of detecting meaningful effects.
 To add on, not all participants were in pain, so the efficacy of the improvement of pain killers may be biased and using a virtual population may not ensure whether this aspect could be captured.
+
 Lastly, cognitive retention was measured immediately post-treatment – the long term impacts are not yet explored.
@@
 So if we were to include a wider range of dosages in future studies, it could give a fuller picture.
+
 Another issue is that our sample might not fully represent the general population since we selected participants from specific clusters of locations -- not all locations were covered equally.
@@
 Next time, we could choose more diverse and evenly spread-out clusters to make the results more general.
+
 Lastly, despite our efforts to control for confounding factors, there are still some variables (like sleep quality, stress levels, or baseline cognitive function) that could affect memory performance.

### 2025-04-10 paper/paper.qmd
Conclusion added

@@
 
+We performed a Two- way ANOVA to evaluate whether different types of pain relievers (Aspirin, Paracetamol, Tramadol, and Placebo) influence cognitive performance measured through memory game performance to address our research question 1.
+The null hypothesis proposed that all pain relievers produce equal effects on memory performance, while the alternative hypothesis suggests that at least one type differs significantly.
+The ANOVA results indicated that there was no statistical significant difference in memory game score between the four pain relievers under main effects.
+These results indicate that, at the standard dosages, none of the pain relievers significantly affected cognitive performance.
+This supports the interpretation that commonly used pain relievers neither impair nor enhance cognitive performance in the context of memory games performance.
+To answer research question 2, we employed the same Two-way ANOVA model to assess whether an interaction exists between the type of pain reliever (Aspirin, Paracetamol, Tramadol, and Placebo) and dosage level (low/high) on memory game performance.
+The analysis revealed no statistically significant interaction effect (p=0.24), leading us to fail to reject the null hypothesis.
+This indicates that the effect of pain reliever type on cognitive performance does not vary meaningfully across dosage levels, and vice versa.
+Specifically, the ANOVA results demonstrated that the interaction term between drug type and dosage level did not reach significance, suggesting that dosage adjustments do not modify the cognitive effects of the tested pain relievers.
+This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention.
+However, the exploratory trends observed, particularly with Paracetamol and Tramadol, highlight the need for larger-scale studies to investigate subtle or context-dependent effects.
+Future research could incorporate longitudinal designs, broader age-specific analyses, and alternative cognitive metrics to deepen understanding of painkillers’ cognitive implications.
 This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention.

### 2025-04-10 paper/paper.qmd
Changes in Conclusion

@@
 
-We performed a Two- way ANOVA to evaluate whether different types of pain relievers (Aspirin, Paracetamol, Tramadol, and Placebo) influence cognitive performance measured through memory game performance to address our research question 1.
+We performed a Two-way ANOVA to evaluate whether different types of pain relievers (Aspirin, Paracetamol, Tramadol, and Placebo) influence cognitive performance measured through memory game performance to address our research question 1.
 The null hypothesis proposed that all pain relievers produce equal effects on memory performance, while the alternative hypothesis suggests that at least one type differs significantly.
@@
 Specifically, the ANOVA results demonstrated that the interaction term between drug type and dosage level did not reach significance, suggesting that dosage adjustments do not modify the cognitive effects of the tested pain relievers.
+
 This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention.
@@
 This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention.
-However, the exploratory trends observed, particularly with Paracetamol and Tramadol, highlight the need for larger-scale studies to investigate subtle or context-dependent effects.
-Future research could incorporate longitudinal designs, broader age-specific analyses, and alternative cognitive metrics to deepen understanding of painkillers’ cognitive implications.
 

### 2025-04-10 paper/paper.qmd
Edits

@@
 We use this $R^2$ value to report the effect that corresponds to Cohen’s f guidelines, i.e.
-$| f |$ is about 0.20 since our $R^2$ falls between the small-medium categories.
+$| f |$ is assumed to be about 0.20 since our $R^2$ falls between the small-medium categories.
 Even though the statistical test did not yield significant results, this quantity suggests we have approximately a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.
@@
 
-This suggests that while our ANOVA results were not statistically significant -- possibly due to insufficient power rather than the absence of any real effect.
+This suggests that our ANOVA results were not statistically significant possibly due to insufficient power rather than the absence of any real effect.
 The observed effect sizes fall into the small range according to Cohen’s conventions, which typically require a larger sample size to detect reliably.
@@
 
-Lastly, cognitive retention was measured immediately post-treatment – the long term impacts are not yet explored.
+The cognitive retention was measured immediately post-treatment, but the long term impacts are not yet explored.
 To improve our study, we can try to consider individuals with real pain symptoms before the study to ensure a reduction of bias, and provide a realistic test setting.
@@
 
-Another issue is that our sample might not fully represent the general population since we selected participants from specific clusters of locations -- not all locations were covered equally.
+Another issue is that our sample might not fully represent the general population since we selected participants from specific clusters of locations, so not all locations were covered equally.
 This means our findings might not apply to everyone.
@@
 
-This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention.
+To conclude, this study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention.
 However, the exploratory trends observed, particularly with Paracetamol and Tramadol, highlight the need for larger-scale studies to investigate subtle or context-dependent effects.
